---
title: "Bacterial Carbon"
author: "Nicholas Baetge"
date: "5/19/2020"
output: github_document
---
# Intro

This document shows how **individual bottle** bacterial carbon data from NAAMES remineralization bioassays were processed, QC'd, and analyzed. 

```{r Packages, message = F, warning = F}
library(tidyverse) 
library(readxl)
library(zoo)
library(oce)
library(patchwork)
#stat tests
library(lmtest)
library(lmodel2)
library(rstatix)
library(ggpubr)
```


```{r Aesthetics, include = FALSE}
custom_theme <- function() {
  theme_test(base_size = 16) %+replace%
    theme(legend.position = "top",
          legend.title = element_blank(),
          legend.spacing.x = unit(0.5,"cm"),
          legend.background = element_rect(fill = "transparent",colour = NA),
          legend.key = element_rect(fill = "transparent",colour = NA),
          panel.background = element_rect(fill = "transparent",colour = NA),
          plot.background = element_rect(fill = "transparent",colour = NA),
          strip.text.x = element_text(size = 14, color = "white", face = "bold.italic"),
          strip.text.y = element_text(size = 14, color = "white", face = "bold.italic", angle = 270),
          strip.background = element_rect(color = "black", fill = "#005a9c", size = 0.5, linetype = "solid")) 
}

custom_theme_linedraw <- function() {
  theme_linedraw(base_size = 16) %+replace%
    theme(legend.position = "top",
          legend.title = element_blank(),
          legend.spacing.x = unit(0.5,"cm"),
          legend.background = element_rect(fill = "transparent",colour = NA),
          legend.key = element_rect(fill = "transparent",colour = NA),
          panel.background = element_rect(fill = "transparent",colour = NA),
          plot.background = element_rect(fill = "transparent",colour = NA),
          strip.text.x = element_text(size = 14, color = "white", face = "bold.italic"),
          strip.text.y = element_text(size = 14, color = "white", face = "bold.italic", angle = 270),
          strip.background = element_rect(color = "black", fill = "#005a9c", size = 0.5, linetype = "solid")) 
}

custom.colors <- c("AT39" = "#377EB8", "AT34" = "#4DAF4A", "AT38" = "#E41A1C", "AT32" = "#FF7F00", "Temperate" = "#A6CEE3", "Subpolar" = "#377EB8", "Subtropical" = "#FB9A99", "GS/Sargasso" = "#E41A1C", "Early Spring" = "#377EB8", "Late Spring" = "#4DAF4A","Early Autumn" = "#E41A1C", "Summer" = "#E41A1C", "Late Autumn" = "#FF7F00", "A" = "#E41A1C", "B" = "#377EB8", "C" = "#4DAF4A", "D" = "#FF7F00", "E" = "#FDB927", "F" = "#552583", "G" = "#FDB927", "H" = "#552583",   "Control" = "#E41A1C", "TW12" = "#377EB8", "T. Weissflogii 12C Exudate" = "#377EB8", "TW13" = "#4DAF4A", "T. Weissflogii 13C Exudate" = "#4DAF4A", "MixDS" = "#377EB8", "Deep Comm., Surface DOM" = "#377EB8","MixSD" = "#4DAF4A", "Surface Comm., Deep DOM" = "#4DAF4A", "SynLys" = "#377EB8", "Synechococcus Lysate" = "#377EB8", "SynExd" = "#4DAF4A", "Synechococcus Exudate" = "#4DAF4A", "TWExd" = "#FF7F00", "T. Weissflogii Exudate" = "#FF7F00", "TW5" = "#377EB8", "TW10" = "#4DAF4A", "TW20" = "#FF7F00", "Parallel" = "#377EB8", "W" = "#552583", "Whole Seawater" = "#552583", "1.2" = "#4DAF4A", "1.2 µm Filtrate" = "#4DAF4A", "NV" = "#FF7F00", "1.2 µm Filtrate: TFF Filtrate (3:7)" = "#FF7F00", "Carbon" = "#E41A1C", "Nitrogen" = "#377EB8", "+5 µmol C/L Exudate" = "#FF7F00", "+10 µmol C/L Exudate" = "#FF7F00", "+20 µmol C/L Exudate" = "#FF7F00", "Filter 1" = "#E41A1C", "Filter 2" = "#377EB8", "10 m" = "#E41A1C", "200 m" = "#377EB8", "BCD" = "#377EB8" , "NPP" = "#4DAF4A" , "Cruise Specific BGE" = "#377EB8", "Global BGE" = "#4DAF4A") 

custom.shapes <- c("Early Spring" = 21, "Late Spring" = 22,"Early Autumn" = 23)

custom.lines <- c("GS/Sargasso" = "blank", "Subtropical" = "solid", "Temperate" = "longdash", "Subpolar" = "dotted" )


levels = c("GS/Sargasso", "Subtropical", "Temperate", "Subpolar",  "AT39-6", "AT34", "AT38", "AT32","South", "North", "Early Spring", "Late Spring","Early Autumn",  "Summer", "Late Autumn", "Control", "Parallel", "SynLys", "SynExd", "TWExd", "MixSD", "MixDS", "TW12", "TW13", "TW5", "TW10", "TW20",  "Surface Comm., Deep DOM", "Deep Comm., Surface DOM", "Synechococcus Exudate", "Synechococcus Lysate", "T. Weissflogii Exudate", "T. Weissflogii 12C Exudate", "T. Weissflogii 13C Exudate", "+5 µmol C/L Exudate", "+10 µmol C/L Exudate","+20 µmol C/L Exudate", "A", "B", "C", "D", "E", "F", "G", "H", "I", "J", "K", "L", "M", "N", "O", "P", "W", "Whole Seawater","1.2", "1.2 µm Filtrate","NV", "1.2 µm Filtrate: TFF Filtrate (3:7)")
```

POC from DOC remineralization bioassays was estimated by filtering cells onto double-stacked GF75 filters (0.3 µm pore size) and then running each filter on an elemental analyzer at Bigelow (Maine). This document shows how bacterial carbon estimates were calculated from those measurements.

Upon importing the dataset, we'll add two categorical variables that indicate what type of filtrate was used as the "blank" water. On NAAMES 2, 0.2 µm-filtered water was used and on NAAMES 4, TFF-filtered water was used. Unfortunately, blanks were not taken on NAAMES 3. 

```{r Import data, message = F}

bigelow <- read_csv("~/GITHUB/naames_bioav_ms/Input/master/N2-4_BactC_Processing.csv") %>% 
  select(-c(Treatment_Btl:Days)) %>% 
  rename(Filter = Rep) %>% 
  mutate(BlnkFiltrate = ifelse(Cruise == "AT34", "0.2 µm", "TFF"),
         BlnkFiltrate = ifelse(Cruise == "AT38", NA, BlnkFiltrate),
         facetlabel = paste(Depth, " m"),
         Season = Cruise,
         Season = gsub("AT34", "Late Spring", Season),
         Season = gsub("AT38", "Early Autumn", Season),
         Season = gsub("AT39", "Early Spring", Season),
         Treatment = ifelse(is.na(Treatment), "Niskin", Treatment),
         Treatment = ifelse(Bottle %in% c("SA13", "SB13", "DA13", "DB13"), "TW13", Treatment),
         Bottle = gsub("SA", "A", Bottle),
         Bottle = gsub("SB", "B", Bottle),
         Bottle = gsub("DA", "C", Bottle),
         Bottle = gsub("DB", "D", Bottle), 
         Timepoint = ifelse(Treatment == "Niskin", 0, Timepoint)
         ) %>% 
  mutate_at(vars(BactN_µg, BactC_µg), round, 1)
```

Here, we plot all of the bacterial POC data from all of the experiments across all of the cruises, including blanks. We've cut off the max value to 25 µg C, but note there are samples with much greater values. 

```{r Bact POC plot, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center"}

bigelow %>% 
  mutate(blank = ifelse(Bottle == "Blank", "Blank", "Non-blank"),
         Filter = ifelse(Filter == 1, "First Filter", "Second Filter"),
         Addition = ifelse(!Treatment %in% c("Control", "MixDS", "MixSD", "Niskin"), "Amendment", NA),
         Addition = ifelse(Treatment %in% c("MixDS", "MixSD"), "Mix", Addition),
         Addition = ifelse(is.na(Addition), "Control", Addition)) %>%
  ggplot(aes(x = Season, y = BactC_µg)) + 
  geom_boxplot(width = 0.3, aes(group = Season)) +
  geom_jitter(width = 0.1, size = 4, alpha = 0.7, color = "black", shape = 21,aes(fill = factor(Addition, levels = c("Control", "Mix", "Amendment")))) +
  labs(x = "", y = expression(italic("POC, µg C")), colour = expression(italic("Filter")), shape = expression(italic("Blank Filtrate"))) + 
  #scale_colour_brewer(palette = "Set1") +
  custom_theme() +
  scale_y_continuous(limits = c(0, 25)) +
  facet_grid(Filter~blank )

```
There is a large spread in the data points for the second filter of the non-blank samples on the early autumn cruise, with higher values suggesting more material slipped through the first filter onto the second filter. 

# Determine Blank Correction 

```{r Subset blank data}
blank.data <- bigelow %>% 
  filter(Bottle == "Blank") %>% 
  mutate(BactC_µM = round(BactC_µg/12,2),
         BactN_µM = round(BactN_µg/14,2),
         BactC_N = ifelse(BactN_µM > 0, round(BactC_µM/BactN_µM,1), NA)) %>% 
  #filter out outliers
  filter(!Cruise == "AT34" | !Filter == 2 | !Depth == 10 | !Station == 1,
         !Cruise == "AT39" | !Filter == 1  | !Depth == 200 | !Station == 2)
```

The 0.2 µm filter 2 value of 6.46 and the TFF filter 1 value of 9.8 appears to be outliers relative to all the other filters (across cruises and filtrate types), indicating possible contamination or the compromised integrity of the first filter. These samples (filter 1 & 2) are going to be removed from the analysis.

## Filter t-tests
```{r Subset t-test data}
t.test.data <- bigelow %>% 
  filter(!Bottle %in% c("100mls", "250mls", "500mls")) %>%
  filter(!Season == "Late Spring" | !Station == 1 | !Depth == 10 | !Bottle == "Blank") %>%
  filter(!Season == "Early Spring" |  !Depth == 200 | !Bottle == "Blank") %>%
  mutate(Treatment = ifelse(Bottle == "Blank", "Blank", Treatment),
         Treatment = ifelse(Treatment == "Blank" & BlnkFiltrate == "TFF", "TFF", Treatment),
         Treatment = ifelse(Treatment == "Blank" & BlnkFiltrate == "0.2 µm", "0.2 µm", Treatment),
         Treatment = gsub("Niskin", "1.2 µm", Treatment),
         Type = ifelse(Bottle == "Blank", "Blank", "Non-blank")) %>% 
  select(Season, Treatment, Type, facetlabel, Filter, BactC_µg)  %>% 
  rename(Filtrate = Treatment,
         Depth = facetlabel)

```


```{r Blanks t-tests plots, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 18}

t.test.data %>% 
 filter(Type == "Blank") %>% 
  ggboxplot(x = "Filter", y = "BactC_µg", add = "jitter", width = 0.3, title = "POC: Blanks", xlab = expression(italic("Filter")), ylab = expression(italic("POC, µg"))) +
  stat_compare_means(label.y = 10, method = "t.test") +
  
   t.test.data %>% 
  filter(Type == "Blank", Filtrate == "0.2 µm") %>% 
  ggboxplot(x = "Filter", y = "BactC_µg", add = "jitter", width = 0.3, title = "POC: 0.2 µm Filtrate Blank ", xlab = expression(italic("Filter")), ylab = expression(italic(""))) +
  stat_compare_means(label.y = 6, method = "t.test") +
  
  t.test.data %>% 
  filter(Type == "Blank", Filtrate == "TFF") %>% 
  ggboxplot(x = "Filter", y = "BactC_µg", add = "jitter", width = 0.3, title = "POC: TFF Filtrate Blank ", xlab = expression(italic("Filter")), ylab = expression(italic(""))) +
  stat_compare_means(label.y = 11, method = "t.test") +

t.test.data %>% 
  filter(Type == "Blank", Filter == 1) %>% 
  ggboxplot(x = "Filtrate", y = "BactC_µg", add = "jitter", width = 0.3, title = "POC: Blank Filter 1", xlab = expression(italic("Filtrate")), ylab = expression(italic("POC, µg"))) +
  stat_compare_means(label.y = 10, method = "t.test") +

t.test.data %>% 
  filter(Type == "Blank", Filter == 2) %>% 
  ggboxplot(x = "Filtrate", y = "BactC_µg", add = "jitter", width = 0.3, title = "POC: Blank Filter 2", xlab = expression(italic("Filtrate")), ylab = expression(italic(""))) +
  stat_compare_means(label.y = 7, method = "t.test") 
  

```

There is a significant difference between the first (top) and second (bottom) filters of the blanks, suggesting that there was some material in the blank water that was caught on the first filter, subsequently increasing its carbon value. This difference appears to be driven mostly by the TFF filtrate. Given that there is not a significant diffence between the carbon retained filter 2 of the blanks, the mean of those values may provide a reasonable correction factor. 


## Summary Stats

We'll report non-blank corrected POC estimates as well as blank-corrected POC estimates. Because we will be calculating delta bacterial carbon to then estimate BGE, a blank correction may not be necessary. However, if we were to blank correct, we'll use universal correction factors based on the data/plots above. The detection limit for Bigelow's Costech ECS 4010 elemental analysis is 0.1 µg C.

We'll make 3 universal correction factors:

- poc.cf1 = the mean of filter 2 for all blanks
- poc.cf2 = the mean of filter 2 of only TFF filtrate blanks
- poc.cf3 = the mean of filter 2 of only 0.2 µm filtrate blanks

Each of these will be subtracted from each sample filter to estimate bacterial carbon in µg. Values below the detection limits for N (<0.1) are converted to 0. The addition of the corrected value from filter 1 and from filter 2 of each sample will provide the bacterial carbon estimate for that sample.

Bacterial carbon estimates will then be converted to µmol C^-1^. The same will be done for PON.

```{r Correction factors}
corrfactor <- blank.data %>% 
  filter(Filter == 2) %>% 
  select(Season, BlnkFiltrate, BactC_µg, BactN_µg) %>% 
  mutate(global_c_ug = mean(BactC_µg, na.rm = T),
         global_n_ug = mean(BactN_µg, na.rm = T),) %>% 
  group_by(BlnkFiltrate) %>% 
  mutate(filtrate_c_ug = mean(BactC_µg, na.rm = T),
         filtrate_n_ug = mean(BactN_µg, na.rm = T)) %>% 
  ungroup() %>% 
  select(-BactC_µg, -BactN_µg) %>% 
  distinct() %>% 
  mutate_at(vars(global_c_ug:filtrate_n_ug), round, 1) %>% 
  pivot_longer(cols = c(global_c_ug, filtrate_c_ug), names_to = "type", values_to = "poc_cf") %>% 
  mutate(type = ifelse(BlnkFiltrate == "0.2 µm" & type == "filtrate_c_ug", "poc.cf3", type),
         type = ifelse(BlnkFiltrate == "TFF" & type == "filtrate_c_ug", "poc.cf2", type),
         type = ifelse(type == "global_c_ug", "poc.cf1", type)) %>% 
   pivot_longer(cols = c(global_n_ug, filtrate_n_ug), names_to = "n_type", values_to = "pon_cf") %>% 
   mutate(n_type = ifelse(BlnkFiltrate == "0.2 µm" & n_type == "filtrate_n_ug", "pon.cf3", n_type),
         n_type = ifelse(BlnkFiltrate == "TFF" & n_type == "filtrate_n_ug", "pon.cf2", n_type),
         n_type = ifelse(n_type == "global_n_ug", "pon.cf1", n_type)) %>% 
  select(type:pon_cf) %>% 
  distinct() %>% 
  pivot_wider(names_from = type, values_from = poc_cf) %>% 
  pivot_wider(names_from = n_type, values_from = pon_cf) %>% 
  fill(poc.cf1:pon.cf2, .direction = "downup") %>% 
  distinct() %>% 
  select(poc.cf1, poc.cf2, poc.cf3, pon.cf1, pon.cf2, pon.cf3)

corrfactor
  
```

# Perform Corrections


The carbon correction factors are subtracted from the POC values of the samples:

- poc.c1.ug = POC (µg) - poc.cf1
- poc.c2.ug = POC (µg) - poc.cf2
- poc.c3.ug = POC (µg) - poc.cf3 

which are then converted to µmol C L^-1^:

- poc.c1.um
- poc.c2.um
- poc.c3.um
 
We will do the same for nitrogen:

- pon.cx.ug = PON (µg) - pon.cf1, 2, or 3 

and convert the calculated values to µmol N L ^-1^:

- pon.cx.um

We'll also calculate C:N ratios:

- cn = poc.um/pon.um
- cn.c1 = poc.c1.um/pon.um
- cn.c2 = poc.c2.um/pon.um
- cn.c3 = poc.c3.um/pon.m

```{r Corrected carbon}
bactcarbon <- bigelow %>%
  filter(!Bottle == "Blank") %>%
  mutate(Treatment = ifelse(Bottle %in% c("1L", "100mls", "250mls", "500mls"), "Volume", Treatment)) %>% 
  rename(pon.ug = BactN_µg,
         poc.ug = BactC_µg) %>% 
  cbind(., corrfactor) %>% 
  mutate(poc.c1.ug = poc.ug - poc.cf1,
         poc.c2.ug = poc.ug - poc.cf2,
         poc.c3.ug = poc.ug - poc.cf3,
         pon.c1.ug = pon.ug - pon.cf1,
         pon.c2.ug = pon.ug - pon.cf2,
         pon.c3.ug = pon.ug - pon.cf3,
         poc.c1.ug = ifelse(poc.c1.ug < 0, 0, poc.c1.ug),
         poc.c2.ug = ifelse(poc.c2.ug < 0, 0, poc.c2.ug),
         poc.c3.ug = ifelse(poc.c3.ug < 0, 0, poc.c3.ug),
         pon.c1.ug = ifelse(pon.c1.ug < 0, 0, pon.c1.ug),
         pon.c2.ug = ifelse(pon.c2.ug < 0, 0, pon.c2.ug),
         pon.c3.ug = ifelse(pon.c3.ug < 0, 0, pon.c3.ug)) %>%
  group_by(Cruise, Station, Depth, Bottle, Timepoint) %>%
  mutate(poc.ug = round((sum(poc.ug)),1),
         pon.ug = round((sum(pon.ug)),1),
         poc.c1.ug = round((sum(poc.c1.ug)),1),
         poc.c2.ug = round((sum(poc.c2.ug)),1),
         poc.c3.ug = round((sum(poc.c3.ug)),1),
         pon.c1.ug = round((sum(pon.c1.ug)),1),
         pon.c2.ug = round((sum(pon.c2.ug)),1),
         pon.c3.ug = round((sum(pon.c3.ug)),1)) %>% 
  ungroup() %>% 
  mutate(poc.um = round(poc.ug/12, 1),
         poc.c1.um = round(poc.c1.ug/12, 1),
         poc.c2.um = round(poc.c2.ug/12, 1),
         poc.c3.um = round(poc.c3.ug/12, 1),
         pon.um = round(pon.ug/14, 1),
         pon.c1.um = round(pon.c2.ug/14, 1),
         pon.c2.um = round(pon.c2.ug/14, 1),
         pon.c3.um = round(pon.c3.ug/14, 1),
         cn = round(poc.um/pon.um),
         cn.c1 = round(poc.c1.um/pon.c1.um),
         cn.c2 = round(poc.c2.um/pon.c2.um),
         cn.c3 = round(poc.c3.um/pon.c3.um)) %>% 
  select(Season, Cruise, Station, Depth, facetlabel, Treatment, Bottle, Timepoint, poc.ug, pon.ug, poc.cf1, poc.cf2, poc.cf3, pon.cf1, pon.cf2, pon.cf3, poc.c1.ug:cn.c3 ) %>% 
  distinct() %>% 
  arrange(Season, Cruise, Station, Depth, Treatment, Bottle, Timepoint) 
  
```


# Calculate Carbon Per Cell

Here we calculate fg C or fg N cell^-1^ by:

- Estimating the cell abundance captured on the 0.3 µm GF75 filters (whole water - filtrate, cells L^-1^) 
- Dividing the GF75 POC or PON value (µmol C or N L^-1^) by the cell abundance on the GF75 filter, then applying the subsequent conversions

The GF75 POC data are tidied before calculations are made (e.g renaming bottle identifiers so they are congruent with datasets to be merged with, duplicating values for initial timepoints where one POC value was taken for replicate bottles). For ease, initial POC and cell abundance data are handled separately from data collected at stationary timepoints. 

## Calculate Filter Cell Abundance and Retention

```{r Import cell abundance}
#initial cell abundance
i.gf75 <- readRDS("~/GITHUB/naames_bioav_ms/Input/master/tidy_N2-4_BactA_Remin_Master.rds") %>% 
  select(Season:cells) %>% 
  filter(Timepoint == 0, Bottle %in% c("GF75", "Niskin")) %>% 
  group_by(Cruise, Station, Depth) %>% 
  mutate(filtrate.cells = ifelse(Bottle == "GF75", cells, NA)) %>% 
  fill(filtrate.cells, .direction = "downup") %>% 
  filter(Bottle == "Niskin") %>% 
  mutate(i.gf75.cells = cells - filtrate.cells,
         i.gf75.ret = round((cells - filtrate.cells)/cells, 2)) %>% 
  ungroup() %>% 
  select(Season:Depth, i.gf75.cells, i.gf75.ret)

#stationary cell abundance
s.gf75 <- readRDS("~/GITHUB/naames_bioav_ms/Input/master/tidy_N2-4_BactA_Remin_Master.rds") %>% 
  select(Season:cells) %>% 
  filter(!Timepoint == 0) %>% 
  arrange(Cruise, Station, Depth, Bottle, Timepoint) %>% 
  group_by(Cruise, Station,  Depth, Bottle) %>%
  mutate(gf75.timepoint = ifelse(Treatment == "GF75", Timepoint, NA)) %>% 
  fill(gf75.timepoint, .direction = "updown") %>% 
  filter(Timepoint == gf75.timepoint) %>% 
  mutate(filtrate.cells = ifelse(Treatment == "GF75", cells, NA)) %>% 
  fill(filtrate.cells, .direction = "updown") %>%  
  filter(!Treatment == "GF75") %>% 
  mutate(s.gf75.cells = cells - filtrate.cells,
         s.gf75.ret = round((cells - filtrate.cells)/cells, 2)) %>% 
  ungroup() %>% 
  select(Season:Bottle, Treatment, Timepoint, s.gf75.cells, s.gf75.ret) 
```


## Combine Cell Abundance and POC Data, Calculate CCF

We'll calculate 6 CCFs (fg C cell^-1^) from the POC data:

- i.ccf.c1 = poc.c1.um/cells on filter * 12 * 10^9^ (initial)
- s.ccf.c1 = poc.c1.um/cells on filter * 12 * 10^9^ (stationary)
- i.ccf.c2 = poc.c2.um/cells on filter * 12 * 10^9^ (initial)
- s.ccf.c2 = poc.c2.um/cells on filter * 12 * 10^9^ (stationary)
- i.ccf.c3 = poc.c3.um/cells on filter * 12  * 10^9^ (initial)
- s.ccf.c3 = poc.c3.um/cells on filter * 12  * 10^9^ (stationary)

We'll also add 3 other CCFs from the literature:

- ccf.white = 6.5 (SAR11), White et al 2019 
  + also close to 6.3 of Carlson et al 1996 and 7 of Zubkov 2000
- ccf.fukuda = 12.3 (average oceanic Pacific), Fukuda et al 1998 
  + also close to 10 generally used by many papers Wear et al 2020, Christian and Karl 1994, Caron et al 1995, James et al 2017
- ccf.lee = 20 (Long Island Sound), Lee and Fuhrman 1987
  + generally used as reported by Gunderson et al 2002

```{r CCF calculations, message= F, warning = F}

#initial timepoints
i.fg_cell <-  bactcarbon %>% 
  filter(!Treatment == "Volume", Timepoint == 0) %>% 
  select_at(vars(poc.ug:cn.c3), .funs = funs(paste0("i.", .))) %>% 
  bind_cols(bactcarbon %>% filter(!Treatment == "Volume", Timepoint == 0) %>% select(Season:facetlabel), .) %>% 
  mutate(Station = gsub("2RD", "S2RD", Station),
         Station = gsub("2RF", "S2RF", Station)) %>% 
  left_join(., i.gf75) %>% 
  mutate(i.ccf.c1 = round(i.poc.c1.um/i.gf75.cells * 12 * 10^9),
         i.ccf.c2 = round(i.poc.c2.um/i.gf75.cells * 12 * 10^9),
         i.ccf.c3 = round(i.poc.c3.um/i.gf75.cells * 12 * 10^9)) 

#stationary timepoints
s.fg_cell <- bactcarbon %>% 
  filter(!Treatment == "Volume", !Timepoint == 0) %>% 
  select_at(vars(poc.ug:cn.c3), .funs = funs(paste0("s.", .))) %>% 
  bind_cols(bactcarbon %>% filter(!Treatment == "Volume", !Timepoint == 0) %>% select(Season:facetlabel, Treatment, Bottle, Timepoint), .) %>% 
  mutate(Station = gsub("2RD", "S2RD", Station),
         Station = gsub("2RF", "S2RF", Station),
         Treatment = gsub("TW15", "TW20", Treatment),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW12" & Bottle == "A12", gsub("A12", "C", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW12" & Bottle == "B12", gsub("B12", "D", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW13" & Bottle == "A13", gsub("A13", "E", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW13" & Bottle == "B13", gsub("B13", "F", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "Control" & Bottle == "C", gsub("C", "G", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "Control" & Bottle == "D", gsub("D", "H", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW12" & Bottle == "C12", gsub("C12", "I", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW12" & Bottle == "D12", gsub("D12", "J", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW13" & Bottle == "C13", gsub("C13", "K", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW13" & Bottle == "D13", gsub("D13", "L", Bottle), Bottle)) %>% 
  add_row(Season = "Early Autumn", Cruise = "AT38", Station = "1", Depth = 10, Treatment = "SynExd", Bottle = "I") %>% 
    add_row(Season = "Early Autumn", Cruise = "AT38", Station = "1", Depth = 10, Treatment = "SynLys", Bottle = "N") %>% 
  add_row(Season = "Early Autumn", Cruise = "AT38", Station = "1", Depth = 10, Treatment = "TWExd", Bottle = "K") %>% 
  add_row(Season = "Early Autumn", Cruise = "AT38", Station = "1", Depth = 200, Treatment = "SynLys", Bottle = "P") %>% 
  arrange(Cruise, Station, Depth, Treatment, Bottle) %>% 
  group_by(Cruise, Station, Depth, Treatment) %>% 
  fill(s.poc.ug:s.cn.c3, .direction = "updown") %>% 
  mutate(Bottle = gsub("JI", "J", Bottle),
         Bottle = gsub("MN", "M", Bottle),
         Bottle = gsub("LK", "L", Bottle),
         Bottle = gsub("OP", "O", Bottle)) %>% 
  left_join(., s.gf75) %>% 
  mutate(s.ccf.c1 = round(s.poc.c1.um/s.gf75.cells * 12 * 10^9),
         s.ccf.c2 = round(s.poc.c2.um/s.gf75.cells * 12 * 10^9),
         s.ccf.c3 = round(s.poc.c3.um/s.gf75.cells * 12 * 10^9)) %>% 
  ungroup() %>% 
  rename(s.timepoint = Timepoint)

fg_cell <- left_join(s.fg_cell, i.fg_cell)  %>% 
   group_by(Cruise, Station, Depth, Treatment) %>% 
  fill(c(s.timepoint,i.poc.ug:i.ccf.c3), .direction = "updown") %>% 
  mutate(ccf.white = 6.5,
         ccf.fukuda = 12.3,
         ccf.lee = 20) %>% 
  ungroup()
  
```

## Flag Retention of GF75 Filters

```{r GF75 retention plot, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 10}
fg_cell %>% 
  select(Season, Station, Depth, Treatment, Bottle, i.gf75.ret, s.gf75.ret) %>% 
  mutate(facet_depth = paste(Depth, "m"),
         type = ifelse(Treatment == "Control", "Control", "Non-control")) %>% 
  gather(key, value, i.gf75.ret:s.gf75.ret) %>% 
  mutate(key = gsub("i.gf75.ret", "Initial", key),
         key = gsub("s.gf75.ret", "Stationary", key),
         value = ifelse(key == "Initial" & Bottle %in% c("B", "D", "F"), NA, value)) %>% 
  ggplot(aes(x = Season, y = value)) + 
  geom_boxplot(width = 0.3) +
  geom_jitter(aes(fill = key), width = 0.1, shape = 21, size = 4, alpha = 0.7) + 
  labs(x = "", y = expression(italic("Bacterioplankton Fraction Retained on GF75")), colour = expression(italic(""))) + 
  scale_fill_brewer(palette = "Set1") +
  custom_theme() +
  facet_grid(facet_depth+type~key, scales = "free")

```

```{r Retention statistics, echo = F, message = F}
ret.stats <- fg_cell %>% 
  select(Season, Cruise, Station, Bottle, Depth, Treatment, i.gf75.ret, s.gf75.ret) %>% 
  mutate(facet_depth = paste(Depth, "m"),
         type = ifelse(Treatment == "Control", "Control", "Non-control")) %>% 
  gather(key, value, i.gf75.ret:s.gf75.ret) %>% 
  mutate(key = gsub("i.gf75.ret", "Initial", key),
         key = gsub("s.gf75.ret", "Stationary", key),
         value = ifelse(key == "Initial" & Bottle %in% c("B", "D", "F"), NA, value)) 

ret.stats %>% 
  filter(key == "Initial", Treatment == "Control", Depth == 10) %>% 
  drop_na() %>% ungroup() %>% 
  mutate(ave_Initial_10m = mean(value),
         sd_Initial_10m = sd(value)) %>% 
  select(contains("ave"), contains("sd")) %>% distinct() %>% 
  bind_cols(., ret.stats %>% 
              filter(key == "Initial", Treatment == "Control", Depth == 200) %>%
              drop_na() %>% ungroup() %>% 
              mutate(ave_Initial_200m = mean(value),
                     sd_Initial_200m = sd(value)) %>%
              select(contains("ave"), contains("sd")) %>% distinct()) %>% 
  bind_cols(., ret.stats %>% 
              filter(key == "Stationary", Treatment == "Control", Depth == 10) %>%
              drop_na() %>% ungroup() %>% 
              mutate(ave_Stat_Control_10m = mean(value),
                     sd_Stat_Control_10m = sd(value)) %>%
              select(contains("ave"), contains("sd")) %>% distinct()) %>% 
  bind_cols(., ret.stats %>% 
              filter(key == "Stationary", type == "Non-control", Depth == 10) %>%
              drop_na() %>% ungroup() %>% 
              mutate(ave_Stat_Noncontrol_10m = mean(value),
                     sd_Stat_Noncontrol_10m = sd(value)) %>%
              select(contains("ave"), contains("sd")) %>% distinct()) %>% 
  bind_cols(., ret.stats %>% 
              filter(key == "Stationary", Treatment == "Control", Depth == 200) %>%
              drop_na() %>% ungroup() %>% 
              mutate(ave_Stat_Control_200m = mean(value),
                     sd_Stat_Control_200m = sd(value)) %>%
              select(contains("ave"), contains("sd")) %>% distinct()) %>% 
  bind_cols(., ret.stats %>% 
              filter(key == "Stationary", type == "Non-control", Depth == 200) %>%
              drop_na() %>% ungroup() %>% 
              mutate(ave_Stat_Noncontrol_200m = mean(value),
                     sd_Stat_Noncontrol_200m = sd(value)) %>%
              select(contains("ave"), contains("sd")) %>% distinct()) %>% 
  pivot_longer(., contains(c("ave", "sd")), names_to = "group", values_to = "value") %>% 
  mutate(ave = ifelse(group %in% c("ave_Initial_10m", "ave_Initial_200m", "ave_Stat_Control_10m", "ave_Stat_Noncontrol_10m", "ave_Stat_Control_200m", "ave_Stat_Noncontrol_200m"), value, NA),
         sd = ifelse(group %in% c("sd_Initial_10m", "sd_Initial_200m", "sd_Stat_Control_10m", "sd_Stat_Noncontrol_10m", "sd_Stat_Control_200m", "sd_Stat_Noncontrol_200m"), value, NA),
         group = gsub("ave_", "", group),
         group = gsub("sd_", "", group)) %>% 
  group_by(group) %>% 
  fill(ave:sd, .direction = "downup") %>% 
  select(-value) %>% distinct() %>%
  mutate_at(vars(ave, sd), round, 2)
    
```

This figure shows that while GF75 filter retention is fairly consistent across the samples taken during the stationary phase of cell growth, they are pretty variable for the samples taken at the initial condition. Those samples with filter retentions below the average for a group could reflect faulty procedure (i.e. ripped filters) and may be associated with questionable measurements. We'll flag these data. 

```{r Flag data based on retention}
fg_cell.qc <- fg_cell %>% 
  mutate(type = ifelse(Treatment == "Control", "Control", "Non-control"),
         i.gf75.flag = ifelse(Depth == 10 & i.gf75.ret < 0.72, "< Ave. Ret.", NA),
         i.gf75.flag = ifelse(Depth == 200 & i.gf75.ret < 0.51, "< Ave. Ret.", i.gf75.flag ),
         i.gf75.flag = ifelse(is.na(i.gf75.ret), "ND", i.gf75.flag),
         i.gf75.flag = ifelse(is.na(i.gf75.flag), "No Flag", i.gf75.flag),
         s.gf75.flag = ifelse(Depth == 10 & type == "Control" & s.gf75.ret < 0.81, "< Ave. Ret.", NA),
         s.gf75.flag = ifelse(Depth == 10 & type == "Non-control" & s.gf75.ret < 0.88, "< Ave. Ret.",  s.gf75.flag ),
         s.gf75.flag = ifelse(Depth == 200 & type == "Control" & s.gf75.ret < 0.76, "< Ave. Ret.",  s.gf75.flag ),
         s.gf75.flag = ifelse(Depth == 200 & type == "Non-control" & s.gf75.ret < 0.95, "< Ave. Ret.",  s.gf75.flag ),
         s.gf75.flag = ifelse(is.na(s.gf75.ret), "ND", s.gf75.flag),
         s.gf75.flag = ifelse(is.na(s.gf75.flag), "No Flag", s.gf75.flag),
         gf75.flag = ifelse(i.gf75.flag == "No Flag" & s.gf75.flag == "No Flag", "No Flag", NA),
         gf75.flag = ifelse(i.gf75.flag == "< Ave. Ret." & s.gf75.flag == "No Flag", "Init. < Ave. Ret.", gf75.flag),
         gf75.flag = ifelse(s.gf75.flag == "< Ave. Ret." & i.gf75.flag == "No Flag", "Stat. < Ave. Ret.", gf75.flag),
         gf75.flag = ifelse(i.gf75.flag == "< Ave. Ret." & s.gf75.flag == "ND", "Init. < Ave. Ret./Stat. ND", gf75.flag),
         gf75.flag = ifelse(i.gf75.flag == "< Ave. Ret." & s.gf75.flag == "< Ave. Ret.", "< Ave. Ret.", gf75.flag),
         gf75.flag = ifelse(i.gf75.flag == "No Flag" & s.gf75.flag == "ND", "Stat. ND", gf75.flag),
         gf75.flag = ifelse(s.gf75.flag == "No Flag" & i.gf75.flag == "ND", "Init. ND", gf75.flag),
         gf75.flag = ifelse(s.gf75.flag == "ND" & i.gf75.flag == "ND", "ND", gf75.flag)) %>% 
  select(Season:Bottle, type, i.gf75.ret, s.gf75.ret, i.gf75.flag, s.gf75.flag, gf75.flag, contains("i."), contains("s."), contains("ccf"))

```


# CCFs

```{r CCF statistics, echo = FALSE, message = F}
fg_cell.qc %>% 
  filter(Treatment == "Control", Depth == 10, !Station == "U") %>% 
  select(Cruise, contains("i.ccf"), contains("s.ccf")) %>% 
  group_by(Cruise) %>% 
  mutate_at(vars(contains("ccf")), mean, na.rm = T) %>%
  mutate_at(vars(contains("ccf")), round) %>% distinct() %>% 
  pivot_longer(., contains("ccf"), names_to = "correction", values_to = "ave_ccf") %>% 
  left_join(., fg_cell.qc %>% 
              filter(Treatment == "Control", Depth == 10) %>% 
              select(Cruise, contains("i.ccf"), contains("s.ccf")) %>%
              group_by(Cruise) %>% 
              mutate_at(vars(contains("ccf")), sd, na.rm = T) %>%
              mutate_at(vars(contains("ccf")), round) %>% distinct() %>%
              pivot_longer(., contains("ccf"), names_to = "correction", values_to = "sd"))

```


```{r CCF plots with flags, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 20}
fg_cell.qc %>% 
  filter(!Station == "U", Depth == 10) %>% 
  select(Season, Station, Depth, Bottle, Treatment, gf75.flag, i.ccf.c1, i.ccf.c2, i.ccf.c3, s.ccf.c1, s.ccf.c2, s.ccf.c3) %>% 
  mutate(facet_depth = paste(Depth, "m"),
         type = ifelse(Treatment == "Control", "Control", "Non-control"),
         i.ccf.c1 = ifelse(type != "Control", NA, i.ccf.c1),
         i.ccf.c2 = ifelse(type != "Control", NA, i.ccf.c2),
         i.ccf.c3 = ifelse(type != "Control", NA, i.ccf.c3)) %>% 
  gather(key, value, i.ccf.c1:s.ccf.c3) %>% 
  mutate(label = key,
         label = gsub("i.ccf.c1", "POC corr. filt 2, all blanks", label),
         label = gsub("i.ccf.c2", "POC corr. filt 2, TFF blanks", label),
         label = gsub("i.ccf.c3", "POC corr. filt 2, 0.2 µm blanks", label),
         label = gsub("s.ccf.c1", "POC corr. filt 2, all blanks", label),
         label = gsub("s.ccf.c2", "POC corr. filt 2, TFF blanks", label),
         label = gsub("s.ccf.c3", "POC corr. filt 2, 0.2 µm blanks", label),
         time = ifelse(key %in% c("i.ccf.c1", "i.ccf.c2", "i.ccf.c3"), "Initial", "Stationary"),
         value = ifelse(time == "Initial" & Bottle %in% c("B", "D", "F"), NA, value)) %>% 
  filter(!type == "Non-control" | !time == "Initial") %>% 
  ggplot(aes(x = Season, y = value)) + 
  geom_boxplot(width = 0.3) +
  geom_jitter(aes(fill = factor(gf75.flag, levels = c("No Flag", "Init. < Ave. Ret.", "Stat. < Ave. Ret.", "< Ave. Ret.", "Init. < Ave. Ret./Stat. ND", "Init. ND", "Stat. ND"))), shape = 21, width = 0.1,  size = 4, alpha = 0.6) + 
  labs(x = "", y = expression(italic("Cellular Carbon, fg C cell"^-1)), colour = expression(italic(""))) + 
  custom_theme() +
  facet_grid(type+time~factor(label, levels = c("POC uncorr.", "POC corr. filt 2, all blanks","POC corr. filt 2, TFF blanks", "POC corr. filt 2, 0.2 µm blanks" )), scales = "free") + 
  ggtitle("Carbon Conversion Factors")

```

The points are colored by the QC flag associated with the POC samples. ”Questionable” measures indicate below average (of all samples, not grouped) cell retention on the POC filters. “ND” indicates no data. 


# C:N Ratios

```{r C:N statistics, echo = FALSE, message = F}
fg_cell.qc %>% 
  filter(Treatment == "Control", Depth == 10, !Station == "U") %>% 
  na_if(., "Inf") %>% 
  select(Cruise, contains("i.cn"), contains("s.cn")) %>% 
  group_by(Cruise) %>% 
  mutate_at(vars(contains("cn")), mean, na.rm = T) %>%
  mutate_at(vars(contains("cn")), round, 1) %>% distinct() %>% 
  pivot_longer(., contains("cn"), names_to = "correction", values_to = "ave_cn") %>% 
  left_join(., fg_cell.qc %>% 
              filter(Treatment == "Control", Depth == 10, !Station == "U",  !i.cn == "Inf") %>% 
              na_if(., "Inf") %>% 
              select(Cruise, contains("i.cn"), contains("s.cn")) %>%
              group_by(Cruise) %>% 
              mutate_at(vars(contains("cn")), sd, na.rm = T) %>%
              mutate_at(vars(contains("cn")), round, 1) %>% distinct() %>%
              pivot_longer(., contains("cn"), names_to = "correction", values_to = "sd"))

```


```{r C:N ratio plots, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 20}
fg_cell.qc %>% 
  filter(Depth == 10, !Station == "U") %>% 
  select(Season, Station, Depth, Bottle, Treatment, gf75.flag, i.cn, i.cn.c1, i.cn.c2, i.cn.c3, s.cn, s.cn.c1, s.cn.c2, s.cn.c3) %>% 
  mutate(facet_depth = paste(Depth, "m"),
         type = ifelse(Treatment == "Control", "Control", "Non-control"),
         i.cn = ifelse(type != "Control", NA, i.cn),
         i.cn.c1 = ifelse(type != "Control", NA, i.cn.c1),
         i.cn.c2 = ifelse(type != "Control", NA, i.cn.c2),
         i.cn.c3 = ifelse(type != "Control", NA, i.cn.c3)) %>% 
  gather(key, value, i.cn:s.cn.c3) %>% 
  mutate(label = key,
         label = gsub("i.cn.c1", "POC corr. filt 2, all blanks", label),
         label = gsub("i.cn.c2", "POC corr. filt 2, TFF blanks", label),
         label = gsub("i.cn.c3", "POC corr. filt 2, 0.2 µm blanks", label),
         label = gsub("i.cn", "POC uncorr.", label),
         label = gsub("s.cn.c1", "POC corr. filt 2, all blanks", label),
         label = gsub("s.cn.c2", "POC corr. filt 2, TFF blanks", label),
         label = gsub("s.cn.c3", "POC corr. filt 2, 0.2 µm blanks", label),
         label = gsub("s.cn", "POC uncorr.", label),
         time = ifelse(key %in% c("i.cn", "i.cn.c1", "i.cn.c2", "i.cn.c3"), "Initial", "Stationary"),
         value = ifelse(time == "Initial" & Bottle %in% c("B", "D", "F"), NA, value)) %>%
  filter(!type == "Non-control" | !time == "Initial") %>% 
  ggplot(aes(x = Season, y = value)) + 
  geom_boxplot(width = 0.3) +
  geom_jitter(aes(fill = factor(gf75.flag, levels = c("No Flag", "Init. < Ave. Ret.", "Stat. < Ave. Ret.", "< Ave. Ret.", "Init. < Ave. Ret./Stat. ND", "Init. ND", "Stat. ND"))), shape = 21, width = 0.1,  size = 4, alpha = 0.6) + 
  labs(x = "", y = expression(italic("Cellular C:N")), colour = expression(italic(""))) + 
  custom_theme() +
  facet_grid(type+time~factor(label, levels = c("POC uncorr.", "POC corr. filt 2, all blanks","POC corr. filt 2, TFF blanks", "POC corr. filt 2, 0.2 µm blanks" )), scales = "free") + 
  ggtitle("Cellular C:N")

```

The points on the line intersecting the max of the y-axis represent "Inf" values, where PON values are 0. 

We would expect the carbon content of oceanic surface bacterioplankton to be around 5 (Faggerbakke et al 1996, Fukuda et al, 1998, Gundersen et al 2002, Zimmerman et al 2014, White et al 2019). Excluding infinity values where PON was undetectable, C:N ratios for the spring are comparable to expectations, with slight improvement using corrected values. 

The C:N ratios of the early autumn samples are clear outliers, outside even the maximum reported by Gundersen et al 2002 (9.1). These high values might point to issues with the POC data. What might be causing the high C:N ratios observed in the early autumn? Below average cell retentions don’t appear to be skewing results in at least the initial condition or during the spring. It could, in some cases, be skewing early autumn measurements.

# Identify Outliers: Property-Property Plots


```{r CCF property-property, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 12, fig.width = 28}

ccf_prop_prop <- fg_cell.qc %>%
  select(Season:Bottle, i.ccf.c1, i.ccf.c2, i.ccf.c3, s.ccf.c1, s.ccf.c2, s.ccf.c3 ) %>% 
  gather(key, ccf, i.ccf.c1:s.ccf.c3) %>% 
  mutate(time = ifelse(str_detect(key, "i"), "Initial", "Stationary" ),
         corr = ifelse(str_detect(key, "c1"), "POC corr. filt 2, all blanks", NA),
         corr = ifelse(str_detect(key, "c2"), "POC corr. filt 2, TFF blanks", corr),
         corr = ifelse(str_detect(key, "c3"),  "POC corr. filt 2, 0.2 µm blanks", corr),
         ccf = ifelse(time == "Initial" & Bottle %in% c("B", "D", "F"), NA, ccf), 
         ccf = ifelse(time == "Initial" & Treatment != "Control", NA, ccf), 
         type = ifelse(Treatment == "Control", "Control", "Non-control")) %>% 
  drop_na(ccf) %>% 
  select(-key)

ccf_prop_prop  %>% 
  left_join(., fg_cell.qc %>% 
              select(Season:Bottle, i.gf75.ret, s.gf75.ret ) %>%
              gather(time, ret, i.gf75.ret:s.gf75.ret) %>%
              mutate(time = ifelse(str_detect(time, "i"), "Initial", "Stationary" )) ) %>% 
  mutate(facetlabel = paste(Depth, "m")) %>% 
  filter(Depth == 10) %>% 
  mutate(vline = ifelse(Treatment == "Control" & time == "Initial", 66, NA),
         vline = ifelse(Treatment == "Control" & time == "Stationary", 80, vline),
         vline = ifelse(!Treatment == "Control" & time == "Stationary", 90, vline)) %>% 
  #####PLOT####
  ggplot(aes(x =  ret*100, y = ccf)) +
  geom_point( aes(fill = Season), shape = 21, size = 4, alpha = 0.7 ) +
  geom_vline(aes(xintercept = vline), color  = "blue", linetype = 2) +
  labs(x = expression(paste("GF75 Filter Cell Retention, %")), y = expression(paste("Cellular C, fg C Cell"^-1)), caption = "Blue dotted line indicates mean.") +
  scale_x_continuous(trans = 'log10') +
  scale_y_continuous(trans = 'log10') +
  scale_fill_manual(values = custom.colors) +
  custom_theme_linedraw()  +
  facet_grid(type + time~factor(corr, levels = c("POC corr. filt 2, all blanks", "POC corr. filt 2, TFF blanks", "POC corr. filt 2, 0.2 µm blanks")), scales = "free") +
  theme(plot.caption = element_text(color = "blue", face = "italic"),
        strip.background.y = element_blank()) +
  
  #################################
  ccf_prop_prop  %>% 
  left_join(., fg_cell.qc %>% 
              select(Season:Bottle, i.gf75.cells, s.gf75.cells ) %>%
              gather(time, cells, i.gf75.cells:s.gf75.cells) %>%
              mutate(time = ifelse(str_detect(time, "i"), "Initial", "Stationary" )) ) %>% 
  mutate(facetlabel = paste(Depth, "m")) %>% 
  #####PLOT####
  ggplot(aes(x =  cells/10^9, y = ccf)) +
  geom_point( aes(fill = Season), shape = 21, size = 4, alpha = 0.7 ) +
  labs(x = expression(paste("10"^9," Cells L"^-1)), y = expression(paste(""))) +
  scale_x_continuous(trans = 'log10') +
  scale_y_continuous(trans = 'log10') +
  scale_fill_manual(values = custom.colors) +
  custom_theme_linedraw()  +
  facet_grid(type + time~factor(corr, levels = c("POC corr. filt 2, all blanks", "POC corr. filt 2, TFF blanks", "POC corr. filt 2, 0.2 µm blanks")), scales = "free") +
  guides(fill = F)  +
  
  #########################
  ccf_prop_prop  %>% 
  left_join(., fg_cell.qc %>% 
              select(Season:Bottle, i.poc.um:i.poc.c3.um, s.poc.um:s.poc.c3.um ) %>%
              gather(key, poc, i.poc.um:s.poc.c3.um) %>%
              mutate(time = ifelse(str_detect(key, "i"), "Initial", "Stationary" ),
                   corr = ifelse(str_detect(key, "c1"), "POC corr. filt 2, all blanks", NA),
                   corr = ifelse(str_detect(key, "c2"), "POC corr. filt 2, TFF blanks", corr),
                   corr = ifelse(str_detect(key, "c3"),  "POC corr. filt 2, 0.2 µm blanks", corr),
                   corr = ifelse(key %in% c("i.poc.um", "s.poc.um"), "POC uncorr.", corr)) %>% 
              drop_na(poc) %>% 
              select(-key)) %>% 
  mutate(facetlabel = paste(Depth, "m")) %>% 
  #####PLOT####
  ggplot(aes(x =  poc, y = ccf)) +
  geom_point( aes(fill = Season), shape = 21, size = 4, alpha = 0.7 ) +
  labs(x = expression(paste("POC, µmol C L"^-1)), y = expression(paste("Cellular C, fg C Cell"^-1))) +
  scale_x_continuous(trans = 'log10') +
  scale_y_continuous(trans = 'log10') +
  scale_fill_manual(values = custom.colors) +
  custom_theme_linedraw()  +
  facet_grid(type + time~factor(corr, levels = c("POC uncorr.", "POC corr. filt 2, all blanks", "POC corr. filt 2, TFF blanks", "POC corr. filt 2, 0.2 µm blanks")), scales = "free") +
  guides(fill = F) +
  theme(strip.background.y = element_blank(),
        strip.background.x = element_blank()) +
  
#########################
  ccf_prop_prop  %>% 
   left_join(., fg_cell.qc %>% 
              select(Season:Bottle, i.cn:i.cn.c3, s.cn:s.cn.c3 ) %>%
              gather(key, cn, i.cn:s.cn.c3) %>%
              mutate(time = ifelse(str_detect(key, "i"), "Initial", "Stationary" ),
                    corr = ifelse(str_detect(key, "c1"), "POC corr. filt 2, all blanks", NA),
                    corr = ifelse(str_detect(key, "c2"), "POC corr. filt 2, TFF blanks", corr),
                    corr = ifelse(str_detect(key, "c3"),  "POC corr. filt 2, 0.2 µm blanks", corr),
                    corr = ifelse(key %in% c("i.cn", "s.cn"), "POC uncorr.", corr)) %>% 
              drop_na(cn) %>% 
              select(-key)) %>% 
  mutate(facetlabel = paste(Depth, "m")) %>% 
  filter(Depth == 10) %>% 
  #####PLOT####
  ggplot(aes(x = cn, y = ccf)) +
  geom_point( aes(fill = Season), shape = 21, size = 4, alpha = 0.7 ) +
  geom_vline(xintercept = 5, linetype = 2, color = "blue") +
  geom_hline(yintercept = 12.4, linetype = 2, color = "red" ) +
  labs(x = expression(paste("Bacterial C:N")), y = expression(paste("")), caption = "Blue and red dotted lines indicate expected values from literature.") +
  scale_x_continuous(trans = 'log10') +
  scale_y_continuous(trans = 'log10') +
  scale_fill_manual(values = custom.colors) +
  custom_theme_linedraw()  +
  facet_grid(type + time~corr, scales = "free") +
  annotate(geom = "text", x = 30, y = 80, label = "Q1", color = "#005a9c") +
  annotate(geom = "text", x = 30, y = 5, label = "Q2", color = "#005a9c") +
  annotate(geom = "text", x = 1, y = 5, label = "Q3", color = "#005a9c") +
  annotate(geom = "text", x = 1, y = 80, label = "Q4", color = "#005a9c") +
  guides(fill = F) +
  theme(strip.background.x = element_blank(),
        plot.caption = element_text(color = "blue", face = "italic")) + 
  
  plot_annotation(tag_levels = "a")
  
```


```{r cell C property-property, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 28, fig.align = "center", warning = FALSE}

cellC_prop_prop <- fg_cell.qc %>% 
  select(Season:Bottle, i.poc.um:i.poc.c3.um, s.poc.um:s.poc.c3.um ) %>%
  gather(key, poc, i.poc.um:s.poc.c3.um) %>%
  mutate(time = ifelse(str_detect(key, "i"), "Initial", "Stationary" ),
         corr = ifelse(str_detect(key, "c1"), "POC corr. filt 2, all blanks", NA),
         corr = ifelse(str_detect(key, "c2"), "POC corr. filt 2, TFF blanks", corr),
         corr = ifelse(str_detect(key, "c3"),  "POC corr. filt 2, 0.2 µm blanks", corr),
         corr = ifelse(key %in% c("i.poc.um", "s.poc.um"), "POC uncorr.", corr),
         poc = ifelse(time == "Initial" & Bottle %in% c("B", "D", "F"), NA, poc), 
         poc = ifelse(time == "Initial" & Treatment != "Control", NA, poc), 
         type = ifelse(Treatment == "Control", "Control", "Non-control")) %>% 
  drop_na(poc) %>% 
  select(-key) 

cellC_prop_prop %>% 
  left_join(., fg_cell.qc %>% 
              select(Season:Bottle, i.gf75.ret, s.gf75.ret ) %>%
              gather(time, ret, i.gf75.ret:s.gf75.ret) %>%
              mutate(time = ifelse(str_detect(time, "i"), "Initial", "Stationary" )) ) %>% 
  mutate(facetlabel = paste(Depth, "m")) %>% 
  filter(Depth == 10) %>% 
  mutate(vline = ifelse(Treatment == "Control" & time == "Initial", 66, NA),
         vline = ifelse(Treatment == "Control" & time == "Stationary", 80, vline),
         vline = ifelse(!Treatment == "Control" & time == "Stationary", 90, vline)) %>% 
  #####PLOT####
  ggplot(aes(x =  ret*100, y = poc)) +
  geom_point( aes(fill = Season), shape = 21, size = 4, alpha = 0.7 ) +
  geom_vline(aes(xintercept = vline), color  = "blue", linetype = 2) +
  labs(x = expression(paste("GF75 Filter Cell Retention, %")), y = expression(paste("POC, µmol C L"^-1))) +
  scale_x_continuous(trans = 'log10') +
  scale_y_continuous(trans = 'log10') +
  scale_fill_manual(values = custom.colors) +
  custom_theme_linedraw()  +
  facet_grid(type + time~factor(corr, levels = c("POC uncorr.", "POC corr. filt 2, all blanks", "POC corr. filt 2, TFF blanks", "POC corr. filt 2, 0.2 µm blanks")), scales = "free") +
  theme(strip.background.y = element_blank()) +

########################
cellC_prop_prop %>% 
   left_join(., fg_cell.qc %>% 
              select(Season:Bottle, i.gf75.cells, s.gf75.cells ) %>%
              gather(time, cells, i.gf75.cells:s.gf75.cells) %>%
              mutate(time = ifelse(str_detect(time, "i"), "Initial", "Stationary" )) ) %>% 
  mutate(facetlabel = paste(Depth, "m")) %>% 
  filter(Depth == 10) %>% 
  #####PLOT####
  ggplot(aes(x =  cells/10^9, y = poc)) +
  geom_point( aes(fill = Season), shape = 21, size = 4, alpha = 0.7 ) +
  labs(x = expression(paste("10"^9," Cells L"^-1)), y = expression(paste("POC, µmol C L"^-1))) +
  scale_x_continuous(trans = 'log10') +
  scale_y_continuous(trans = 'log10') +
  scale_fill_manual(values = custom.colors) +
  custom_theme_linedraw()  +
  facet_grid(type + time~factor(corr, levels = c("POC uncorr.", "POC corr. filt 2, all blanks", "POC corr. filt 2, TFF blanks", "POC corr. filt 2, 0.2 µm blanks")), scales = "free") +
  guides(fill = F)

```

Generally, samples with below average cell retentions have higher cell C content, but this seems to be less of an effect at stationary. 

For the initial condition, it is clear that there are two outliers  in the spring data. The  initial early spring outlier sample (station 1) has a reasonable C:N ratio (2-3), a low POC value, and a relatively high carbon per cell estimate (35-53 fg C cell^-1^). This points to an issue in the cell count data, where cell abundance is likely underestimated. The late spring  outlier is characterized by a C:N ratio and a cell carbon content that does not deviate from the rest of the late spring data, so it may not be a true outlier.

The early autumn sample (station 1) with a cell carbon content of 77 fg C cell^-1^ and a filter cell retention of 55% has low POC infinity C:N ratio. All of these metrics would suggest this sample to be a true outlier where filter cell abundance was likely underestimated due to ripped filters. The other two early autumn samples with slightly below average cell retentions do have high cell carbon contents (56-57 fg C cell-1), but also have lower C:N ratios (9, 11) than the remaining early autumn samples (13, 25, infinity), making them hard to distinguish as outliers. 

The cell carbon content and C:N ratios of all early autumn samples are higher than what is expected for oceanic bacterioplankton. It is possible that POC is overestimated or cell abundances are underestimated for these samples (or both). Low cell retentions for these samples would suggest that cell abundances could have been underestimated. Generally, the relationship between cell carbon content and C:N appear to be reasonable at stationary, with less separation between the seasons. This would suggest that the POC data taken during the early autumn are not necessarily all compromised. The divergence of these samples from the other seasons could point to other factors, such as the larger influence of detrital matieral. 

We will remove the CCF for the two outlier samples (intial condition, AT39 S1 and AT38 S1) from remaining analyses. 

```{r GF75 retention with QCd data}
fg_cell.qc %>% 
  select(Season:s.gf75.ret) %>% 
  filter(Depth == 10, Treatment == "Control") %>% 
  select(-c(Depth:Treatment, type)) %>% 
  distinct() %>% 
  mutate(i.gf75.ret = ifelse(Cruise == "AT39" & Station == 1, NA, i.gf75.ret),
        s.gf75.ret = ifelse(Cruise == "AT39" & Station == 1, NA, s.gf75.ret),
        i.gf75.ret = ifelse(Cruise == "AT38" & Station == 1, NA, i.gf75.ret),
        s.gf75.ret = ifelse(Cruise == "AT38" & Station == 1, NA, s.gf75.ret),
        i.gf75.ret = ifelse(Bottle == "B", NA, i.gf75.ret)) %>% 
  pivot_longer(i.gf75.ret:s.gf75.ret, names_to = "names", values_to = "ret" ) %>% 
  drop_na(ret) %>% 
  mutate(ave_ret = mean(ret),
         sd_re = sd(ret))
  
```

# Save Data

```{r Remove outliers & save}
unfiltered.data <- fg_cell.qc %>% 
  mutate(i.ccf.c1 = ifelse(Cruise == "AT39" & Station == 1 & Depth == 10, NA, i.ccf.c1),
         i.ccf.c2 = ifelse(Cruise == "AT39" & Station == 1 & Depth == 10, NA, i.ccf.c2),
         i.ccf.c3 = ifelse(Cruise == "AT39" & Station == 1 & Depth == 10, NA, i.ccf.c3),
         i.ccf.c1 = ifelse(Cruise == "AT38" & Station == 1 & Depth == 10, NA, i.ccf.c1),
         i.ccf.c2 = ifelse(Cruise == "AT38" & Station == 1 & Depth == 10, NA, i.ccf.c2),
         i.ccf.c3 = ifelse(Cruise == "AT38" & Station == 1 & Depth == 10, NA, i.ccf.c3))
  
saveRDS(unfiltered.data, "~/GITHUB/naames_bioav_ms/Output/unfiltered/processed_bacterial_carbon.rds")

filtered.data <- unfiltered.data %>% 
  filter(Treatment == "Control", Depth == 10, !Station == "U") %>% 
  select(Season:Bottle,s.timepoint, contains(c("poc.cf1", "poc.c1.um", "ccf.c1", "pon.cf1", "pon.c1.um", "ccf.c1", "cn.c1")), -facetlabel) 
  
saveRDS(filtered.data, "~/GITHUB/naames_bioav_ms/Output/filt_processed_bacterial_carbon.rds")
```



