---
title: "BCD and DOC Bioavailability"
author: "Nicholas Baetge"
date: "5/26/2020"
output: github_document
---

# Intro

This document shows plots and tables of the merged field-experiment NAAMES DOC data.

```{r message = F, warning = F}
library(tidyverse) 
library(rmarkdown)
library(knitr)
library(readxl)
library(data.table) 
library(scales)
library(zoo)
library(oce)
library(patchwork)
#rmarkdown tables
library(stargazer)
library(pander)
library(growthcurver)
#stat tests
library(lmtest)
library(lmodel2)
library(rstatix)
library(ggpubr)
```


```{r include = FALSE}
custom_theme <- function() {
  theme_test(base_size = 16) %+replace%
    theme(legend.position = "top",
          legend.title = element_blank(),
          legend.spacing.x = unit(0.5,"cm"),
          legend.background = element_rect(fill = "transparent",colour = NA),
          legend.key = element_rect(fill = "transparent",colour = NA),
          panel.background = element_rect(fill = "transparent",colour = NA),
          plot.background = element_rect(fill = "transparent",colour = NA),
          strip.text.x = element_text(size = 14, color = "white", face = "bold.italic"),
          strip.text.y = element_text(size = 14, color = "white", face = "bold.italic", angle = 270),
          strip.background = element_rect(color = "black", fill = "#005a9c", size = 0.5, linetype = "solid")) 
}

custom_theme_linedraw <- function() {
  theme_linedraw(base_size = 16) %+replace%
    theme(legend.position = "top",
          legend.title = element_blank(),
          legend.spacing.x = unit(0.5,"cm"),
          legend.background = element_rect(fill = "transparent",colour = NA),
          legend.key = element_rect(fill = "transparent",colour = NA),
          panel.background = element_rect(fill = "transparent",colour = NA),
          plot.background = element_rect(fill = "transparent",colour = NA),
          strip.text.x = element_text(size = 14, color = "white", face = "bold.italic"),
          strip.text.y = element_text(size = 14, color = "white", face = "bold.italic", angle = 270),
          strip.background = element_rect(color = "black", fill = "#005a9c", size = 0.5, linetype = "solid")) 
}

custom.colors <- c("AT39" = "#377EB8", "AT34" = "#4DAF4A", "AT38" = "#E41A1C", "AT32" = "#FF7F00", "Temperate" = "#A6CEE3", "Subpolar" = "#377EB8", "Subtropical" = "#FB9A99", "GS/Sargasso" = "#E41A1C", "Early Spring" = "#377EB8", "Late Spring" = "#4DAF4A","Early Autumn" = "#E41A1C", "Summer" = "#E41A1C", "Late Autumn" = "#FF7F00", "A" = "#E41A1C", "B" = "#377EB8", "C" = "#4DAF4A", "D" = "#FF7F00", "E" = "#FDB927", "F" = "#552583", "G" = "#FDB927", "H" = "#552583",   "Control" = "#E41A1C", "TW12" = "#377EB8", "T. Weissflogii 12C Exudate" = "#377EB8", "TW13" = "#4DAF4A", "T. Weissflogii 13C Exudate" = "#4DAF4A", "MixDS" = "#377EB8", "Deep Comm., Surface DOM" = "#377EB8","MixSD" = "#4DAF4A", "Surface Comm., Deep DOM" = "#4DAF4A", "SynLys" = "#377EB8", "Synechococcus Lysate" = "#377EB8", "SynExd" = "#4DAF4A", "Synechococcus Exudate" = "#4DAF4A", "TWExd" = "#FF7F00", "T. Weissflogii Exudate" = "#FF7F00", "TW5" = "#377EB8", "TW10" = "#4DAF4A", "TW20" = "#FF7F00", "Parallel" = "#377EB8", "W" = "#552583", "Whole Seawater" = "#552583", "1.2" = "#4DAF4A", "1.2 µm Filtrate" = "#4DAF4A", "NV" = "#FF7F00", "1.2 µm Filtrate: TFF Filtrate (3:7)" = "#FF7F00", "Carbon" = "#E41A1C", "Nitrogen" = "#377EB8", "+5 µmol C/L Exudate" = "#FF7F00", "+10 µmol C/L Exudate" = "#FF7F00", "+20 µmol C/L Exudate" = "#FF7F00", "Filter 1" = "#E41A1C", "Filter 2" = "#377EB8", "10 m" = "#E41A1C", "200 m" = "#377EB8", "BCD" = "#377EB8" , "NPP" = "#4DAF4A" , "Cruise Specific BGE" = "#377EB8", "Global BGE" = "#4DAF4A", "Long-term" = "#377EB8","Short-term" = "#E41A1C") 

custom.shapes <- c("Early Spring" = 21, "Late Spring" = 22,"Early Autumn" = 23)

custom.lines <- c("GS/Sargasso" = "blank", "Subtropical" = "solid", "Temperate" = "longdash", "Subpolar" = "dotted" )


levels = c("GS/Sargasso", "Subtropical", "Temperate", "Subpolar",  "AT39-6", "AT34", "AT38", "AT32","South", "North", "Early Spring", "Late Spring","Early Autumn",  "Summer", "Late Autumn", "Control", "Parallel", "SynLys", "SynExd", "TWExd", "MixSD", "MixDS", "TW12", "TW13", "TW5", "TW10", "TW20",  "Surface Comm., Deep DOM", "Deep Comm., Surface DOM", "Synechococcus Exudate", "Synechococcus Lysate", "T. Weissflogii Exudate", "T. Weissflogii 12C Exudate", "T. Weissflogii 13C Exudate", "+5 µmol C/L Exudate", "+10 µmol C/L Exudate","+20 µmol C/L Exudate", "A", "B", "C", "D", "E", "F", "G", "H", "I", "J", "K", "L", "M", "N", "O", "P", "W", "Whole Seawater","1.2", "1.2 µm Filtrate","NV", "1.2 µm Filtrate: TFF Filtrate (3:7)")
```

# Import Data

```{r}
doc <- read_rds("~/naames_bioav_ms/Output/processed_bioavailability.rds") %>% 
   select(-c(Bottle, doc, interp_doc)) %>% 
  arrange(Cruise, Station, Hours) %>% 
  distinct() %>% 
  mutate(bge = ifelse(Cruise == "AT39" & Station == 4, T, F),
         bge = ifelse(Cruise == "AT34" & Station %in% c(1, 2, 3), T, bge),
         bge = ifelse(Cruise == "AT38" & Station %in% c(3, 6), T, bge),
         degree_bin = as.character(degree_bin))  %>% 
  distinct()  %>% 
  #for 3 stations, 
  filter(int_delta_DOC_ez > 0)

bcd <- read_rds("~/naames_bioav_ms/Output/processed_integrated_BCD.rds")
```


Units for imported data frames are currently: 

- BP, µmol C m^-3^ d^-1^
- BCD, µmol C m^-3^ d^-1^
- BA, cells m^-3^
- BC,  µmol C m^-3^
- mew, d^-1^
- NPP, µmol C m^-3^ d^-1^
- ∆DOC (from export MS, integrated to Ez), mol C m^-2^

# Bar plots: NPP, BP, BA, µ, ∆DOC

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 14, fig.width = 12, fig.align = "center", warning = FALSE}

#NPP
npp.bar <- bcd %>% 
  select(Cruise:Station, degree_bin, int.NPP, sd_int.NPP) %>%  distinct() %>% 
  mutate_at(vars(contains("NPP")), funs(./10^3)) %>% 
  mutate_at(vars(degree_bin), as.character) %>% 
  ##PLOT
  ggplot(aes(x = degree_bin, y =  int.NPP, group = interaction(Season, Station, degree_bin)))  + 
  geom_bar(position = position_dodge(), stat = "identity", color = "black", fill = "#999999", alpha = 1) +
  geom_errorbar(aes(ymin = int.NPP - sd_int.NPP, ymax = int.NPP + sd_int.NPP), position = position_dodge(width = 0.9), stat = "identity", width = 0.1, size = 0.5) +
  labs(x = expression(italic("")), y = expression(italic(paste("NPP, mmol C m"^-3, "d"^-1))), colour = expression(italic(""))) +
  scale_y_continuous(breaks = pretty_breaks()) +
  custom_theme() +
  facet_grid(~factor(Season, levels = levels), scales = "free") +
  guides(fill = F) 
  
#BP
bp.bar <- bcd %>% 
  select(Cruise:Station, degree_bin, int.bp, sd_int.bp) %>% distinct() %>% 
  mutate_at(vars(degree_bin), as.character) %>% 
  ##PLOT
  ggplot(aes(x = degree_bin, y =  int.bp, group = interaction(Season, Station, degree_bin)))  + 
  geom_bar(position = position_dodge(), stat = "identity", color = "black", fill = "#999999", alpha = 1) +
  geom_errorbar(aes(ymin = int.bp - sd_int.bp, ymax = int.bp + sd_int.bp), position = position_dodge(width = 0.9), stat = "identity", width = 0.1, size = 0.5) +
  labs(x = expression(italic("")), y = expression(italic(paste("BP, µmol C m"^-3, "d"^-1))), colour = expression(italic(""))) +
  scale_y_continuous(breaks = pretty_breaks()) +
  custom_theme() +
  facet_grid(~factor(Season, levels = levels), scales = "free") +
  theme(strip.background = element_blank(), strip.text = element_blank()) +
  guides(fill = F)

#BA 
ba.bar <- bcd %>% 
  select(Cruise:Station, degree_bin, int.ba, sd_int.ba) %>% distinct() %>% 
  mutate_at(vars(degree_bin), as.character) %>% 
  ##PLOT
  ggplot(aes(x = degree_bin, y =  int.ba, group = interaction(Season, Station, degree_bin)))  + 
  geom_bar(position = position_dodge(), stat = "identity", color = "black", fill = "#999999", alpha = 1) +
  geom_errorbar(aes(ymin = int.ba - sd_int.ba, ymax = int.ba + sd_int.ba), position = position_dodge(width = 0.9), stat = "identity", width = 0.1, size = 0.5) +
  labs(x = expression(italic("")), y = expression(italic(paste("BA, cells m"^-3))), colour = expression(italic(""))) +
  scale_y_continuous(breaks = pretty_breaks()) +
  scale_fill_manual(values = custom.colors) +
  custom_theme() +
  facet_grid(~factor(Season, levels = levels), scales = "free") +
  theme(strip.background = element_blank(), strip.text = element_blank()) +
  guides(fill = F)


#µ
mew.bar <- bcd %>% 
  select(Cruise:Station, degree_bin, contains("mew")) %>% 
  distinct() %>% 
  pivot_longer(cols = c(mew.global_i, mew.global_s, mew.season_i, mew.season_s), names_to = "ccf", values_to = "mew") %>%  
  mutate(ccf = ifelse(ccf == "mew.global_i", "Initial Global CCF", NA),
         ccf = ifelse(ccf == "mew.global_s", "Stationary Global CCF", ccf),
         ccf = ifelse(ccf == "mew.season_i", "Initial Season-specific CCF", ccf),
         ccf = ifelse(ccf == "mew.season_s", "Stationary Season-specific CCF", ccf),
         degree_bin = as.character(degree_bin)) %>% 
  group_by(Cruise, Station) %>% 
  mutate(ave = mean(mew),
         sd = sd(mew)) %>% 
  ungroup() %>% 
  ##PLOT
  ggplot(aes(x = degree_bin, y =  ave, group = interaction(Season, Station, degree_bin)))  + 
  geom_bar(position = position_dodge(), stat = "identity", color = "black", fill = "#999999", alpha = 1) +
  geom_errorbar(aes(ymin = ave - sd, ymax = ave + sd), position = position_dodge(width = 0.9), stat = "identity", width = 0.1, size = 0.5) +
  labs(x = expression(italic("")), y = expression(italic(paste("µ, d"^-1))), colour = expression(italic(""))) +
  scale_y_continuous(breaks = pretty_breaks()) +
  scale_fill_manual(values = custom.colors) +
  custom_theme() +
  facet_grid(~factor(Season, levels = levels), scales = "free") +
  theme(strip.background = element_blank(), strip.text = element_blank()) +
  guides(fill = F) 

# ∆DOC
deldoc.bar <- doc %>% 
  select(Season:Subregion, degree_bin, Ez, int_delta_DOC_ez) %>% 
  drop_na(int_delta_DOC_ez) %>% 
  distinct() %>% 
  ##PLOT
  ggplot(aes(x = degree_bin, y =  int_delta_DOC_ez, group = interaction(Season, Station, degree_bin)))  + 
  geom_bar(position = position_dodge(), stat = "identity", color = "black", fill = "#999999", alpha = 1) +
  labs(x = expression(italic("Latitude, ˚N")), y = expression(italic(paste("∆DOC, mol C m"^-3))), colour = expression(italic(""))) +
  scale_y_continuous(breaks = pretty_breaks()) +
  custom_theme() +
  facet_grid(~factor(Season, levels = levels), scales = "free") +
  theme(strip.background = element_blank(), strip.text = element_blank()) +
  guides(fill = F)

npp.bar / bp.bar / ba.bar / mew.bar / deldoc.bar
```

Error bars for µ represent standard deviation from mean of values calculated using different CCFs to convert BA to BC (Global Initial CCF, Global Stationary CCF, Season-Specific Initial CCF, Season-Specific Stationary CCF). All other error bars represent standard deviation from mean of station values. 


# Table: NPP and Bacterial Parameters

```{r message = F}
bcd_table <- bcd %>% 
  select(Cruise:degree_bin, int.bcd.global_bge, int.bcd.season_bge) %>% 
  distinct() %>% 
  mutate_at(vars(int.bcd.global_bge, int.bcd.season_bge), funs(./1000)) %>% 
  pivot_longer(cols = c(int.bcd.global_bge, int.bcd.season_bge), names_to = "var", values_to = "bcd") %>% 
  select(-var) %>% 
  distinct() %>% 
  group_by(Cruise, Season, Subregion, degree_bin, Station) %>% 
  summarise(ave_BCD = round(mean(bcd), 2),
            sd_BCD = round(sd(bcd), 2)) %>% 
  ungroup() %>% 
  left_join(., bcd %>% 
              select(Cruise:Station, degree_bin,ave_Ez, sd_Ez, int.NPP, sd_int.NPP) %>% 
              distinct() %>% 
              mutate_at(vars(contains("NPP")), funs(round(./10^3, 2)))
            ) %>% 
  left_join(., bcd %>% 
              select(Cruise:Station, degree_bin, bcd.npp.global_bge, bcd.npp.season_bge) %>% 
              distinct() %>% 
              pivot_longer(cols = c( bcd.npp.global_bge, bcd.npp.season_bge), names_to = "var", values_to = "bcd_npp") %>% 
              select(-var) %>% 
              distinct() %>% 
              group_by(Cruise, Season, Subregion, degree_bin, Station) %>% 
              summarise(ave_BCD_NPP = mean(bcd_npp),
                        sd_BCD_NPP = sd(bcd_npp)) %>% 
              ungroup()
            ) %>% 
  arrange(factor(Season, levels = levels)) %>% 
  group_by(Cruise) %>% 
  mutate(Cruise_ave_Ez = mean(ave_Ez),
         Cruise_sd_Ez = sd(ave_Ez),
         Cruise_ave_NPP = mean(int.NPP),
         Cruise_sd_NPP = sd(int.NPP),
         Cruise_ave_BCD = mean(ave_BCD),
         Cruise_sd_BCD = sd(ave_BCD),
         Cruise_ave_BCD_NPP = mean(ave_BCD_NPP),
         Cruise_sd_BCD_NPP = sd(ave_BCD_NPP)
         ) %>% 
  ungroup() %>% 
  group_by(Cruise, Subregion) %>% 
  mutate(Cruise_SR_ave_NPP = mean(int.NPP),
         Cruise_SR_sd_NPP = mean(int.NPP),
         Cruise_SR_ave_BCD = mean(ave_BCD),
         Cruise_SR_sd_BCD = sd(ave_BCD),
         Cruise_SR_ave_BCD_NPP = mean(ave_BCD_NPP),
         Cruise_SR_sd_BCD_NPP = sd(ave_BCD_NPP)
         ) %>% 
  ungroup() %>% 
  mutate_at(vars(contains("BCD_NPP")), round) %>% 
  mutate_at(vars(Cruise_ave_NPP:Cruise_sd_BCD, Cruise_SR_ave_NPP:Cruise_SR_sd_BCD ), round, 2) %>% 
  arrange(factor(Season, levels = levels), factor(Subregion, levels = levels))
```

```{r echo = FALSE, results = 'asis'}
kable(bcd_table, caption = "BCD & NPP")
```


# Line plots: DOC Decay Curves 

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 16, fig.align = "center", warning = FALSE}
doc %>% 
  drop_na(sd_doc) %>% 
  group_by(Cruise, Station) %>%
  ggplot(aes(x = Days, y = norm_doc, group = interaction(Cruise, Station, degree_bin))) + 
  geom_hline(aes(yintercept = 0)) +
  geom_vline(aes(xintercept = 7), linetype = 2) +
  geom_vline(aes(xintercept = 30), linetype = 3) +
  geom_errorbar(aes(ymin = norm_doc - sd_doc, ymax = norm_doc + sd_doc, color = factor(Season, levels = levels)), width = 0.5) +
  geom_point(aes(fill = factor(Season, levels = levels)), size = 3, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Season, linetype = bge), size = 0.75, alpha = 0.7) +
  geom_label(aes(x = 7, y = -1, label = "Short-term"), size = 3) +
  geom_label(aes(x = 30, y = -1, label = "Long-term"), size = 3) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~factor(Subregion, levels = levels), scales = "free") +
  labs(x = expression(italic("Days")), y = expression(italic(paste("Seasonally Accumulated DOC, µmol C L"^-1)))) +
  custom_theme() +
  guides(color = F, linetype = F)
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 16, fig.align = "center", warning = FALSE}
doc %>% 
  drop_na(sd_doc) %>% 
  group_by(Cruise, Station) %>%
  ggplot(aes(x = Days, y = norm_doc, group = interaction(Cruise, Station, degree_bin))) + 
  geom_hline(aes(yintercept = 0)) +
  geom_vline(aes(xintercept = 7), linetype = 2) +
  geom_vline(aes(xintercept = 30), linetype = 3) +
  geom_errorbar(aes(ymin = norm_doc - sd_doc, ymax = norm_doc + sd_doc, color = factor(Subregion, levels = levels)), width = 0.5) +
  geom_point(aes(fill = factor(Subregion, levels = levels)), size = 3, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Subregion, linetype = bge), size = 0.75, alpha = 0.7) +
  geom_label(aes(x = 7, y = -1, label = "Short-term"), size = 3) +
  geom_label(aes(x = 30, y = -1, label = "Long-term"), size = 3) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~factor(Season, levels = levels), scales = "free") +
 labs(x = expression(italic("Days")), y = expression(italic(paste("Seasonally Accumulated DOC, µmol C L"^-1)))) +
  custom_theme() +
  guides(color = F, linetype = F)
```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8, fig.align = "center", warning = FALSE}
doc %>% 
  filter(degree_bin == 44) %>% 
  drop_na(sd_doc) %>% 
  group_by(Cruise, Station) %>%
  ggplot(aes(x = Days, y = norm_doc, group = interaction(Cruise, Station, degree_bin))) + 
  geom_hline(aes(yintercept = 0)) +
  geom_vline(aes(xintercept = 7), linetype = 2) +
  geom_vline(aes(xintercept = 30), linetype = 3) +
  geom_errorbar(aes(ymin = norm_doc - sd_doc, ymax = norm_doc + sd_doc, color = factor(Season, levels = levels)), width = 0.5) +
  geom_point(aes(fill = factor(Season, levels = levels)), size = 3, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Season, linetype = bge), size = 0.75, alpha = 0.7) +
  geom_label(aes(x = 7, y = -1, label = "Short-term"), size = 3) +
  geom_label(aes(x = 30, y = -1, label = "Long-term"), size = 3) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  #facet_grid(~factor(Season, levels = levels), scales = "free") +
 labs(x = expression(italic("Days")), y = expression(italic(paste("Seasonally Accumulated DOC, µmol C L"^-1)))) +
  custom_theme() +
  ggtitle("44˚N") +
  guides(color = F, linetype = F)
```


Black vertical dashed and dotted lines indicate the 7 and 30-day marks, respectively. Dashed decay lines indicate experiments in which BGEs could be calculated. 

# Table: ∆DOC, Bioavailability, Persistence

```{r}
bioav.table <- doc %>% 
  select(Season:Subregion, degree_bin, int_delta_DOC_ez, contains("bioav_accm_doc"), contains("bioav_doc"), contains("per_bioav"), contains("persis"), contains("ddoc")) %>% 
  distinct() %>% 
  group_by(Season, Subregion, degree_bin) %>% 
  summarise(ave_accm = round(mean(int_delta_DOC_ez, na.rm = T), 2),
            sd_accm = round(sd(int_delta_DOC_ez, na.rm = T), 2),
            
            ave_total.deldoc = round(mean(total.bioav_accm_doc, na.rm = T), 2),
            sd_total.deldoc = round(sd(total.bioav_accm_doc, na.rm = T), 2),
            ave_st.deldoc = round(mean(st.bioav_accm_doc, na.rm = T), 2),
            sd_st.deldoc = round(sd(st.bioav_accm_doc, na.rm = T), 2),
            ave_total.per_bioav = round(mean(total.per_bioav, na.rm = T), 2),
            sd_total.per_bioav = round(sd(total.per_bioav, na.rm = T), 2),
            ave_st.per_bioav = round(mean(st.per_bioav, na.rm = T), 2),
            sd_st.per_bioav = round(sd(st.per_bioav, na.rm = T), 2),
            
            ave_per_persis = round(mean(per_persis, na.rm = T), 2),
            sd_per_persis = round(sd(per_persis, na.rm = T), 2),
            
            ave_total.ddoc = round(mean(total.ddoc, na.rm = T), 2),
            sd_total.ddoc = round(sd(total.ddoc, na.rm = T), 2),
            ave_st.ddoc = round(mean(st.ddoc, na.rm = T), 2),
            sd_st.ddoc = round(sd(st.ddoc, na.rm = T), 2),
            
            
            ) %>%
   arrange(factor(Season, levels = levels), degree_bin) %>% 
  ungroup()
```


```{r echo = FALSE, results = 'asis'}
kable(bioav.table, caption = "Seasonal Accumulated DOC Bioavailability and Persistance")
```

# Bar plots: Experiment ∆DOC and %Bioavailability


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 12, fig.align = "center", warning = FALSE}
# δDOC
ddoc.bar <- doc %>% 
  filter(!Cruise == "AT32") %>% 
  select(Season:Subregion, degree_bin, total.bioav_accm_doc, st.bioav_accm_doc) %>% 
  distinct() %>% 
  pivot_longer(cols = c(total.bioav_accm_doc, st.bioav_accm_doc), names_to = "names", values_to = "values") %>%  
  mutate(names = ifelse(names == "total.bioav_accm_doc", "Long-term", "Short-term" )) %>% 
  ##PLOT
  ggplot(aes(x = degree_bin, y = values, fill = names, group = interaction(Season, Station, degree_bin)))  + 
  geom_bar(position = position_dodge(), stat = "identity", color = "black", alpha = 1) +
  labs(x = expression(italic("")), y = expression(italic(paste("Bioavailable DOC, µmol C L"^-1))), colour = expression(italic(""))) +
  scale_fill_manual(values = custom.colors) +
  scale_y_continuous(breaks = pretty_breaks()) +
  custom_theme() +
  facet_grid(~factor(Season, levels = levels), scales = "free") 
  #theme(strip.background = element_blank(), strip.text = element_blank()) +
  #guides(fill = F)

#percent bioav
bioav_doc.bar <- doc %>% 
  filter(!Cruise == "AT32") %>% 
  select(Season:Subregion, degree_bin, total.per_bioav, st.per_bioav) %>% 
  distinct() %>% 
  pivot_longer(cols = c(total.per_bioav, st.per_bioav), names_to = "names", values_to = "values") %>%  
  mutate(names = ifelse(names == "total.per_bioav", "Long-term", "Short-term" )) %>% 
  ##PLOT
  ggplot(aes(x = degree_bin, y =  values, fill = names, group = interaction(Season, Station, degree_bin)))  + 
  geom_bar(position = position_dodge(), stat = "identity", color = "black", alpha = 1) +
  labs(x = expression(italic("Latitude, ˚N")), y = expression(italic(paste("Bioavailable DOC, %"))), colour = expression(italic(""))) +
  scale_fill_manual(values = custom.colors) +
  scale_y_continuous(breaks = pretty_breaks()) +
  custom_theme() +
  facet_grid(~factor(Season, levels = levels), scales = "free") +
  theme(strip.background = element_blank(), strip.text = element_blank()) +
  guides(fill = F)


ddoc.bar / bioav_doc.bar

```


# Bar plots: BCD and BCD:NPP

We'll convert BCD and NPP to mmol C m^-3^ d^-1^ before plotting. 

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 12, fig.align = "center", warning = FALSE}
bcd.bar <- bcd %>% 
  select(Cruise:degree_bin, contains("int."), mew.global_i:bcd.npp.season_bge) %>% 
  distinct() %>% 
  mutate(bge = ifelse(Cruise == "AT39" & Station == 4, "!", NA),
         bge = ifelse(Cruise == "AT34" & Station %in% c(1, 2, 3), "!", bge),
         bge = ifelse(Cruise == "AT38" & Station %in% c(3, 6), "!", bge)) %>% 
  pivot_longer(cols = c(int.bcd.season_bge, int.bcd.global_bge), names_to = "names", values_to = "value") %>%  
  mutate(names = ifelse(names == "int.bcd.season_bge", "Season-specific BGE", "Global BGE"),
         degree_bin = as.character(degree_bin)) %>% 
  group_by(Cruise, Station) %>% 
  mutate(ave = mean(value)/10^3,
         sd = sd(value)/10^3) %>% 
  ungroup() %>% 
  ##PLOT
  ggplot(aes(x = degree_bin, y = ave, group = interaction(Season, Station, degree_bin)))  +
  geom_bar(position = position_dodge(), stat = "identity", color = "black", alpha = 1, fill = "#377EB8") +
  geom_errorbar(aes(ymin = ave - sd, ymax = ave + sd), position = position_dodge(width = 0.9), stat = "identity", width = 0.1, size = 0.5) +
  geom_text(aes(label = bge, y = ave + 0.1), position = position_dodge(width = 0.9), stat = "identity", size = 6, color = "#E41A1C") +
  labs(x = expression(italic("")), y = expression(italic(paste("BCD, mmol C m"^-3, "d"^-1))), colour = expression(italic(""))) +
  scale_y_continuous(breaks = pretty_breaks()) +
  custom_theme() +
  facet_grid(~factor(Season, levels = levels), scales = "free") 

bcd.npp.bar <- bcd %>% 
  select(Cruise:Station, degree_bin, int.NPP, sd_int.NPP, int.bcd.global_bge, int.bcd.season_bge) %>% 
  distinct() %>% 
   mutate(bge = ifelse(Cruise == "AT39" & Station == 4, "!", NA),
         bge = ifelse(Cruise == "AT34" & Station %in% c(1, 2, 3), "!", bge),
         bge = ifelse(Cruise == "AT38" & Station %in% c(3, 6), "!", bge)) %>% 
  pivot_longer(cols = c(int.NPP, int.bcd.global_bge, int.bcd.season_bge), names_to = "names", values_to = "value") %>%  
  mutate(names = ifelse(names %in% c("int.bcd.global_bge,", "int.bcd.season_bge"), "BCD", "NPP"),
         degree_bin = as.character(degree_bin),
         bge = ifelse(names == "BCD", NA, bge)) %>% 
  group_by(Cruise, Station, names) %>% 
  mutate(ave = mean(value)/10^3,
         sd = sd(value)/10^3,
         sd = ifelse(names == "NPP", sd_int.NPP/10^3, sd )) %>% 
  ungroup() %>% 
  ##PLOT
  ggplot(aes(x = degree_bin, fill = factor(names, levels = c("NPP", "BCD")), y =  ave, group = interaction(Season, Station, degree_bin)))  + 
  geom_bar(position = position_dodge(), stat = "identity", color = "black", alpha = 1) +
  geom_errorbar(aes(ymin = ave - sd, ymax = ave + sd), position = position_dodge(width = 0.9), stat = "identity", width = 0.1, size = 0.5) +
    geom_text(aes(label = bge, y = ave + 1), position = position_dodge(width = 0.9), stat = "identity", size = 6, color = "#E41A1C") +
  labs(x = expression(italic("")), y = expression(italic(paste("mmol C m"^-3, "d"^-1))), colour = expression(italic(""))) +
  scale_y_continuous(breaks = pretty_breaks()) +
  scale_fill_manual(values = custom.colors) +
  custom_theme() +
  facet_grid(~factor(Season, levels = levels), scales = "free") +
  theme(strip.background = element_blank(), strip.text = element_blank()) +
  theme(legend.position = "right",
        legend.title = element_blank()) 

ratio.bar <- bcd %>% 
  select(Cruise:Station, degree_bin, bcd.npp.global_bge, bcd.npp.season_bge ) %>% 
  distinct() %>% 
  mutate(bge = ifelse(Cruise == "AT39" & Station == 4, "!", NA),
         bge = ifelse(Cruise == "AT34" & Station %in% c(1, 2, 3), "!", bge),
         bge = ifelse(Cruise == "AT38" & Station %in% c(3, 6), "!", bge)) %>%  
  pivot_longer(cols = c(bcd.npp.global_bge, bcd.npp.season_bge), names_to = "names", values_to = "value") %>%  
  mutate(names = ifelse(names == "bcd.npp.global_bge", "Global BGE", "Season-specific BGE"),
         degree_bin = as.character(degree_bin)) %>% 
  group_by(Cruise, Station) %>% 
  mutate(ave = mean(value),
         sd = sd(value)) %>% 
  ungroup() %>% 
  ##PLOT
  ggplot(aes(x = degree_bin, y = ave, group = interaction(Season, Station, degree_bin)))  +
  geom_bar(position = position_dodge(), stat = "identity", color = "black", alpha = 1,  fill = "#999999") +
  geom_errorbar(aes(ymin = ave - sd, ymax = ave + sd), position = position_dodge(width = 0.9), stat = "identity", width = 0.1, size = 0.5) +
   geom_text(aes(label = bge, y = ave + 10), position = position_dodge(width = 0.9), stat = "identity", size = 6, color = "#E41A1C") +
  labs(x = expression(italic("Latitude, ˚N")), y = expression(italic(paste("BCD:NPP"))), colour = expression(italic(""))) +
  scale_y_continuous(breaks = pretty_breaks()) +
  custom_theme() +
  facet_grid(~factor(Season, levels = levels), scales = "free") +
  theme(strip.background = element_blank(), strip.text = element_blank())
  
bcd.bar / bcd.npp.bar / ratio.bar
```
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 6, fig.align = "center", warning = FALSE}
# δDOC
ddoc44.bar <- doc %>% 
  filter(!Cruise == "AT32", degree_bin == 44) %>% 
  select(Season:Subregion, degree_bin, total.bioav_accm_doc, st.bioav_accm_doc) %>% 
  distinct() %>% 
  pivot_longer(cols = c(total.bioav_accm_doc, st.bioav_accm_doc), names_to = "names", values_to = "values") %>%  
  mutate(names = ifelse(names == "total.bioav_accm_doc", "Long-term", "Short-term" )) %>% 
  ##PLOT
  ggplot(aes(x = factor(Season, levels = levels), y = values, fill = names, group = interaction(Season, Station, degree_bin)))  + 
  geom_bar(position = position_dodge(), stat = "identity", color = "black", alpha = 1, width = 0.5) +
  labs(x = expression(italic("")), y = expression(italic(paste("Bioavailable DOC, µmol C L"^-1))), colour = expression(italic(""))) +
  scale_fill_manual(values = custom.colors) +
  scale_y_continuous(breaks = pretty_breaks()) +
  custom_theme() 
  #facet_grid(~factor(Season, levels = levels), scales = "free") 
  #theme(strip.background = element_blank(), strip.text = element_blank()) +
  #guides(fill = F)

#percent bioav
bioav_doc44.bar <- doc %>% 
  filter(!Cruise == "AT32", degree_bin == 44) %>% 
  select(Season:Subregion, degree_bin, total.per_bioav, st.per_bioav) %>% 
  distinct() %>% 
  pivot_longer(cols = c(total.per_bioav, st.per_bioav), names_to = "names", values_to = "values") %>%  
  mutate(names = ifelse(names == "total.per_bioav", "Long-term", "Short-term" )) %>% 
  ##PLOT
  ggplot(aes(x = factor(Season, levels = levels), y =  values, fill = names, group = interaction(Season, Station, degree_bin)))  + 
  geom_bar(position = position_dodge(), stat = "identity", color = "black", alpha = 1, width = 0.5) +
  labs(x = expression(italic("")), y = expression(italic(paste("Bioavailable DOC, %"))), colour = expression(italic(""))) +
  scale_fill_manual(values = custom.colors) +
  scale_y_continuous(breaks = pretty_breaks()) +
  custom_theme() +
  #facet_grid(~factor(Season, levels = levels), scales = "free") +
  theme(strip.background = element_blank(), strip.text = element_blank()) +
  guides(fill = F)


ddoc44.bar / bioav_doc44.bar + plot_annotation(title = "44˚N")

```


# Merge DOC and BCD data

Here we merge the integrated and depth-normalized data. We'll also convert:

- BCD to mmol C m^-3^ d^-1^
- BC to mmol C m^-3^
- NPP to mmol C m^-3^ d^-1^


```{r message = F}

bcd_bioav <- bcd %>% 
  select(Cruise:degree_bin, int.bcd.season_bge, int.bcd.global_bge) %>% distinct() %>% 
  pivot_longer(cols = c(int.bcd.season_bge, int.bcd.global_bge), names_to = "var", values_to = "bcd") %>% 
  select(-var) %>% distinct() %>% 
  group_by(Cruise,Subregion, degree_bin, Station) %>% 
  summarise(ave_BCD = mean(bcd),
            sd_BCD = sd(bcd)) %>% ungroup() %>% 
  left_join(., bcd %>% 
              select(Cruise:degree_bin, int.bc.global_i:int.bc.season_s) %>% distinct() %>% 
              pivot_longer(cols = c(int.bc.global_i:int.bc.season_s), names_to = "var", values_to = "bc") %>% 
              select(-var) %>% distinct() %>% 
              group_by(Cruise,Subregion, degree_bin, Station) %>% 
              summarise(ave_BC = mean(bc),
                        sd_BC = sd(bc)) %>% ungroup()
  ) %>% 
  left_join(., bcd %>% 
              select(Cruise:degree_bin, mew.global_i:mew.season_s) %>% distinct() %>%
              pivot_longer(cols = c(mew.global_i:mew.season_s), names_to = "var", values_to = "mew") %>% 
              select(-var) %>% distinct() %>% 
              group_by(Cruise,Subregion, degree_bin, Station) %>%
              summarise(ave_mew = mean(mew),
                        sd_mew = sd(mew)) %>% 
              ungroup()
  ) %>% 
  left_join(., bcd %>% 
              select(Cruise:degree_bin, bcd.npp.global_bge, bcd.npp.season_bge) %>%
              distinct() %>%
              pivot_longer(cols = c(bcd.npp.global_bge, bcd.npp.season_bge), names_to = "var", values_to = "bcd.npp") %>% 
              select(-var) %>% distinct() %>% 
              group_by(Cruise,Subregion, degree_bin, Station) %>%
              summarise(ave_bcd.npp = mean(bcd.npp),
                        sd_bcd.npp = sd(bcd.npp)) %>% 
              ungroup()
  ) %>% 
  left_join(bcd %>% 
              select(Cruise:sd_Ez, int.bp:sd_int.ba, int.NPP:sd_int.NPP) %>%
              distinct(), 
            .) %>% 
  mutate(Station = as.character(Station)) %>% 
  left_join(., doc %>% 
              select(Cruise:Subregion, degree_bin, int_delta_DOC_ez, accm_doc:bge) %>%
              distinct() %>% 
              mutate(degree_bin = as.numeric(degree_bin))
            ) %>% 
  select(Cruise:ave_Ez, everything()) %>% 
  mutate_at(vars(int.NPP, int.NPP:sd_BC), funs(./1000))
```


# Regressions: Property-Property 

## ** BCD v NPP

```{r echo = FALSE}
reg1 <- lmodel2(ave_BCD ~ int.NPP, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg1
```

## BCD v Seasonally Accumulated DOC

```{r echo = FALSE}
reg2 <- lmodel2(ave_BCD ~ int_delta_DOC_ez, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg2
```


## BCD v % DOC Bioavailability

```{r echo = FALSE}
reg3 <- lmodel2(ave_BCD ~ total.per_bioav, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg3
```


```{r echo = FALSE}
reg4 <- lmodel2(ave_BCD ~ st.per_bioav, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg4
```

## BCD v DOC removal rate

```{r echo = FALSE}
reg5 <- lmodel2(ave_BCD ~ total.ddoc, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg5
```

```{r echo = FALSE}
reg6 <- lmodel2(ave_BCD ~ st.ddoc, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg6
```

## ** BCD:NPP v Seasonally Accumulated DOC

```{r echo = FALSE}
reg7 <- lmodel2(ave_bcd.npp ~ int_delta_DOC_ez, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg7
```


## ** BCD:NPP v % DOC Bioavailability

```{r echo = FALSE}
reg8 <- lmodel2(ave_bcd.npp ~ total.per_bioav, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg8
```


```{r echo = FALSE}
reg9 <- lmodel2(ave_bcd.npp ~ st.per_bioav, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg9
```

## BCD:NPP v % DOC removal rate

```{r echo = FALSE}
reg10 <- lmodel2(ave_bcd.npp ~ total.ddoc, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg10
```

```{r echo = FALSE}
reg11 <- lmodel2(ave_bcd.npp ~ st.ddoc, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg11
```

## ** µ v NPP 

```{r echo = FALSE}
reg12 <- lmodel2(ave_mew ~ int.NPP, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg12
```

## µ v Seasonally Accumulated DOC 

```{r echo = FALSE}
reg13 <- lmodel2(ave_mew ~ int_delta_DOC_ez, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg13
```

## µ v % DOC Bioavailability

```{r echo = FALSE}
reg14 <- lmodel2(ave_mew ~ total.per_bioav, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg14
```

```{r echo = FALSE}
reg15 <- lmodel2(ave_mew ~ st.per_bioav, data = bcd_bioav, nperm = 99)
```

```{r echo = FALSE}
reg15
```

# Plots: Property-Property

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 16, fig.align = "center", warning = FALSE}
reg1.plot <- bcd_bioav %>% 
  ggplot(aes(x = int.NPP, y = ave_BCD)) + 
  geom_abline(intercept = reg1$regression.results[3,2],
              slope = reg1$regression.results[3,3],colour = "black", linetype = 2, size = 1) +
  geom_errorbar(aes(color = factor(Season, levels = levels), ymin = ave_BCD - sd_BCD, ymax = ave_BCD + sd_BCD), width = 0.05) +
  geom_errorbarh(aes(color = factor(Season, levels = levels), xmin = int.NPP - sd_int.NPP, xmax = int.NPP + sd_int.NPP), height = 0.01) +
  geom_point( aes(fill = factor(Season, levels = levels)), shape = 21, color = "black", size = 4, alpha = 1) +
  labs(x = expression(italic(paste("NPP, mmol C m"^-3, "d"^-1))), y = expression(italic(paste("BCD, mmol C m"^-3, "d"^-1)))) +
  scale_fill_manual(values = custom.colors) +
  scale_color_manual(values = custom.colors) +
  custom_theme() +
  guides(color = F) +
  annotate( geom = "text", label = expression(atop("y = 0.17x + 0.07", paste("r"^2," = 0.71, ", italic("p "), "<< 0.01"))), x = 3.8, y = 0.08, size = 4) 
  
reg7.plot  <- bcd_bioav %>% 
  ggplot(aes(x = int_delta_DOC_ez, y = ave_bcd.npp)) + 
  geom_abline(intercept = reg7$regression.results[3,2],
              slope = reg7$regression.results[3,3],colour = "black", linetype = 2, size = 1) +
  geom_errorbar(aes(color = factor(Season, levels = levels), ymin = ave_bcd.npp - sd_bcd.npp, ymax = ave_bcd.npp + sd_bcd.npp), width = 0.02) +
  geom_point( aes(fill = factor(Season, levels = levels)), shape = 21, color = "black", size = 4, alpha = 1) +
  labs(x = expression(italic(paste("Seasonally Accumulated DOC, mol C m"^-2))), y = expression(italic(paste("BCD : NPP")))) +
  scale_fill_manual(values = custom.colors) +
  scale_color_manual(values = custom.colors) +
  custom_theme() +
  guides(color = F, fill = F) +
  annotate( geom = "text", label = expression(atop("y = 104.39x + 4.21", paste("r"^2," = 0.24, ", italic("p "), "= 0.02"))), x = 0.90, y = 15, size = 4) 

reg8.plot  <- bcd_bioav %>% 
  ggplot(aes(x = total.per_bioav, y = ave_bcd.npp)) + 
  geom_abline(intercept = reg8$regression.results[3,2],
              slope = reg8$regression.results[3,3],colour = "black", linetype = 2, size = 1) +
  geom_errorbar(aes(color = factor(Season, levels = levels), ymin = ave_bcd.npp - sd_bcd.npp, ymax = ave_bcd.npp + sd_bcd.npp), width = 0.05) +
  geom_point( aes(fill = factor(Season, levels = levels)), shape = 21, color = "black", size = 4, alpha = 1) +
  labs(x = expression(italic(paste("Long-term Bioavailability of Seasonally Accumulated DOC, %"))), y = expression(italic(paste("")))) +
  scale_fill_manual(values = custom.colors) +
  scale_color_manual(values = custom.colors) +
  custom_theme() +
  guides(color = F, fill = F) +
  annotate( geom = "text", label = expression(atop("y = 82.78x - 0.82", paste("r"^2," = 0.43, ", italic("p "), "= 0.03"))), x = 105, y = 112, size = 4) 

reg1.plot / (reg7.plot + reg8.plot)

```











