---
title: "BGE"
author: "Nicholas Baetge"
date: "5/20/2020"
output: github_document
---

# Intro

This document shows how processed **individual bottle** data from NAAMES remineralization bioassays were combined, QC'd, and analyzed. Here, we calculate derived variables, including BGE. 

```{r Packages, message = F, warning = F}
library(tidyverse) 
library(readxl)
library(zoo)
library(patchwork)
```


# Merge and Tidy Processed Data

```{r Import & merge & tidy, message = F, warning = F}

ba <- readRDS("~/GITHUB/naames_bioav_ms/Input/Bact_Abund_Input.rds") %>% 
  ungroup() %>% 
  group_by(Cruise, Station, Treatment, Timepoint) %>% 
  mutate(station_cells = mean(cells),
         sd_station_cells = sd(cells)) %>% 
  ungroup() %>% 
  select(Season:Station, Bottle:sd_cells, station_cells, sd_station_cells, p_cells:sd_p_cells) 
  
oc <- readRDS("~/GITHUB/naames_bioav_ms/Output/filt_processed_doc.rds") %>% 
  select(-c(Depth, Days, key:facet_bottle, doc_from_last:pdoc_from_t0)) 

bc <- readRDS("~/GITHUB/naames_bioav_ms/Output/filt_processed_bacterial_carbon.rds") %>% 
  select(-c(Depth, i.poc.cf1, s.poc.cf1, contains("ccf"), contains("cn"), contains("pon"))) %>% 
  rename(i.poc = i.poc.c1.um,
         s.poc = s.poc.c1.um) # gf75 POC corrected by subtracting universal blank (average of 0.2 and TFF filtrate)


merge <- full_join(ba, oc) %>% 
  left_join(., bc) %>% 
  arrange(Cruise, Station, Treatment, Bottle, Hours) %>%
  mutate(Days = round(Hours/24, 2)) %>% 
  drop_na(Hours) %>% 
  select(Cruise:Treatment, Hours, Days, everything()) %>% 
  group_by(Cruise, Station, Treatment, Bottle) %>% 
  mutate(s.timepoint = ifelse(s.timepoint == Timepoint, Hours, NA)) %>% 
  fill(s.timepoint, .direction = "downup") %>%
  ungroup() %>% 
  group_by(Cruise, Station, Treatment) %>% 
  fill(s.timepoint, .direction = "downup") %>%
  ungroup() %>% 
  rename(stationary.harvest = s.timepoint) %>% 
  select(Season, Cruise:Treatment, stationary.harvest, Hours, Days, everything()) %>% 
  select(-Timepoint) 

```

# Interpolations

## Split

```{r Interpolation split}
to_interpolate <- merge %>% 
  select(Cruise, Station, Treatment, Bottle, Hours, pdoc, doc, toc, ptoc) %>% 
  group_by(Cruise, Station, Treatment, Bottle) # first we'll define the grouping of our dataframe

list <- to_interpolate %>% 
  group_split()  #then we can convert the dataframe into a list, broken up by the groups (list elements)

keys <- to_interpolate %>% 
  group_keys() %>%
  mutate(key = paste(Cruise, Station, Treatment, Bottle, sep = "."))

names(list) <- keys$key

```

## Write the function

```{r Interpolation function, warning = FALSE}
interp.func <- function(x) {
  y <- zoo(x, order.by = x$Hours)
  interp_toc <- round(as.numeric(na.approx(y$toc, na.rm = F)), 1)
  interp_ptoc <- round(as.numeric(na.approx(y$ptoc, na.rm = F)), 1)
  interp_doc <- round(as.numeric(na.approx(y$doc, na.rm = F)), 1)
  interp_pdoc <- round(as.numeric(na.approx(y$pdoc, na.rm = F)), 1)
  z <- cbind(y,  interp_toc, interp_ptoc, interp_doc, interp_pdoc)
  as_tibble(z)
}
```

## Apply and Combine

```{r Interpolated df}
interpolated <- lapply(list, interp.func) %>% 
  plyr::ldply(., as.data.frame) %>% 
  select(-.id) %>% 
  mutate_at(vars(Hours:interp_pdoc), as.numeric) %>% 
  left_join(merge, .) %>% 
  group_by(Cruise, Station, Bottle) %>% 
  ungroup()
  
```


# Calculate Derived Variables

We need to readjust our initial bacterial carbon numbers before calculating other parameters. Since the initial condition was 1.2-µm filtrate, the carbon content of that filtrate would be higher than the 30:70 incubation mix at the beginning of the experiment. As a result we'll correct the initial carbon number to account for this: Bacterial POC~initial~ = 0.3 * Bacterial POC~1.2 µm filtrate~

We'll then calculate and define:

- doc.star = TOC or PTOC - POC (for N3 and 4)
- Bacterial growth efficiencies (BGE), only where ∆DOC is resolvable (>= 2.0 µmol C L^-1^ change):
  + ∆POC and ∆DOC (N2) or ∆DOC_star (N3) from T0 to stationary
  
```{r Calculate derived vars, message = F}
calcs <- interpolated %>%
  mutate_at(vars(i.poc), funs(.*0.3)) %>% 
  group_by(Cruise, Station, Treatment, Bottle) %>% 
######delta cells and poc ####
  mutate(del.cells = ifelse(Hours == stationary.harvest, cells - first(cells), NA),
         del.poc = round(s.poc - i.poc, 1)) %>% 
  fill(c(del.cells, del.poc), .direction = "downup") %>% 
#######toc and doc star###
  mutate(doc.star_i = ifelse(Cruise != "AT34" & Hours == 0, round(ptoc - i.poc, 1), NA),
         doc.star_s = ifelse(Cruise != "AT34" & Hours == stationary.harvest, round(interp_ptoc - s.poc, 1), NA)) %>% 
  fill(contains("star"), .direction = "downup") %>% 
######delta toc, toc.star, doc, doc.star####
  mutate(del.toc = ifelse(Cruise != "AT34" & Hours == stationary.harvest, first(ptoc) - interp_ptoc, NA),
         del.toc = ifelse(del.toc < 1.75, NA, del.toc),
         
         del.doc = ifelse(Cruise == "AT34" & Hours == stationary.harvest, first(doc) - interp_doc, NA),
         del.doc = ifelse(del.doc < 1.75, NA, del.doc),
         
         del.doc.star = doc.star_i - doc.star_s,
         del.doc.star = ifelse(del.doc.star < 1.75, NA, del.doc.star),
         del.doc.star = ifelse(del.toc < 1.75, NA, del.doc.star),
         ) %>% 
  fill(contains(c("del.toc", "del.doc")), .direction = "downup")  %>% 
  ######BGE####  
mutate(bge = ifelse(Cruise == "AT34", del.poc/del.doc, del.poc/del.doc.star),
       bge = ifelse(Cruise == "AT34" & Station == 3, NA, bge)) %>% #N2S3 omitted because poc change and cell change from data well beyond stationary (in death phase)
  mutate_at(vars(contains("bge")), round, 2) %>% 
  ungroup() %>% 
  arrange(factor(Season, levels = c("Early Spring", "Late Spring", "Early Autumn")))

```


# Summary Data, Table

```{r Summary table}
bge_summary <- calcs %>% 
    filter(Treatment == "Control") %>% 
  select(Season:Treatment, contains("del"), bge) %>% 
  distinct() 

bge_cruise_means <- bge_summary %>% 
 group_by(Cruise, Season) %>% 
  summarise_at(vars(del.cells:bge), list(mean = mean, sd = sd), na.rm = T) %>% 
  arrange(factor(Season, levels = c("Early Spring", "Late Spring", "Early Autumn")))

bge_station_means <- bge_summary %>% 
 group_by(Cruise, Season, Station) %>% 
  summarise_at(vars(del.cells:bge), list(mean = mean, sd = sd), na.rm = T) %>% 
  arrange(factor(Season, levels = c("Early Spring", "Late Spring", "Early Autumn")))

```

# Save Data

```{r Save, message = F}

saveRDS(calcs, "~/GITHUB/naames_bioav_ms/Output/processed_bge.rds")

saveRDS(bge_summary,  "~/GITHUB/naames_bioav_ms/Output/bge_summary.rds")

saveRDS(bge_cruise_means,  "~/GITHUB/naames_bioav_ms/Output/bge_cruise_means.rds")

saveRDS(bge_station_means,  "~/GITHUB/naames_bioav_ms/Output/bge_station_means.rds")


```



