---
title: "BGE"
author: "Nicholas Baetge"
date: "5/20/2020"
output: github_document
---

# Intro

This document shows how processed **individual bottle** data from NAAMES remineralization bioassays were combined, QC'd, and analyzed. Here, we calculate derived variables, including BGE. 

```{r message = F, warning = F}
library(tidyverse) 
library(rmarkdown)
library(knitr)
library(readxl)
library(data.table) 
library(scales)
library(zoo)
library(oce)
library(patchwork)
#rmarkdown tables
library(stargazer)
library(pander)
library(growthcurver)
#stat tests
library(lmtest)
library(lmodel2)
library(rstatix)
library(ggpubr)
```


```{r include = FALSE}
custom_theme <- function() {
  theme_test(base_size = 16) %+replace%
    theme(legend.position = "top",
          legend.title = element_blank(),
          legend.spacing.x = unit(0.5,"cm"),
          legend.background = element_rect(fill = "transparent",colour = NA),
          legend.key = element_rect(fill = "transparent",colour = NA),
          panel.background = element_rect(fill = "transparent",colour = NA),
          plot.background = element_rect(fill = "transparent",colour = NA),
          strip.text.x = element_text(size = 14, color = "white", face = "bold.italic"),
          strip.text.y = element_text(size = 14, color = "white", face = "bold.italic", angle = 270),
          strip.background = element_rect(color = "black", fill = "#005a9c", size = 0.5, linetype = "solid")) 
}

custom_theme_linedraw <- function() {
  theme_linedraw(base_size = 16) %+replace%
    theme(legend.position = "top",
          legend.title = element_blank(),
          legend.spacing.x = unit(0.5,"cm"),
          legend.background = element_rect(fill = "transparent",colour = NA),
          legend.key = element_rect(fill = "transparent",colour = NA),
          panel.background = element_rect(fill = "transparent",colour = NA),
          plot.background = element_rect(fill = "transparent",colour = NA),
          strip.text.x = element_text(size = 14, color = "white", face = "bold.italic"),
          strip.text.y = element_text(size = 14, color = "white", face = "bold.italic", angle = 270),
          strip.background = element_rect(color = "black", fill = "#005a9c", size = 0.5, linetype = "solid")) 
}

custom.colors <- c("AT39" = "#377EB8", "AT34" = "#4DAF4A", "AT38" = "#E41A1C", "AT32" = "#FF7F00", "Temperate" = "#A6CEE3", "Subpolar" = "#377EB8", "Subtropical" = "#FB9A99", "GS/Sargasso" = "#E41A1C", "Early Spring" = "#377EB8", "Late Spring" = "#4DAF4A","Early Autumn" = "#E41A1C", "Summer" = "#E41A1C", "Late Autumn" = "#FF7F00", "A" = "#E41A1C", "B" = "#377EB8", "C" = "#4DAF4A", "D" = "#FF7F00", "E" = "#FDB927", "F" = "#552583", "G" = "#FDB927", "H" = "#552583",   "Control" = "#E41A1C", "TW12" = "#377EB8", "T. Weissflogii 12C Exudate" = "#377EB8", "TW13" = "#4DAF4A", "T. Weissflogii 13C Exudate" = "#4DAF4A", "MixDS" = "#377EB8", "Deep Comm., Surface DOM" = "#377EB8","MixSD" = "#4DAF4A", "Surface Comm., Deep DOM" = "#4DAF4A", "SynLys" = "#377EB8", "Synechococcus Lysate" = "#377EB8", "SynExd" = "#4DAF4A", "Synechococcus Exudate" = "#4DAF4A", "TWExd" = "#FF7F00", "T. Weissflogii Exudate" = "#FF7F00", "TW5" = "#377EB8", "TW10" = "#4DAF4A", "TW20" = "#FF7F00", "Parallel" = "#377EB8", "W" = "#552583", "Whole Seawater" = "#552583", "1.2" = "#4DAF4A", "1.2 µm Filtrate" = "#4DAF4A", "NV" = "#FF7F00", "1.2 µm Filtrate: TFF Filtrate (3:7)" = "#FF7F00", "Carbon" = "#E41A1C", "Nitrogen" = "#377EB8", "+5 µmol C/L Exudate" = "#FF7F00", "+10 µmol C/L Exudate" = "#FF7F00", "+20 µmol C/L Exudate" = "#FF7F00", "Filter 1" = "#E41A1C", "Filter 2" = "#377EB8", "10 m" = "#E41A1C", "200 m" = "#377EB8", "BCD" = "#377EB8" , "NPP" = "#4DAF4A" , "Cruise Specific BGE" = "#377EB8", "Global BGE" = "#4DAF4A") 

custom.shapes <- c("Early Spring" = 21, "Late Spring" = 22,"Early Autumn" = 23)

custom.lines <- c("GS/Sargasso" = "blank", "Subtropical" = "solid", "Temperate" = "longdash", "Subpolar" = "dotted" )


levels = c("GS/Sargasso", "Subtropical", "Temperate", "Subpolar",  "AT39-6", "AT34", "AT38", "AT32","South", "North", "Early Spring", "Late Spring","Early Autumn",  "Summer", "Late Autumn", "Control", "Parallel", "SynLys", "SynExd", "TWExd", "MixSD", "MixDS", "TW12", "TW13", "TW5", "TW10", "TW20",  "Surface Comm., Deep DOM", "Deep Comm., Surface DOM", "Synechococcus Exudate", "Synechococcus Lysate", "T. Weissflogii Exudate", "T. Weissflogii 12C Exudate", "T. Weissflogii 13C Exudate", "+5 µmol C/L Exudate", "+10 µmol C/L Exudate","+20 µmol C/L Exudate", "A", "B", "C", "D", "E", "F", "G", "H", "I", "J", "K", "L", "M", "N", "O", "P", "W", "Whole Seawater","1.2", "1.2 µm Filtrate","NV", "1.2 µm Filtrate: TFF Filtrate (3:7)")

bge_lvls <- c("p2p, POC", 
              "p2p, POC c1", 
              "p2p, POC c2", 
              "p2p, POC c3", 
              "p2p, CCF c1", 
              "ph2ph, CCF c1", 
              "p2p, CCF c2", 
              "ph2ph, CCF c2", 
              "p2p, CCF c3", 
              "ph2ph, CCF c3", 
              "p2p, White CCF", 
              "ph2ph, White CCF", 
              "p2p, Fukuda CCF", 
              "ph2ph, Fukuda CCF", 
              "p2p, Lee CCF", 
              "ph2ph, Lee CCF", 
              "p2p, Dyn. White_Fukuda CCF", 
              "ph2ph, Dyn. White_Fukuda CCF", 
              "p2p, Dyn. White_Lee CCF", 
              "ph2ph, Dyn. White_Lee CCF" )

bge_lvls2 <- c("POC", 
              "POC c1", 
              "POC c2", 
              "POC c3", 
              "CCF c1", 
              "CCF c2", 
              "CCF c3",
              "Fukuda CCF", 
              "Lee CCF")

```

# Merge Processed Data

```{r message = F, warning = F}

ba <- readRDS("~/naames_bioav_ms/Output/processed_bacterial_abundance.rds") %>% 
  mutate(key = paste(Cruise, Station, Depth, Treatment, Bottle, Timepoint, sep = "."),
         Depth = as.numeric(Depth)) %>% 
  filter(!Treatment %in% c("GF75", "Niskin", "TFF-Ret", "Volume", "Parallel"))

oc <- readRDS("~/naames_bioav_ms/Output/processed_doc.rds") %>% 
  select(-Days) %>% 
  filter(!Treatment == "Parallel")

bc <- readRDS("~/naames_bioav_ms/Output/processed_bacterial_carbon.rds") %>% 
  select(-c(contains(".ug"), contains("gf75.cells"))) 


merge <- full_join(ba, oc) %>% 
  left_join(., bc) %>% 
  arrange(Cruise, Station, Depth, Treatment, Bottle, Hours) %>%
  mutate(Days = round(Hours/24, 2)) %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle) %>%
  select(Season:Depth, facet_depth,  Treatment, facet_treatment, Bottle, facet_bottle, Timepoint, Hours, stationary, s.timepoint, Days, cells:sd_p_cells, doc, sd_doc, ptoc, sd_ptoc, doc_from_t0, ptoc_from_t0, gf75.flag, i.poc.cf1:i.ccf.c3, s.poc.cf1:s.ccf.c3, ccf.white:ccf.lee) %>% 
  fill(stationary, facet_treatment, facet_depth, facet_bottle, .direction = "downup") %>% 
  ungroup() %>% 
  drop_na(Hours) 

```


# Tidy and Wrangle

## Condense DOC Data

Because DOC and TOC samples are essentially the same in this dataset, we will treat them as such. We'll use the DOC samples from AT34 and the parallel TOC samples from AT38 and AT39.

```{r}
tidy_merge <- merge %>% 
  mutate(ptoc = ifelse(Cruise == "AT34", doc, ptoc),
         sd_ptoc = ifelse(Cruise == "AT34", sd_doc, sd_ptoc),
         ptoc_from_t0 = ifelse(Cruise == "AT34", doc_from_t0, ptoc_from_t0)) %>% 
  select(-c(p_cells, sd_p_cells, doc, sd_doc, doc_from_t0)) %>% 
  rename(doc = ptoc,
         sd_doc = sd_ptoc,
         doc_from_t0 = ptoc_from_t0) %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle) %>% 
  mutate(s.timepoint = ifelse(s.timepoint == Timepoint, Hours, NA)) %>% 
  fill(s.timepoint, .direction = "downup") %>% 
  rename(s.gf75 = s.timepoint) %>% 
  select(-Timepoint) %>% 
  # merge duplicate stationary timepoints
  group_by(Cruise, Station, Depth, Treatment, Bottle, Hours) %>%
  fill(cells:doc_from_t0, i.poc.cf1:ccf.lee, .direction = "downup") %>% 
  distinct() %>% 
  ungroup() %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle) 
```

## Add 7 and 30 Day Timepoints

If experiments do not already have these timepoints, they will be added and then interpolated. These timepoints will be markers for short-term and long-term DOC bioavailability.

```{r}
tidy_merge_keys <- tidy_merge %>% 
  group_keys() %>%
  mutate(key = paste(Cruise, ", S", Station, ", Z =", Depth, ",", Treatment, ",", Bottle))
tidy_merge_header <- tidy_merge_keys$key

tidy_merge_list <- tidy_merge %>%
  group_split()
names(tidy_merge_list) <- tidy_merge_header

two_newrow.func <- function(morty){
   morty[nrow(morty) + 1,] <- NA
   morty$Days[is.na(morty$Days)] <- 7
  rick <- morty %>% 
    fill(., Season:facet_bottle, stationary:s.gf75, .direction = c("updown")) 
  
   rick[nrow(rick) + 1,] <- NA
  rick$Days[is.na(rick$Days)] <- 30
  summer <- rick %>% 
    fill(., Season:facet_bottle, stationary:s.gf75, .direction = c("updown")) 
}

add_tidy_merge <- lapply(tidy_merge_list, two_newrow.func) %>% 
  plyr::ldply(., as.data.frame) %>% 
  select(-.id) %>% 
  arrange(Cruise, Station, Depth, Treatment, Bottle, Days) %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle, Days) %>%
  fill(Hours, gf75.flag, cells:doc_from_t0, i.poc.cf1:ccf.lee, .direction = "downup") %>% 
  distinct() %>% 
  ungroup() %>% 
  mutate(Hours = ifelse(Days == 30, 720, Hours ),
         Hours = ifelse(Days == 7, 168, Hours )) %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle)  

add_tidy_merge_keys <- add_tidy_merge %>% 
  group_keys() %>%
  mutate(key = paste(Cruise, ", S", Station, ", Z =", Depth, ",", Treatment, ",", Bottle))
add_tidy_merge_header <- add_tidy_merge_keys$key

add_tidy_merge_list <- add_tidy_merge %>%
  group_split()
names(add_tidy_merge_list) <- add_tidy_merge_header
```

## Interpolations

```{r warning = FALSE}
interp.func <- function(x) {
  y <- zoo(x, order.by = x$Hours)
  interp_cells <- round(as.numeric(na.approx(y$cells, na.rm = F)))
  interp_doc <- round(as.numeric(na.approx(y$doc, na.rm = F)), 1)
  z <- cbind(y, interp_cells,  interp_doc)
  as_tibble(z)
}

interpolated <- lapply(add_tidy_merge_list, interp.func) %>% 
  plyr::ldply(., as.data.frame) %>% 
  select(-.id) %>% 
  mutate_at(vars(Depth, Hours:doc_from_t0, i.poc.cf1:interp_doc), as.numeric) %>% 
  select(Season:doc_from_t0, interp_cells, interp_doc, everything())
```

# Calculate Derived Variables

We need to readjust our initial bacterial carbon numbers before calculating other parameters. Since the initial condition was 1.2-µm filtrate, the carbon content of that filtrate would be higher than the 30:70 incubation mix at the beginning of the experiment. As a result we'll correct the initial carbon number to account for this: POC~initial~ = 0.3(POC~1.2 µm filtrate~)

We'll then calculate and define:

- Division rates (**r**) between each timepoint (Monod 1949). We assume all cells are viable. 
- Duration of lag, log, stationary phases based on calculated division rates and timing of stationary determined via GrowthCurver
  + lag phase ends when r > 0.01 (Yates and Smotzer 2007)
  + we've already filtered out the death phases so the stationary phase runs from the GrowthCurver model determined timepoint until cell counts cease
  + we do not determine growth phases where there is no observable growth
- Carrying Capacity (**k**), mean of cell abundance during stationary
- Exponential growth rate day^-1^
- Cell carbon in µmol C L^-1^, using different CCFS 
- Bacterial growth efficiencies (BGE) using multiple approaches, only where ∆DOC is resolvable:
  + point-to-point (**BGE_p**), ∆BC and ∆DOC from T0 to stationary
  + phase-to-phase (**BGE_ph**), ∆BC and ∆DOC using means of lag phase and stationary phase values
  
```{r message = F}
calcs <- interpolated %>%
  mutate_at(vars( i.poc.cf1:i.pon.c3.um), funs(.*0.3)) %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle) %>% 
  
  #####division rates#### 
  mutate(r = round((log(interp_cells) - lag(log(interp_cells)))/(Hours - lag(Hours)), 2),
         r = ifelse(Hours == 0, 0, r)) %>% 
  
  ######cell growth phases####
  mutate(cell_div = ifelse(Hours >= stationary & !is.na(interp_cells), "stationary", NA),
         cell_div = ifelse(Hours > stationary & is.na(cell_div), "out of bounds", cell_div),
         cell_div = ifelse(Hours < stationary & r > 0.01, "exponential", cell_div)) %>% 
  fill(cell_div, .direction = "down") %>% 
  mutate(cell_div = ifelse(Hours < stationary & r == 0 & is.na(cell_div), "lag", cell_div)) %>% 
  fill(cell_div, .direction = "down") %>% 
  mutate(growth = ifelse(cell_div == "stationary" | cell_div == "exponential", cell_div, NA)) %>%
  fill(growth, .direction = "downup") %>% 
  mutate(growth = ifelse(growth == "stationary" | growth == "exponential", T, F),
         growth = ifelse(is.na(growth), F, growth),
         cell_div = ifelse(growth == F, "no growth", cell_div)) %>% 
  fill(growth, .direction = "downup") %>% 
  fill(interp_cells, .direction = "down") %>% 
  mutate(interp_cells = ifelse(Days > 24, NA, interp_cells)) %>% 
  
  ###### carrying capacity ######
  mutate(k = ifelse(cell_div == "stationary", interp_cells, NA),
         k = ifelse(!is.na(k), mean(k, na.rm = T), NA)) %>% 
  
  #####exponential growth rate#####
  mutate(end_lag_t = ifelse(cell_div == "lag", Hours, NA),
         end_lag_t = ifelse(!is.na(end_lag_t), max(end_lag_t, na.rm = T), NA),
         end_lag_cells = ifelse(Hours == end_lag_t, interp_cells, NA),
         beg_stat_cells = ifelse(Hours == stationary, interp_cells, NA)) %>% 
  fill(k:beg_stat_cells, .direction = "downup") %>% 
  mutate(mew = ifelse(!is.na(end_lag_cells), ((log(beg_stat_cells) - log(end_lag_cells))/(stationary - end_lag_t)) * 24, NA )) %>% 
 
  ######cell carbon based on CCFs, points####
  mutate(i.cells = ifelse(Hours == 0, cells, NA)) %>% 
  fill(i.cells, .direction = "updown") %>% 
  mutate(delta_cells = interp_cells - i.cells,
         s.delta_cells = ifelse(Hours == stationary & stationary != 0 & growth == T, delta_cells, NA)) %>% 
  fill(s.delta_cells, .direction = "updown") %>% 
  mutate(norm_cells = ifelse(!is.na(s.delta_cells), round(delta_cells/s.delta_cells,2), NA)) %>% 
  rename(weight = norm_cells) %>% 
  mutate(dyn.ccf.white_fukuda = round(ccf.white + (weight * (ccf.fukuda - ccf.white)),1),
         dyn.ccf.white_lee = round(ccf.white + (weight * (ccf.lee - ccf.white)),1),
         i.bc.ccf.c1 =  ifelse(cell_div %in% c("lag", "exponential", "stationary"), round((interp_cells * i.ccf.c1) / (12*10^9), 1), NA), 
         i.bc.ccf.c2 =  ifelse(cell_div %in% c("lag", "exponential", "stationary"), round((interp_cells * i.ccf.c2) / (12*10^9), 1), NA), 
         i.bc.ccf.c3 =  ifelse(cell_div %in% c("lag", "exponential", "stationary"), round((interp_cells * i.ccf.c3) / (12*10^9), 1), NA), 
         s.bc.ccf.c1 =  ifelse(cell_div %in% c("lag", "exponential", "stationary"), round((interp_cells * s.ccf.c1) / (12*10^9), 1), NA), 
         s.bc.ccf.c2 =  ifelse(cell_div %in% c("lag", "exponential", "stationary"), round((interp_cells * s.ccf.c2) / (12*10^9), 1), NA), 
         s.bc.ccf.c3 =  ifelse(cell_div %in% c("lag", "exponential", "stationary"), round((interp_cells * s.ccf.c3) / (12*10^9), 1), NA), 
         bc.ccf.white =  ifelse(cell_div %in% c("lag", "exponential", "stationary"), round((interp_cells * ccf.white) / (12*10^9), 1), NA), 
         bc.ccf.fukuda =  ifelse(cell_div %in% c("lag", "exponential", "stationary"), round((interp_cells * ccf.fukuda) / (12*10^9), 1), NA), 
         bc.ccf.lee =  ifelse(cell_div %in% c("lag", "exponential", "stationary"), round((interp_cells * ccf.lee) / (12*10^9), 1), NA), 
         bc.dyn.ccf.white_fukuda =  ifelse(cell_div %in% c("lag", "exponential", "stationary"), round((interp_cells * dyn.ccf.white_fukuda) / (12*10^9), 1), NA), 
         bc.dyn.ccf.white_lee =  ifelse(cell_div %in% c("lag", "exponential", "stationary"), round((interp_cells * dyn.ccf.white_lee) / (12*10^9), 1), NA)) %>% 
  ungroup() %>% 
  
  ######cell carbon based on CCFs, phase averages####
  group_by(Cruise, Station, Depth, Treatment, Bottle, cell_div) %>% 
  mutate(ph.i.bc.ccf.c1 = ifelse(!cell_div %in% c("no growth", "out of bounds"), round(mean(i.bc.ccf.c1, na.rm = T), 1), NA),
         ph.i.bc.ccf.c2 = ifelse(!cell_div %in% c("no growth", "out of bounds"), round(mean(i.bc.ccf.c2, na.rm = T), 1), NA),
         ph.i.bc.ccf.c3 = ifelse(!cell_div %in% c("no growth", "out of bounds"), round(mean(i.bc.ccf.c3, na.rm = T), 1), NA),
         ph.s.bc.ccf.c1 = ifelse(!cell_div %in% c("no growth", "out of bounds"), round(mean(s.bc.ccf.c1, na.rm = T), 1), NA),
         ph.s.bc.ccf.c2 = ifelse(!cell_div %in% c("no growth", "out of bounds"), round(mean(s.bc.ccf.c2, na.rm = T), 1), NA),
         ph.s.bc.ccf.c3 = ifelse(!cell_div %in% c("no growth", "out of bounds"), round(mean(s.bc.ccf.c3, na.rm = T), 1), NA),
         ph.bc.ccf.white = ifelse(!cell_div %in% c("no growth", "out of bounds"), round(mean(bc.ccf.white, na.rm = T), 1), NA),
         ph.bc.ccf.fukuda = ifelse(!cell_div %in% c("no growth", "out of bounds"), round(mean( bc.ccf.fukuda, na.rm = T), 1), NA),
         ph.bc.ccf.lee = ifelse(!cell_div %in% c("no growth", "out of bounds"), round(mean(bc.ccf.lee, na.rm = T), 1), NA),
         ph.bc.dyn.ccf.white_fukuda =  ifelse(!cell_div %in% c("no growth", "out of bounds"), round(mean(bc.dyn.ccf.white_fukuda, na.rm = T), 1), NA),
         ph.bc.dyn.ccf.white_lee = ifelse(!cell_div %in% c("no growth", "out of bounds"), round(mean(bc.dyn.ccf.white_lee, na.rm = T), 1), NA),
         
  ######DOC, phase averages####
         ph.doc = ifelse(!cell_div %in% c("no growth", "out of bounds"), round(mean(interp_doc, na.rm = T), 1), NA)
         ) %>% 
  ungroup() %>% 
  
  ######delta cell carbon, points####
  group_by(Cruise, Station, Depth, Treatment, Bottle) %>% 
  fill(ph.i.bc.ccf.c1:ph.doc, .direction = "down") %>%
  mutate(del.bc.poc = s.poc.um - i.poc.um,
         del.bc.poc.c1 = s.poc.c1.um - i.poc.c1.um,
         del.bc.poc.c2 = s.poc.c2.um - i.poc.c2.um,
         del.bc.poc.c3 = s.poc.c3.um - i.poc.c3.um,
         del.bc.p.ccf.c1 = ifelse(Hours == stationary, s.bc.ccf.c1, NA) - first(i.bc.ccf.c1),
         del.bc.p.ccf.c2 = ifelse(Hours == stationary, s.bc.ccf.c2, NA) - first(i.bc.ccf.c2),
         del.bc.p.ccf.c3 = ifelse(Hours == stationary, s.bc.ccf.c3, NA) - first(i.bc.ccf.c3),
         del.bc.p.ccf.white = ifelse(Hours == stationary, bc.ccf.white, NA) - first(bc.ccf.white),
         del.bc.p.ccf.fukuda = ifelse(Hours == stationary, bc.ccf.fukuda, NA) - first(bc.ccf.fukuda),
         del.bc.p.ccf.lee = ifelse(Hours == stationary, bc.ccf.lee, NA) - first(bc.ccf.lee),
         del.bc.p.dyn.ccf.white_fukuda = ifelse(Hours == stationary, bc.dyn.ccf.white_fukuda, NA) - first(bc.dyn.ccf.white_fukuda),
         del.bc.p.dyn.ccf.white_lee = ifelse(Hours == stationary, bc.dyn.ccf.white_lee, NA) - first(bc.dyn.ccf.white_lee),
         
  ######delta cell carbon, phase averages####       
         del.bc.ph.ccf.c1 = ifelse(Hours == stationary, ph.s.bc.ccf.c1, NA) - first(ph.i.bc.ccf.c1),
         del.bc.ph.ccf.c2 = ifelse(Hours == stationary, ph.s.bc.ccf.c2, NA) - first(ph.i.bc.ccf.c2),
         del.bc.ph.ccf.c3 = ifelse(Hours == stationary, ph.s.bc.ccf.c3, NA) - first(ph.i.bc.ccf.c3),
         del.bc.ph.ccf.white = ifelse(Hours == stationary, ph.bc.ccf.white, NA) - first(ph.bc.ccf.white),
         del.bc.ph.ccf.fukuda = ifelse(Hours == stationary, ph.bc.ccf.fukuda, NA) - first(ph.bc.ccf.fukuda),
         del.bc.ph.ccf.lee = ifelse(Hours == stationary, ph.bc.ccf.lee, NA) - first(ph.bc.ccf.lee),
         del.bc.ph.dyn.ccf.white_fukuda = ifelse(Hours == stationary, ph.bc.dyn.ccf.white_fukuda, NA) - first(ph.bc.dyn.ccf.white_fukuda),
         del.bc.ph.dyn.ccf.white_lee = ifelse(Hours == stationary, ph.bc.dyn.ccf.white_lee, NA) - first(ph.bc.dyn.ccf.white_lee),
  
  ######delta DOC####  
         del.ph.doc = first(ph.doc) - last(ph.doc),
         del.doc = first(doc) - ifelse(Hours == stationary, interp_doc, NA),
         ) %>% 
  fill(del.bc.p.ccf.c1:del.doc, .direction = "downup") %>% 
  mutate(del.ph.doc.flag = ifelse(del.ph.doc >= 1.5, "Acceptable", "NR"),
         del.doc.flag = ifelse(del.doc >= 1.5, "Acceptable", "NR"),
         
  ######BGE, points####  
         bge.bc.poc = ifelse(del.doc.flag != "NR", del.bc.poc/(del.doc + del.bc.poc), NA),
         bge.bc.poc.c1 = ifelse(del.doc.flag != "NR", del.bc.poc.c1/(del.doc + del.bc.poc.c1), NA),
         bge.bc.poc.c2 = ifelse(del.doc.flag != "NR", del.bc.poc.c2/(del.doc + del.bc.poc.c2), NA),
         bge.bc.poc.c3 = ifelse(del.doc.flag != "NR", del.bc.poc.c3/(del.doc + del.bc.poc.c3), NA),
         bge.p.bc.ccf.c1 = ifelse(del.doc.flag != "NR", del.bc.p.ccf.c1/(del.doc + del.bc.p.ccf.c1), NA),
         bge.p.bc.ccf.c2 = ifelse(del.doc.flag != "NR", del.bc.p.ccf.c2/(del.doc + del.bc.p.ccf.c2), NA),
         bge.p.bc.ccf.c3 = ifelse(del.doc.flag != "NR", del.bc.p.ccf.c3/(del.doc + del.bc.p.ccf.c3), NA),
         bge.p.bc.ccf.white = ifelse(del.doc.flag != "NR", del.bc.p.ccf.white/(del.doc + del.bc.p.ccf.white), NA),
         bge.p.bc.ccf.fukuda = ifelse(del.doc.flag != "NR", del.bc.p.ccf.fukuda/(del.doc +  del.bc.p.ccf.fukuda), NA),
         bge.p.bc.ccf.lee = ifelse(del.doc.flag != "NR", del.bc.p.ccf.lee/(del.doc + del.bc.p.ccf.lee), NA),
         bge.p.bc.dyn.ccf.white_fukuda = ifelse(del.doc.flag != "NR", del.bc.p.dyn.ccf.white_fukuda/(del.doc + del.bc.p.dyn.ccf.white_fukuda), NA),
         bge.p.bc.dyn.ccf.white_lee = ifelse(del.doc.flag != "NR", del.bc.p.dyn.ccf.white_lee/(del.doc + del.bc.p.dyn.ccf.white_lee), NA),
  
  ######BGE, phase averages####  
         bge.ph.bc.ccf.c1 = ifelse(del.ph.doc.flag != "NR", del.bc.ph.ccf.c1/(del.ph.doc + del.bc.ph.ccf.c1), NA),
         bge.ph.bc.ccf.c2 = ifelse(del.ph.doc.flag != "NR", del.bc.ph.ccf.c2/(del.ph.doc + del.bc.ph.ccf.c2), NA),
         bge.ph.bc.ccf.c3 = ifelse(del.ph.doc.flag != "NR", del.bc.ph.ccf.c3/(del.ph.doc + del.bc.ph.ccf.c3), NA),
         bge.ph.bc.ccf.white = ifelse(del.ph.doc.flag != "NR", del.bc.ph.ccf.white/(del.ph.doc + del.bc.ph.ccf.white), NA),
         bge.ph.bc.ccf.fukuda = ifelse(del.ph.doc.flag != "NR", del.bc.ph.ccf.fukuda/(del.ph.doc + del.bc.ph.ccf.fukuda), NA),
         bge.ph.bc.ccf.lee = ifelse(del.ph.doc.flag != "NR", del.bc.ph.ccf.lee/(del.ph.doc + del.bc.ph.ccf.lee), NA),
         bge.ph.bc.dyn.ccf.white_fukuda = ifelse(del.ph.doc.flag != "NR", del.bc.ph.dyn.ccf.white_fukuda/(del.ph.doc + del.bc.ph.dyn.ccf.white_fukuda), NA),
         bge.ph.bc.dyn.ccf.white_lee = ifelse(del.ph.doc.flag != "NR", del.bc.ph.dyn.ccf.white_lee/(del.ph.doc + del.bc.ph.dyn.ccf.white_lee), NA)
         ) %>% 
  ###########
  ungroup() %>% 
  mutate_at(vars(bge.bc.poc:bge.ph.bc.dyn.ccf.white_lee), round, 2) %>% 
 
  #add metadata
  left_join(., readRDS("~/naames_export_ms/Output/processed_export_for_bioavMS.5.14.20.rds") %>% 
              mutate(Cruise = gsub("AT39-6", "AT39", Cruise)) %>%
              mutate_at(vars(Station), as.character) %>% 
              select(Cruise:Subregion) %>% 
              distinct()
  )
```



# Summary Data, Table, and Plots

```{r}
bge_summary <- calcs %>% 
  select(Season:Station, ave_lat:Subregion, Depth:facet_bottle, stationary:s.gf75, gf75.flag, del.doc, del.doc.flag, del.ph.doc, del.ph.doc.flag, del.bc.poc:del.bc.ph.dyn.ccf.white_lee, bge.bc.poc:bge.ph.bc.dyn.ccf.white_lee, i.cn:i.cn.c3, s.cn:s.cn.c3) %>% 
  distinct() %>% 
  mutate(type = ifelse(Treatment == "Control", "Control", "Non-Control"),
         degree_bin = ifelse(Station %in% c("S2RD", "S2RF"), 39, degree_bin),
         Subregion = ifelse(Station %in% c("S2RD", "S2RF"), "GS/Sargasso", Subregion)) %>% 
  select(Season:Treatment, type, everything()) %>% 
  arrange(Cruise, Station, Depth, Treatment, Bottle) %>% 
  #remove outliers
  filter(!Cruise == "AT38" | !Station == 1 | !Depth == 10 | !Treatment == "Control",
         !Cruise == "AT39" | !Station == 1 | !Depth == 10 | !Treatment == "Control") %>% 
   filter(!Station == "U", Depth == 10)
```



```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 18, fig.align = "center", warning = FALSE}

#########delta bc######

del_bc.plot <- bge_summary %>% 
  select(Season:gf75.flag, contains("del.bc"))  %>% 
  distinct() %>% 
  pivot_longer(contains("bc"), names_to = "key", values_to = "del.bc") %>% 
  mutate(appr = key,
         appr = ifelse(appr == "del.bc.poc", "p2p, POC", appr),
         appr = ifelse(appr == "del.bc.poc.c1", "p2p, POC c1", appr),
         appr = ifelse(appr == "del.bc.poc.c2", "p2p, POC c2", appr),
         appr = ifelse(appr == "del.bc.poc.c3", "p2p, POC c3", appr),
         appr = ifelse(appr == "del.bc.p.ccf.c1", "p2p, CCF c1", appr),
         appr = ifelse(appr == "del.bc.p.ccf.c2", "p2p, CCF c2", appr),
         appr = ifelse(appr == "del.bc.p.ccf.c3", "p2p, CCF c3", appr),
         appr = ifelse(appr == "del.bc.p.ccf.white", "p2p, White CCF", appr),
         appr = ifelse(appr == "del.bc.p.ccf.fukuda", "p2p, Fukuda CCF", appr),
         appr = ifelse(appr == "del.bc.p.ccf.lee", "p2p, Lee CCF", appr),
         appr = ifelse(appr == "del.bc.p.dyn.ccf.white_fukuda", "p2p, Dyn. White_Fukuda CCF", appr),
         appr = ifelse(appr == "del.bc.p.dyn.ccf.white_lee", "p2p, Dyn. White_Lee CCF", appr),
         appr = ifelse(appr == "del.bc.ph.ccf.c1", "ph2ph, CCF c1", appr),
         appr = ifelse(appr == "del.bc.ph.ccf.c2", "ph2ph, CCF c2", appr),
         appr = ifelse(appr == "del.bc.ph.ccf.c3", "ph2ph, CCF c3", appr),
         appr = ifelse(appr == "del.bc.ph.ccf.white", "ph2ph, White CCF", appr),
         appr = ifelse(appr == "del.bc.ph.ccf.fukuda", "ph2ph, Fukuda CCF", appr),
         appr = ifelse(appr == "del.bc.ph.ccf.lee", "ph2ph, Lee CCF", appr),
         appr = ifelse(appr == "del.bc.ph.dyn.ccf.white_fukuda", "ph2ph, Dyn. White_Fukuda CCF", appr),
         appr = ifelse(appr == "del.bc.ph.dyn.ccf.white_lee", "ph2ph, Dyn. White_Lee CCF", appr),
         p = appr) %>% 
  separate(., p, into = c("points", "ccf"), sep = "," ) %>% 
  group_by(Cruise, type, appr) %>% 
  add_tally() %>% 
  ungroup() %>% 
  #remove outliers
  filter(!Cruise == "AT38" | !Station == 1 | !Depth == 10 | !Treatment == "Control",
         !Cruise == "AT39" | !Station == 1 | !Depth == 10 | !Treatment == "Control") %>% 
  filter(!Station == "U", Depth == 10, points == "p2p", !key %in% c("del.bc.p.dyn.ccf.c1", "del.bc.p.dyn.ccf.c2", "del.bc.p.dyn.ccf.c3", "del.bc.ph.dyn.ccf.c1", "del.bc.ph.dyn.ccf.c2", "del.bc.ph.dyn.ccf.c3")) %>%
  drop_na(del.bc) %>% 
  distinct() %>% 
  ##PLOT
  ggplot(aes(x = factor(appr, levels = bge_lvls), y = del.bc)) +
  geom_boxplot(width = 0.3) +
  geom_jitter(aes(fill = factor(appr, levels = bge_lvls)), width = 0.1, shape = 21, size = 3, alpha = 0.7) +
  labs(x = "", y = expression(italic("∆POC, µmol C L"^-1)), colour = expression(italic(""))) + 
  scale_y_continuous(breaks = pretty_breaks()) +
  custom_theme() +
  facet_grid(type~factor(Season, levels = levels) , scales = "free") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) 

#######delta TOC#########

del_toc.plot <-  bge_summary %>% 
  select(Season:gf75.flag, del.doc)  %>% 
  distinct() %>% 
  #remove outliers
  filter(!Cruise == "AT38" | !Station == 1 | !Depth == 10 | !Treatment == "Control",
         !Cruise == "AT39" | !Station == 1 | !Depth == 10 | !Treatment == "Control") %>% 
  filter(!Station == "U", Depth == 10) %>%
  drop_na(del.doc) %>% 
  distinct() %>% 
  ##PLOT
  ggplot(aes(x = Season, y = del.doc)) +
  geom_boxplot(width = 0.2) +
  geom_jitter(width = 0.2, shape = 21, size = 2, alpha = 0.7) +
  labs(x = "", y = expression(italic("∆TOC, µmol C L"^-1)), colour = expression(italic(""))) +
  scale_y_continuous(breaks = pretty_breaks()) +
  custom_theme() +
  facet_grid(type~factor(Season, levels = levels) , scales = "free") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  theme(strip.background.x = element_blank()) 

#########BGE##########
  
bge.plot <- bge_summary %>%
  select(Season:Bottle, i.cn:i.cn.c3, s.cn:s.cn.c3, gf75.flag, del.doc.flag, del.ph.doc.flag, contains("bge")) %>% 
  distinct() %>% 
  pivot_longer(contains("bge"), names_to = "key", values_to = "bge") %>% 
  drop_na(bge) %>% 
  mutate(appr = key,
         appr = ifelse(appr == "bge.bc.poc", "p2p, POC", appr),
         appr = ifelse(appr == "bge.bc.poc.c1", "p2p, POC c1", appr),
         appr = ifelse(appr == "bge.bc.poc.c2", "p2p, POC c2", appr),
         appr = ifelse(appr == "bge.bc.poc.c3", "p2p, POC c3", appr),
         appr = ifelse(appr == "bge.p.bc.ccf.c1", "p2p, CCF c1", appr),
         appr = ifelse(appr == "bge.p.bc.ccf.c2", "p2p, CCF c2", appr),
         appr = ifelse(appr == "bge.p.bc.ccf.c3", "p2p, CCF c3", appr),
         appr = ifelse(appr == "bge.p.bc.ccf.white", "p2p, White CCF", appr),
         appr = ifelse(appr == "bge.p.bc.ccf.fukuda", "p2p, Fukuda CCF", appr),
         appr = ifelse(appr == "bge.p.bc.ccf.lee", "p2p, Lee CCF", appr),
         appr = ifelse(appr == "bge.p.bc.dyn.ccf.white_fukuda", "p2p, Dyn. White_Fukuda CCF", appr),
         appr = ifelse(appr == "bge.p.bc.dyn.ccf.white_lee", "p2p, Dyn. White_Lee CCF", appr),
         appr = ifelse(appr == "bge.ph.bc.ccf.c1", "ph2ph, CCF c1", appr),
         appr = ifelse(appr == "bge.ph.bc.ccf.c2", "ph2ph, CCF c2", appr),
         appr = ifelse(appr == "bge.ph.bc.ccf.c3", "ph2ph, CCF c3", appr),
         appr = ifelse(appr == "bge.ph.bc.ccf.white", "ph2ph, White CCF", appr),
         appr = ifelse(appr == "bge.ph.bc.ccf.fukuda", "ph2ph, Fukuda CCF", appr),
         appr = ifelse(appr == "bge.ph.bc.ccf.lee", "ph2ph, Lee CCF", appr),
         appr = ifelse(appr == "bge.ph.bc.dyn.ccf.white_fukuda", "ph2ph, Dyn. White_Fukuda CCF", appr),
         appr = ifelse(appr == "bge.ph.bc.dyn.ccf.white_lee", "ph2ph, Dyn. White_Lee CCF", appr),
         p = appr) %>% 
  separate(., p, into = c("points", "ccf"), sep = "," ) %>% 
  group_by(Cruise, type, appr) %>% 
  add_tally() %>% 
  ungroup() %>% 
  #remove outliers
  filter(!Cruise == "AT38" | !Station == 1 | !Depth == 10 | !Treatment == "Control",
         !Cruise == "AT39" | !Station == 1 | !Depth == 10 | !Treatment == "Control") %>% 
  filter(!Station == "U", Depth == 10, points == "p2p") %>%
 ##PLOT
  ggplot(aes(x = factor(appr, levels = bge_lvls), y = bge)) +
  geom_boxplot(width = 0.3) +
  geom_jitter(aes(fill = factor(appr, levels = bge_lvls)), width = 0.1, shape = 21, size = 3, alpha = 0.7) +
  labs(x = "", y = expression(italic("BGE")), colour = expression(italic(""))) + 
  scale_y_continuous(breaks = pretty_breaks()) +
  custom_theme() +
  facet_grid(type~factor(Season, levels = levels) , scales = "free") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  guides(fill = F) 

###############

(del_bc.plot / del_toc.plot) | bge.plot

```

Generally, good agreement between BGEs estimated using empirical ∆POC and empirical CCFs.

But, there can be wide disagreement. This disagreement is rooted in the ∆POC.

When ∆BC > than ∆POC, carbon per cell is overestimated (cell abundance on the filter is likely underestimated). This would lead to BGEs calculated using CCFs being high and unreliable. 

Based on these criteria, there are two experiments in the late spring (station 3) where BGEs calculated using empirical CCFs should not be included. These will be removed from further analyses. 



```{r}
bge_summary.table <- bge_summary %>% 
  mutate(bge.p.bc.ccf.c1 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.p.bc.ccf.c1),
         bge.p.bc.ccf.c2 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.p.bc.ccf.c2),
         bge.p.bc.ccf.c3 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.p.bc.ccf.c3)) %>%  
  select(Season:Bottle, contains("bge")) %>% 
  group_by(Season, type) %>% 
  gather(appr, bge, contains("bge")) %>% 
  drop_na(bge) %>% 
  group_by(Cruise, type, appr) %>% 
  mutate(ave_bge = mean(bge),
         sd_bge = sd(bge),
         min_bge = min(bge),
         max_bge = max(bge),
         med_bge = median(bge)) %>% 
  ungroup() %>% 
  select(Season, type,  appr, ave_bge:med_bge) %>% 
  distinct() %>% 
  filter(type == "Control") %>% 
  arrange(Season) %>% 
  mutate_at(vars(ave_bge:med_bge), round, 2) 

bge_summary.table 
  
```

```{r}
ave_bges <- bge_summary.table %>% 
  filter(appr %in% c("bge.bc.poc.c1", "bge.p.bc.ccf.c1",  "bge.p.bc.ccf.lee", "bge.p.bc.ccf.fukuda")) %>% 
  mutate(group = ifelse(appr %in% c("bge.bc.poc.c1", "bge.p.bc.ccf.c1"), "Empirical", "Fukuda et al. CCF"),
         group = ifelse(appr == "bge.p.bc.ccf.lee", "Lee and Fuhrman CCF", group ),
         group2 = ifelse(appr == "bge.bc.poc.c1", "Empirical ∆POC", group),
         group2 = ifelse(appr == "bge.p.bc.ccf.c1", "Empirical CCF", group2)) %>%
  select(Season, group2, ave_bge, sd_bge,  group) %>% 
  rename(appr = group2) %>% 
  group_by(Season, group) %>% 
  mutate(group_bge = round(mean(ave_bge),2),
         sd_group_bge = round(sd(ave_bge),2)) %>%
  ungroup() %>% 
  group_by(group) %>% 
  mutate(global_bge = round(mean(ave_bge), 2),
         sd_global_bge = round(sd(ave_bge),2)) %>% 
  ungroup()

ave_bges
```



```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 23, fig.align = "center", warning = FALSE}

ave_bges %>% 
  ggplot(aes(x = factor(appr, levels = c("Empirical ∆POC", "Empirical CCF", "Fukuda et al. CCF", "Lee and Fuhrman CCF" )), y = ave_bge)) +
    geom_bar(position = position_dodge(), stat = "identity", color = "black", alpha = 1, fill = "#999999", width = 0.4) +
    geom_errorbar(aes(ymin = ave_bge - sd_bge, ymax = ave_bge + sd_bge), position = position_dodge(width = 0.9), stat = "identity", width = 0.1, size = 0.5) +
    #geom_label(aes(label = n), fontface = 3) +
   scale_y_continuous(breaks = pretty_breaks()) +
    scale_fill_manual(values = custom.colors) +
    labs(x = expression(italic("Estimation Approach")), y = expression(italic(paste("BGE"))), colour = expression(italic(""))) +
    custom_theme() +
    facet_grid(~factor(Season, levels = levels), scales = "free") 
```

# Save Data

Before saving, we'll want to remove the problematic CCFs and their associated BGEs from further analysis

```{r message = F}
calcs %>% 
  mutate(bge.p.bc.ccf.c1 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.p.bc.ccf.c1),
         bge.p.bc.ccf.c2 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.p.bc.ccf.c2),
         bge.p.bc.ccf.c3 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.p.bc.ccf.c3),
         bge.ph.bc.ccf.c1 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.ph.bc.ccf.c1),
         bge.ph.bc.ccf.c2 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.ph.bc.ccf.c2),
         bge.ph.bc.ccf.c3 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.ph.bc.ccf.c3)) %>% 
  left_join(., calcs %>% 
              filter(Depth == 10, Treatment == "Control", Hours == 0, !Station == "U") %>% 
              mutate(bge.p.bc.ccf.c1 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.p.bc.ccf.c1),
                     bge.p.bc.ccf.c2 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.p.bc.ccf.c2),
                     bge.p.bc.ccf.c3 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.p.bc.ccf.c3),
                     bge.ph.bc.ccf.c1 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.ph.bc.ccf.c1),
                     bge.ph.bc.ccf.c2 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.ph.bc.ccf.c2),
                     bge.ph.bc.ccf.c3 = ifelse(Cruise == "AT34" & Station == 3 & Depth == 10, NA, bge.ph.bc.ccf.c3)) %>%  
              select(Cruise, Season, Subregion, Station,  i.ccf.c1, s.ccf.c1 ) %>%
              distinct() %>% 
              mutate(global_initial_ccf = mean(i.ccf.c1, na.rm = T),
                     global_stationary_ccf = mean(s.ccf.c1, na.rm = T)) %>%
              group_by(Season) %>% 
              mutate(ave_initial_ccf = mean(i.ccf.c1, na.rm = T),
                     ave_stationary_ccf = mean(s.ccf.c1, na.rm = T)) %>%
              ungroup() %>%
              select(Season, global_initial_ccf:ave_stationary_ccf) %>% 
              distinct() ) %>% 
  left_join(., ave_bges %>% filter(group == "Empirical") %>% select(Season, group_bge, global_bge) %>% distinct() %>% rename(season_bge = group_bge)) %>% 
  saveRDS(., "~/naames_bioav_ms/Output/processed_bge.rds")


```
