---
title: "DOC_NAAMES_Remin_Bioassays"
author: "Nicholas Baetge"
date: "5/19/2020"
output: github_document
---

# Intro

This document shows how **individual bottle** DOC data from NAAMES remineralization bioassays were processed, QC'd, and analyzed. 

```{r Packages, message = F, warning = F}
library(tidyverse) 
library(readxl)
library(zoo)
library(oce)
library(patchwork)
#stat tests
library(lmtest)
library(lmodel2)
library(rstatix)
library(ggpubr)
```

# Import and Tidy Data

We will need to tidy the data in the same way the bacterial abundance dataframe was tidied before merging the datasets. We'll then omit data low quality data i.e. poor replication or possible contamination. We observed contamination in many of the NAAMES 2 experiments after incubations were transferred to WHOI.

```{r Import and tidy, message = F}
oc.df <- read_csv("~/GITHUB/naames_bioav_ms/Input/master/N2-4_DOC_Remin_Master.csv") %>%
  mutate(Season = Cruise,
         Season = gsub("AT34", "Late Spring", Season),
         Season = gsub("AT38", "Early Autumn", Season),
         Season = gsub("AT39", "Early Spring", Season),
         Treatment = ifelse(Bottle == "Niskin", "Niskin", Treatment),
         Treatment = ifelse(Bottle == "GF75", "GF75", Treatment),
         Treatment = gsub("TW15", "TW20", Treatment),
         Treatment = ifelse(is.na(Treatment), Bottle, Treatment),
         Treatment = ifelse(Treatment %in% c("Surface", "Deep"), "Parallel", Treatment),
         Treatment = ifelse(Treatment %in% c("100mls", "250mls", "500mls", "1L"), "Volume", Treatment),
         Treatment_Btl = ifelse(Bottle == "Niskin", "Niskin", Treatment_Btl),
         Treatment_Btl = ifelse(Bottle == "GF75" & is.na(Treatment_Btl), "GF75", Treatment_Btl),
         Treatment_Btl = gsub("TW15", "TW20", Treatment_Btl),
         Treatment_Btl = gsub("TW12-A", "TW12-C", Treatment_Btl),
         Treatment_Btl = gsub("TW12-B", "TW12-D", Treatment_Btl),
         Treatment_Btl = gsub("TW13-A", "TW12-E", Treatment_Btl),
         Treatment_Btl = gsub("TW13-B", "TW12-F", Treatment_Btl),
         Treatment_Btl = ifelse(is.na(Treatment_Btl), Bottle, Treatment_Btl),
         Bottle = gsub("SA", "A", Bottle),
         Bottle = gsub("SB", "B", Bottle),
         Bottle = gsub("DA", "C", Bottle),
         Bottle = gsub("DB", "D", Bottle),
         Bottle = ifelse(Bottle == "GF75", Treatment_Btl, Bottle),
         Bottle = gsub("Control-", "", Bottle),
         Bottle = gsub("TW12-", "", Bottle),
         Bottle = gsub("TW13-", "", Bottle),
         Bottle = gsub("MixDS-", "", Bottle),
         Bottle = gsub("MixSD-", "", Bottle),
         Bottle = gsub("SynExd-", "", Bottle),
         Bottle = gsub("TWExd-", "", Bottle),
         Bottle = gsub("SynLys-", "", Bottle),
         Bottle = gsub("TW5-", "", Bottle),
         Bottle = gsub("TW10-", "", Bottle),
         Bottle = gsub("TW20-", "", Bottle),
         Bottle = gsub("12", "", Bottle),
         Bottle = gsub("13", "", Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW12" & Bottle == "A", gsub("A", "C", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW12" & Bottle == "B", gsub("B", "D", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW13" & Bottle == "A", gsub("A", "E", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW13" & Bottle == "B", gsub("B", "F", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "Control" & Bottle == "C", gsub("C", "G", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "Control" & Bottle == "D", gsub("D", "H", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW12" & Bottle == "C", gsub("C", "I", Bottle),Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW12" & Bottle == "D", gsub("D", "J", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW13" & Bottle == "C", gsub("C", "K", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW13" & Bottle == "D", gsub("D", "L", Bottle), Bottle),
         Depth = gsub(5, 10, Depth),
         Depth = as.numeric(Depth),
         key = paste(Cruise, Station, Depth, Treatment, Bottle, Timepoint, sep = "."),
         PTOC_ave = ifelse(Treatment == "Parallel", TOC_ave, PTOC_ave),
         PTOC_sd = ifelse(Treatment == "Parallel", TOC_sd, PTOC_sd)) %>% 
  rename(doc = DOC_ave,
         sd_doc = DOC_sd,
         toc = TOC_ave, 
         sd_toc = TOC_sd, 
         ptoc = PTOC_ave, 
         sd_ptoc = PTOC_sd, 
         pdoc = PDOC_ave, 
         sd_pdoc = PDOC_sd) %>%
  filter(!Treatment %in% c("Niskin", "GF75", "TFF-Ret", "Volume")) %>% 
  select(-Treatment_Btl) %>% 
  select(Season, everything()) %>% 
  arrange(Cruise, Station, Depth, Treatment, Bottle, Hours)  %>% 
  filter(!is.na(Hours))

saveRDS(oc.df, "~/GITHUB/naames_bioav_ms/Input/master/DOC_Input")

```

Because a different suite of organic carbon samples were taken on each cruise, we'll separate the cruise datasets, drop NA values, quality filter them, and then recombine the datasets. To quality filter, we'll calculate rolling ∆DOC values i.e. the difference between the one observation and the one before it. We'll omit the data where ∆DOC indicates contamination due to transport etc. after the 21 d shipboard occupation (increase greater than our detection limit, 1.5 µmol C L^-1^).

```{r QC data}
n2_oc <- oc.df %>% 
  filter(Cruise == "AT34") %>% 
  drop_na(doc) %>%
  group_by(Station, Depth, Treatment, Bottle) %>%
  mutate(doc_from_last = lag(doc) - doc) %>% 
  filter(!doc_from_last <= -1.5 | is.na(doc_from_last) | !Hours > 504)  %>% 
  mutate(doc_from_last = lag(doc) - doc) %>% 
  filter(!doc_from_last <= -1.5 | is.na(doc_from_last) | !Hours > 504) %>% 
  mutate(doc_from_last = lag(doc) - doc) %>% 
  filter(!doc_from_last <= -1.5 | is.na(doc_from_last) | !Hours > 504) %>% 
  mutate(doc_from_last = lag(doc) - doc,
         doc_from_t0 = first(doc) - doc) %>% 
  filter(!Station == 4 | !Hours == 192) %>% 
  ungroup()

n3_4_oc <- oc.df %>% 
  filter(!Cruise == "AT34") %>% 
  drop_na(ptoc) %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle) %>% 
  mutate(ptoc_from_last = lag(ptoc) - ptoc) %>% 
  filter(!ptoc_from_last <= -1.5 | is.na(ptoc_from_last) | !Hours > 504) %>% 
  mutate(ptoc_from_last = lag(ptoc) - ptoc,
         ptoc_from_t0 = first(ptoc) - ptoc,
         doc_from_t0 = first(doc) - doc,
         toc_from_t0 = first(toc) - toc, 
         pdoc_from_t0 = first(pdoc) - pdoc) %>%
  ungroup()

oc_p <- bind_rows(n2_oc, n3_4_oc) %>% 
  mutate(Days = round(Hours/24, 2),
         facet_depth = paste(Depth, "m"), 
         facet_treatment = Treatment, 
         facet_treatment = gsub("MixSD", "Surface Comm., Deep DOM", facet_treatment),
         facet_treatment = gsub("MixDS", "Deep Comm., Surface DOM", facet_treatment),
          facet_treatment = gsub("SynExd", "Synechococcus Exudate", facet_treatment),
         facet_treatment = gsub("SynLys", "Synechococcus Lysate", facet_treatment),
          facet_treatment = gsub("TWExd", "T. Weissflogii Exudate", facet_treatment),
         facet_treatment = gsub("TW5", "+5 µmol C/L Exudate", facet_treatment),
          facet_treatment = gsub("TW10", "+10 µmol C/L Exudate", facet_treatment),
          facet_treatment = gsub("TW20", "+20 µmol C/L Exudate", facet_treatment),
           facet_treatment = gsub("TW12", "T. Weissflogii 12C Exudate", facet_treatment),
          facet_treatment = gsub("TW13", "T. Weissflogii 13C Exudate", facet_treatment),
         facet_bottle = Bottle,
         facet_bottle = gsub("W", "Whole Seawater", facet_bottle),
          facet_bottle = gsub("1.2", "1.2 µm Filtrate", facet_bottle), 
          facet_bottle = gsub("NV", "1.2 µm Filtrate: TFF Filtrate (3:7)", facet_bottle)) 
```

# Save Data

```{r Subset and save}
saveRDS(oc_p, "~/GITHUB/naames_bioav_ms/Output/unfiltered/processed_doc.rds")

filtered_data <- oc_p %>% 
  filter(Treatment %in% c("Control", "TW5", "TW10", "TW20"), Depth == 10, !Station == "U") %>% 
  select(Season:Hours, Days, doc:sd_pdoc, everything(), -facet_depth)

saveRDS(filtered_data, "~/GITHUB/naames_bioav_ms/Output/filt_processed_doc.rds")

    
```





