---
title: "NAAMES DOC Remineralization Bioassays - Bottles"
author: "Nicholas Baetge"
date: "2/29/2020"
output: github_document
---

# Intro

This document shows how **individual bottle** data from NAAMES DOC remineralization bioassays were processed, QC'd, and analyzed. 

```{r message = F, warning = F}
library(tidyverse) 
library(rmarkdown)
library(knitr)
library(data.table) 
library(scales)
library(zoo)
library(oce)
#rmarkdown tables
library(stargazer)
library(pander)
library(growthcurver)
#stat tests
library(lmtest)
library(lmodel2)
```


```{r include = FALSE}
custom_theme <- function() {
  theme_test(base_size = 16) %+replace%
    theme(legend.position = "top",
          legend.title = element_blank(),
          legend.spacing.x = unit(0.5,"cm"),
          legend.background = element_rect(fill = "transparent",colour = NA),
          legend.key = element_rect(fill = "transparent",colour = NA),
          panel.background = element_rect(fill = "transparent",colour = NA),
          plot.background = element_rect(fill = "transparent",colour = NA)) 
}

custom_theme_linedraw <- function() {
  theme_linedraw(base_size = 16) %+replace%
    theme(legend.position = "right",
          legend.title = element_blank(),
          legend.spacing.x = unit(0.5,"cm"),
          legend.background = element_rect(fill = "transparent",colour = NA),
          legend.key = element_rect(fill = "transparent",colour = NA),
          panel.background = element_rect(fill = "transparent",colour = NA),
          plot.background = element_rect(fill = "transparent",colour = NA)) 
}

custom.colors <- c("AT39" = "#377EB8", "AT34" = "#4DAF4A", "AT38" = "#E41A1C", "AT32" = "#FF7F00", "Temperate" = "#A6CEE3", "Subpolar" = "#377EB8", "Subtropical" = "#FB9A99", "GS/Sargasso" = "#E41A1C", "Early Spring" = "#377EB8", "Late Spring" = "#4DAF4A","Early Autumn" = "#E41A1C", "Summer" = "#E41A1C", "Late Autumn" = "#FF7F00", "A" = "#E41A1C", "B" = "#377EB8", "C" = "#4DAF4A", "D" = "#FF7F00", "E" = "#FDB927", "F" = "#552583", "G" = "#FDB927", "H" = "#552583",   "Control" = "#E41A1C", "TW12" = "#377EB8", "T. Weissflogii 12C Exudate" = "#377EB8", "TW13" = "#4DAF4A", "T. Weissflogii 13C Exudate" = "#4DAF4A", "MixDS" = "#377EB8", "Deep Comm., Surface DOM" = "#377EB8","MixSD" = "#4DAF4A", "Surface Comm., Deep DOM" = "#4DAF4A", "SynLys" = "#377EB8", "Synechococcus Lysate" = "#377EB8", "SynExd" = "#4DAF4A", "Synechococcus Exudate" = "#4DAF4A", "TWExd" = "#FF7F00", "T. Weissflogii Exudate" = "#FF7F00", "TW5" = "#377EB8", "TW10" = "#4DAF4A", "TW20" = "#FF7F00", "Parallel" = "#377EB8", "W" = "#552583", "Whole Seawater" = "#552583", "1.2" = "#4DAF4A", "1.2 µm Filtrate" = "#4DAF4A", "NV" = "#FF7F00", "1.2 µm Filtrate: TFF Filtrate (3:7)" = "#FF7F00", "Carbon" = "#E41A1C", "Nitrogen" = "#377EB8", "+5 µmol C/L Exudate" = "#FF7F00", "+10 µmol C/L Exudate" = "#FF7F00", "+20 µmol C/L Exudate" = "#FF7F00") 

custom.shapes <- c("Early Spring" = 21, "Late Spring" = 22,"Early Autumn" = 23)


levels = c("GS/Sargasso", "Subtropical", "Temperate", "Subpolar",  "AT39-6", "AT34", "AT38", "AT32","South", "North", "Early Spring", "Late Spring","Early Autumn",  "Summer", "Late Autumn", "Control", "Parallel", "SynLys", "SynExd", "TWExd", "MixSD", "MixDS", "TW12", "TW13", "TW5", "TW10", "TW20",  "Surface Comm., Deep DOM", "Deep Comm., Surface DOM", "Synechococcus Exudate", "Synechococcus Lysate", "T. Weissflogii Exudate", "T. Weissflogii 12C Exudate", "T. Weissflogii 13C Exudate", "+5 µmol C/L Exudate", "+10 µmol C/L Exudate","+20 µmol C/L Exudate", "A", "B", "C", "D", "E", "F", "G", "H", "I", "J", "K", "L", "M", "N", "O", "P", "W", "Whole Seawater","1.2", "1.2 µm Filtrate","NV", "1.2 µm Filtrate: TFF Filtrate (3:7)")


       


```

# Bacterial Abundance

Here, growth curves are fitted to the logistic equation using the GrowthCurver package. The timing of the onset of the stationary growth phase is determined from the model fit.

## Import and Tidy Data

```{r message = F}
ba.df <- read_csv("~/naames_bioav_ms/Input/N2-4_BactA_Remin_Master.csv") %>% 
  mutate(Season = Cruise,
         Season = gsub("AT34", "Late Spring", Season),
         Season = gsub("AT38", "Early Autumn", Season),
         Season = gsub("AT39", "Early Spring", Season),
         Treatment = ifelse(Bottle == "Niskin", "Niskin", Treatment),
         Treatment = ifelse(Bottle == "GF75", "GF75", Treatment),
         Treatment = gsub("TW15", "TW20", Treatment),
         Treatment = ifelse(is.na(Treatment), Bottle, Treatment),
         Treatment = ifelse(Treatment %in% c("100mls", "250mls", "500mls", "1L"), "Volume", Treatment),
         Treatment = gsub("Surface", "Parallel", Treatment),
         Treatment_Btl = ifelse(Bottle == "Niskin", "Niskin", Treatment_Btl),
         Treatment_Btl = ifelse(Bottle == "GF75" & is.na(Treatment_Btl), "GF75", Treatment_Btl),
         Treatment_Btl = gsub("TW15", "TW20", Treatment_Btl),
         Treatment_Btl = gsub("TW12-A", "TW12-C", Treatment_Btl),
         Treatment_Btl = gsub("TW12-B", "TW12-D", Treatment_Btl),
         Treatment_Btl = gsub("TW13-A", "TW12-E", Treatment_Btl),
         Treatment_Btl = gsub("TW13-B", "TW12-F", Treatment_Btl),
         Treatment_Btl = ifelse(is.na(Treatment_Btl), Bottle, Treatment_Btl),
         Bottle = gsub("SA", "A", Bottle),
         Bottle = gsub("SB", "B", Bottle),
         Bottle = gsub("DA", "C", Bottle),
         Bottle = gsub("DB", "D", Bottle),
         Bottle = ifelse(Bottle == "GF75", Treatment_Btl, Bottle),
         Bottle = gsub("Control-", "", Bottle),
         Bottle = gsub("TW12-", "", Bottle),
         Bottle = gsub("TW13-", "", Bottle),
         Bottle = gsub("MixDS-", "", Bottle),
         Bottle = gsub("MixSD-", "", Bottle),
         Bottle = gsub("SynExd-", "", Bottle),
         Bottle = gsub("TWExd-", "", Bottle),
         Bottle = gsub("SynLys-", "", Bottle),
         Bottle = gsub("TW5-", "", Bottle),
         Bottle = gsub("TW10-", "", Bottle),
         Bottle = gsub("TW20-", "", Bottle),
         Bottle = gsub("12", "", Bottle),
         Bottle = gsub("13", "", Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW12" & Bottle == "A", gsub("A", "C", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW12" & Bottle == "B", gsub("B", "D", Bottle), Bottle),
          Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW13" & Bottle == "A", gsub("A", "E", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW13" & Bottle == "B", gsub("B", "F", Bottle), Bottle),
          Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "Control" & Bottle == "C", gsub("C", "G", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "Control" & Bottle == "D", gsub("D", "H", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW12" & Bottle == "C", gsub("C", "I", Bottle),Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW12" & Bottle == "D", gsub("D", "J", Bottle), Bottle),
          Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW13" & Bottle == "C", gsub("C", "K", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW13" & Bottle == "D", gsub("D", "L", Bottle), Bottle),
          Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "GF75" & Bottle == "A", gsub("A", "G", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "GF75" & Bottle == "B", gsub("B", "H", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "GF75" & Bottle == "C", gsub("C", "I", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "GF75" & Bottle == "D", gsub("D", "J", Bottle), Bottle),
          Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "GF75" & Bottle == "E", gsub("E", "K", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "GF75" & Bottle == "F", gsub("F", "L", Bottle), Bottle),
          Bottle = ifelse(Cruise == "AT34" & Station == 1 & Depth == 200 & Treatment == "GF75" & Bottle == "A", gsub("A", "C", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 1 & Depth == 200 & Treatment == "GF75" & Bottle == "B", gsub("B", "D", Bottle), Bottle),
           Bottle = ifelse(Cruise == "AT34" & Station == 4 & Depth == 200 & Treatment == "GF75" & Bottle == "A", gsub("A", "C", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 4 & Depth == 200 & Treatment == "GF75" & Bottle == "B", gsub("B", "D", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 5 & Depth == 200 & Treatment == "GF75" & Bottle == "A", gsub("A", "C", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 5 & Depth == 200 & Treatment == "GF75" & Bottle == "B", gsub("B", "D", Bottle), Bottle),
         Depth = gsub(5, 10, Depth),
         Depth = as.numeric(Depth)) %>% 
  rename(cells = cellsperL,
         sd_cells = sd_cellsperL,
         p_cells = p_cellsperL,
         sd_p_cells = p_sdcellsperL) %>% 
  drop_na(cells) %>% 
  select(-Treatment_Btl) %>% 
  select(Season, everything()) %>% 
  arrange(Cruise, Station, Depth, Treatment, Bottle, Hours)

ba.df$Season <- factor(ba.df$Season, levels = levels)
```

## Inspect Growth Curves

To be able to calculate derived variables, such as carbon per cell and BGE, we'll need to inspect the growth curves and define the stationary phase for each experiment.

We are using the growthcurver package to fit growth curve data to the standard form of the logistic equation and then return a data table with population-level information. Specifically, the model outputs we are really only interested in are:

- t_mid, the time at which 1/2 carrying capacity is reached. We will double this estimate to attain the time at which carrying capacity is reached (stationary)
- sigma, a measure of the goodnesss of fit of the parameters of the logistic equation for the data; it is the residual sum of squares from the nonlinear regression model. Smaller sigma values indicate a better fit of the logistic curve to the data than larger values.
- df, degrees of freedom


```{r}
gc_input <- ba.df %>% 
  filter(!Treatment %in% c("Niskin","GF75", "Volume", "Parallel", "TFF-Ret")) %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle) %>% 
  #calculate the running delta of nat log cells for each exp
  mutate(lncells = round(log(cells), 2),
         delta_lncells = lncells - lncells[which.min(Hours)],
         delta_lncells = ifelse(delta_lncells < 0, 0, delta_lncells)) 

gc_input_keys <- gc_input %>% 
  group_keys() %>% 
  mutate(key = paste(Cruise, ", S", Station, ", Z =", Depth, ",", Treatment, ",", Bottle))
gc_input_header <- gc_input_keys$key

gc_input_list <- gc_input %>% 
  group_split()
names(gc_input_list) <- gc_input_header

```

```{r}
gcplot.func <- function(x){
  gc_fit <- SummarizeGrowth(x$Hours, x$delta_lncells) 
}
gcplot.list <- lapply(gc_input_list, gcplot.func)
```

For the sake of keeping the length of this document as short as possible, the growth curve model plots are not included here. However, they are included below in the section "Re-evaluate Growth Curves".

```{r include = FALSE}
for (i in 1:length(gcplot.list)) {
  plot(gcplot.list[[i]], main = names(gcplot.list[i]), xlab = expression(italic("Hours")) , ylab = expression(italic(paste("ln cells, L"^"-1") ))) 
}
```

## Re-evaluate Growth Curves

To improve the model fits and thus, the timing estimates of the stationary transition for each experiment, we need to evaluate each growth curve, manually filtering out death/secondary growth phases and poorly replicated samples that skew the model results.

```{r}
eval_gc_input <- gc_input %>% 
  mutate(key = paste(Cruise, Station, Depth, Treatment, Bottle, Timepoint, sep = ".")) %>% 
  select(Season:Treatment, key, everything()) %>% 
  filter(!Hours >= 300) %>% 
  filter(!key %in% c("AT34.1.10.Control.A.1","AT34.1.10.Control.B.1", "AT34.1.200.Control.C.3", "AT34.1.200.Control.D.3","AT34.2.10.Control.A.4", "AT34.2.10.Control.A.9", "AT34.2.10.Control.A.10", "AT34.2.10.Control.A.11","AT34.2.10.Control.A.4", "AT34.2.10.Control.B.7", "AT34.2.10.Control.B.9", "AT34.2.10.Control.A.11", "AT34.2.10.TW12.C.5",
  "AT34.2.10.TW13.E.2", "AT34.2.10.TW13.F.3", "AT34.2.200.Control.G.2", "AT34.2.200.Control.G.5", "AT34.2.200.Control.G.6", "AT34.2.200.Control.G.7", "AT34.2.200.Control.H.5", "AT34.2.200.Control.H.6", "AT34.2.200.Control.H.7", "AT34.2.200.TW12.I.2", "AT34.2.200.TW12.J.2", "AT34.2.200.TW13.K.2", "AT34.3.10.Control.A.8", "AT34.3.10.Control.A.9", "AT34.3.10.Control.A.10", "AT34.3.10.Control.B.8", "AT34.3.10.Control.B.9", "AT34.3.10.Control.B.10", "AT34.3.200.Control.C.4", "AT34.3.200.Control.C.6", "AT34.3.200.Control.C.9", "AT34.3.200.Control.D.7", "AT34.4.200.Control.C.5", "AT34.4.200.Control.C.6", "AT34.4.200.Control.C.7", "AT34.4.200.Control.D.5", "AT34.4.200.Control.D.6", "AT34.4.200.Control.D.7", "AT34.5.10.Control.A.5", "AT34.5.10.Control.B.5", "AT34.U.10.Control.A.5", "AT34.U.10.Control.B.8", "AT34.U.10.Control.B.1", "AT38.1.10.Control.A.1", "AT38.1.10.Control.B.7", "AT38.1.10.MixSD.G.6", "AT38.1.10.SynExd.I.8", "AT38.1.10.SynExd.I.9", "AT38.1.10.SynExd.I.10", "AT38.1.10.SynExd.J.8", "AT38.1.10.SynExd.J.9", "AT38.1.10.SynExd.J.10", "AT38.1.10.SynLys.M.9", "AT38.1.10.SynLys.M.10", "AT38.1.10.SynLys.N.9", "AT38.1.10.SynLys.N.10", "AT38.1.200.Control.F.5", "AT38.1.200.Control.F.6", "AT38.1.200.Control.E.5", "AT38.1.200.Control.E.6", "AT38.1.200.MixDS.C.5", "AT38.1.200.MixDS.C.8", "AT38.1.200.MixDS.D.5", "AT38.1.200.MixDS.D.6", "AT38.4.10.Control.A.7", "AT38.4.10.Control.B.7", "AT38.4.10.Control.B.8", "AT38.5.10.Control.A.9", "AT38.5.10.Control.A.10", "AT38.5.10.Control.A.11", "AT38.5.10.Control.B.7"))

eval_gc_input_keys <- eval_gc_input %>% 
  group_keys() %>% 
  mutate(key = paste(Cruise, ", S", Station, ", Z =", Depth, ",", Treatment, ",", Bottle)) 
eval_gc_input_header <- eval_gc_input_keys$key

eval_gc_input_list <- eval_gc_input %>% 
  group_split()
names(eval_gc_input_list) <- eval_gc_input_header

eval_gcplot.list <- lapply(eval_gc_input_list, gcplot.func)
```

We've omitted 88 of the 768 (~11%) of the observations to improve the model fit. 47% of those omitted observations were taken after 300 hours, which for many experiments constituted the death phase.  

```{r}
for (i in 1:length(eval_gcplot.list)) {
  plot(eval_gcplot.list[[i]], main = names(eval_gcplot.list[i]), xlab = expression(italic("Hours")) , ylab = expression(italic(paste("ln cells, L"^"-1") ))) 
}
```

## Wrangle GrowthCurver Data

We'll add the model output data to the original dataframe, but first we'll tidy the model output and look at the distribution of the model fits. 

We'll determine thresholds for sigma (smaller sigma values indicate a better fit) and df for omission of model fit data. 

```{r}
gcdata.func <- function(y){
  gc.fit <- SummarizeGrowth(y$Hours, y$delta_lncells)
  gcdata.df <- as.data.frame(unlist(gc.fit$vals), stringsAsFactors = FALSE)
}

gcdata <- eval_gc_input_list %>% 
  lapply(., gcdata.func) %>% 
  #save the list as a data frame %>% 
  data.frame(.) %>% 
  t(.) %>% 
  as_data_frame(.) %>% 
  mutate_at(., vars(k:auc_e), as.numeric) %>% 
  mutate_at(vars(sigma, t_mid), round, 2) %>% 
  #calculate time to stationary for each curve
  mutate(stationary = round(t_mid*2)) %>% 
  mutate(key = eval_gc_input_header) %>% 
  ungroup() 
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 6, fig.align = "center", warning = FALSE}
gcdata %>% 
  ggplot(aes(x = sigma)) +
  geom_histogram(bins = 30, alpha = 0.7, color = "black", fill = "#377EB8") +
  custom_theme() +
  scale_x_continuous(breaks = pretty_breaks())
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 6, fig.align = "center", warning = FALSE}
gcdata %>% 
  ggplot(aes(x = df)) +
  geom_histogram(bins = 7, alpha = 0.7, color = "black", fill = "#377EB8") + 
  custom_theme() +
  scale_x_continuous(breaks = pretty_breaks())
```

Based on these two histograms, we'll omit model fit data where sigma > 0.21 and df < 4. In these experiments, we cannot reliably distinguish the onset of stationary.

```{r message = FALSE}
gcmerge.df <- eval_gc_input %>% 
  mutate(key = paste(Cruise, ", S", Station, ", Z =", Depth, ",", Treatment, ",", Bottle)) %>% 
  full_join(., gcdata %>% filter(!sigma > 0.21 | !df < 4)) %>% 
  ungroup() 

```

## Add Stationary Timepoint

We'll add a row to each experiment that includes the stationary timepoint. 

```{r}
gcmerge.list <- gcmerge.df %>% 
  #Split the dataframe into lists
  split(.,  .$key)

#add row to each list element
newrow.func <- function(morty){
  morty[nrow(morty) + 1,] <- NA
  rick <- morty %>% 
    fill(Season:Bottle, Treatment, key, stationary)
  rick
}

#apply function to list
gcstat.list <- lapply(gcmerge.list, newrow.func)

gcstat.df <- plyr::ldply(gcstat.list, data.frame) %>% 
  select(Season:Hours, stationary, cells:auc_e) %>%
  mutate(Hours = ifelse(is.na(Hours), stationary, Hours))
```

# Organic Carbon

## Import and Tidy Data

We will need to tidy the data in the same way the bacterial abundance dataframe was tidied before merging the datasets. We'll then omit data low quality data i.e. poor replication or possible contamination. We observed contamination in many of the NAAMES 2 experiments after incubations were transferred to WHOI.

```{r message = F}
oc.df <- read_csv("~/naames_bioav_ms/Input/N2-4_DOC_Remin_Master.csv") %>%
  mutate(Season = Cruise,
         Season = gsub("AT34", "Late Spring", Season),
         Season = gsub("AT38", "Early Autumn", Season),
         Season = gsub("AT39", "Early Spring", Season),
         Treatment = ifelse(Bottle == "Niskin", "Niskin", Treatment),
         Treatment = ifelse(Bottle == "GF75", "GF75", Treatment),
         Treatment = gsub("TW15", "TW20", Treatment),
         Treatment = ifelse(is.na(Treatment), Bottle, Treatment),
         Treatment = ifelse(Treatment %in% c("Surface", "Deep"), "Parallel", Treatment),
         Treatment = ifelse(Treatment %in% c("100mls", "250mls", "500mls", "1L"), "Volume", Treatment),
         Treatment_Btl = ifelse(Bottle == "Niskin", "Niskin", Treatment_Btl),
         Treatment_Btl = ifelse(Bottle == "GF75" & is.na(Treatment_Btl), "GF75", Treatment_Btl),
         Treatment_Btl = gsub("TW15", "TW20", Treatment_Btl),
         Treatment_Btl = gsub("TW12-A", "TW12-C", Treatment_Btl),
         Treatment_Btl = gsub("TW12-B", "TW12-D", Treatment_Btl),
         Treatment_Btl = gsub("TW13-A", "TW12-E", Treatment_Btl),
         Treatment_Btl = gsub("TW13-B", "TW12-F", Treatment_Btl),
         Treatment_Btl = ifelse(is.na(Treatment_Btl), Bottle, Treatment_Btl),
         Bottle = gsub("SA", "A", Bottle),
         Bottle = gsub("SB", "B", Bottle),
         Bottle = gsub("DA", "C", Bottle),
         Bottle = gsub("DB", "D", Bottle),
         Bottle = ifelse(Bottle == "GF75", Treatment_Btl, Bottle),
         Bottle = gsub("Control-", "", Bottle),
         Bottle = gsub("TW12-", "", Bottle),
         Bottle = gsub("TW13-", "", Bottle),
         Bottle = gsub("MixDS-", "", Bottle),
         Bottle = gsub("MixSD-", "", Bottle),
         Bottle = gsub("SynExd-", "", Bottle),
         Bottle = gsub("TWExd-", "", Bottle),
         Bottle = gsub("SynLys-", "", Bottle),
         Bottle = gsub("TW5-", "", Bottle),
         Bottle = gsub("TW10-", "", Bottle),
         Bottle = gsub("TW20-", "", Bottle),
         Bottle = gsub("12", "", Bottle),
         Bottle = gsub("13", "", Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW12" & Bottle == "A", gsub("A", "C", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW12" & Bottle == "B", gsub("B", "D", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW13" & Bottle == "A", gsub("A", "E", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW13" & Bottle == "B", gsub("B", "F", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "Control" & Bottle == "C", gsub("C", "G", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "Control" & Bottle == "D", gsub("D", "H", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW12" & Bottle == "C", gsub("C", "I", Bottle),Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW12" & Bottle == "D", gsub("D", "J", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW13" & Bottle == "C", gsub("C", "K", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW13" & Bottle == "D", gsub("D", "L", Bottle), Bottle),
         Depth = gsub(5, 10, Depth),
         Depth = as.numeric(Depth),
         key = paste(Cruise, Station, Depth, Treatment, Bottle, Timepoint, sep = "."),
         PTOC_ave = ifelse(Treatment == "Parallel", TOC_ave, PTOC_ave),
         PTOC_sd = ifelse(Treatment == "Parallel", TOC_sd, PTOC_sd)) %>% 
  rename(doc = DOC_ave,
         sd_doc = DOC_sd,
         toc = TOC_ave, 
         sd_toc = TOC_sd, 
         ptoc = PTOC_ave, 
         sd_ptoc = PTOC_sd, 
         pdoc = PDOC_ave, 
         sd_pdoc = PDOC_sd) %>%
  filter(!Treatment %in% c("Niskin", "GF75", "TFF-Ret", "Volume")) %>% 
  select(-Treatment_Btl) %>% 
  select(Season, everything()) %>% 
  arrange(Cruise, Station, Depth, Treatment, Bottle, Hours)  %>% 
  filter(!is.na(Hours))

```

Because a different suite of organic carbon samples were taken on each cruise, we'll separate the cruise datasets, drop NA values, quality filter them, and then recombine the datasets. To quality filter, we'll calculate rolling ∆DOC values i.e. the diffence between the one observation and the one before it. We'll omit the data where ∆DOC indicates contamination due to transport etc. after the 21 d shipboard occupation (increase greater than our detection limit, 1.5 µmol C L^-1^).

```{r}
n2_oc <- oc.df %>% 
  filter(Cruise == "AT34") %>% 
  drop_na(doc) %>%
  group_by(Station, Depth, Treatment, Bottle) %>%
  mutate(doc_from_last = lag(doc) - doc) %>% 
  filter(!doc_from_last <= -1.5 | is.na(doc_from_last) | !Hours > 504)  %>% 
  mutate(doc_from_last = lag(doc) - doc) %>% 
  filter(!doc_from_last <= -1.5 | is.na(doc_from_last) | !Hours > 504) %>% 
  mutate(doc_from_last = lag(doc) - doc) %>% 
  filter(!doc_from_last <= -1.5 | is.na(doc_from_last) | !Hours > 504) %>% 
  mutate(doc_from_last = lag(doc) - doc,
         doc_from_t0 = first(doc) - doc) %>% 
  filter(!Station == 4 | !Hours == 192) %>% 
  ungroup()

n3_4_oc <- oc.df %>% 
  filter(!Cruise == "AT34") %>% 
  drop_na(ptoc) %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle) %>% 
  mutate(ptoc_from_last = lag(ptoc) - ptoc) %>% 
  filter(!ptoc_from_last <= -1.5 | is.na(ptoc_from_last) | !Hours > 504) %>% 
  mutate(ptoc_from_last = lag(ptoc) - ptoc,
         ptoc_from_t0 = first(ptoc) - ptoc,
         doc_from_t0 = first(doc) - doc,
         toc_from_t0 = first(toc) - toc, 
         pdoc_from_t0 = first(pdoc) - pdoc) %>%
  ungroup()

oc_p <- bind_rows(n2_oc, n3_4_oc) %>% 
  mutate(Days = round(Hours/24, 1),
         facet_depth = paste(Depth, "m"), 
         facet_treatment = Treatment, 
         facet_treatment = gsub("MixSD", "Surface Comm., Deep DOM", facet_treatment),
         facet_treatment = gsub("MixDS", "Deep Comm., Surface DOM", facet_treatment),
          facet_treatment = gsub("SynExd", "Synechococcus Exudate", facet_treatment),
         facet_treatment = gsub("SynLys", "Synechococcus Lysate", facet_treatment),
          facet_treatment = gsub("TWExd", "T. Weissflogii Exudate", facet_treatment),
         facet_treatment = gsub("TW5", "+5 µmol C/L Exudate", facet_treatment),
          facet_treatment = gsub("TW10", "+10 µmol C/L Exudate", facet_treatment),
          facet_treatment = gsub("TW20", "+20 µmol C/L Exudate", facet_treatment),
           facet_treatment = gsub("TW12", "T. Weissflogii 12C Exudate", facet_treatment),
          facet_treatment = gsub("TW13", "T. Weissflogii 13C Exudate", facet_treatment),
         facet_bottle = Bottle,
         facet_bottle = gsub("W", "Whole Seawater", facet_bottle),
          facet_bottle = gsub("1.2", "1.2 µm Filtrate", facet_bottle), 
          facet_bottle = gsub("NV", "1.2 µm Filtrate: TFF Filtrate (3:7)", facet_bottle)) 

oc_p$Treatment <- factor(oc_p$Treatment, levels = levels)
oc_p$facet_treatment <- factor(oc_p$facet_treatment, levels = levels)
oc_p$facet_bottle <- factor(oc_p$facet_bottle, levels = levels)
```

## Plot Curves

### NAAMES 2

#### No Addition: Long-term

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT34", Treatment == "Control") %>% 
  mutate(facet_depth = paste(Depth, "m")) %>% 
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = doc, group = Bottle)) + 
  geom_errorbar(aes(ymin = doc - sd_doc, ymax = doc + sd_doc), width = 0.5) +
  geom_point(aes(fill = Bottle), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Bottle), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(Station~facet_depth, scales = "free") +
  labs(y = expression(paste("DOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 2 DOC") + 
  guides(color = F)

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT34", Treatment == "Control") %>% 
  mutate(facet_depth = paste(Depth, "m")) %>% 
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = -doc_from_t0, group = Bottle)) + 
  geom_point(aes(fill = Bottle), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Bottle), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(Station~facet_depth, scales = "free_y") +
  labs(y = expression(paste("Delta DOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 2 DOC") + 
  guides(color = F)

```

#### No Addition: Short-term

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT34", Treatment == "Control") %>% 
  mutate(facet_depth = paste(Depth, "m")) %>% 
  filter(Days < 10) %>% 
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = doc, group = Bottle)) + 
  geom_errorbar(aes(ymin = doc - sd_doc, ymax = doc + sd_doc), width = 0.5) +
  geom_point(aes(fill = Bottle), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Bottle), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(Station~facet_depth, scales = "free") +
  labs(y = expression(paste("DOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 2 DOC") + 
  guides(color = F)

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT34", Treatment == "Control") %>% 
  mutate(facet_depth = paste(Depth, "m")) %>% 
  filter(Days < 10) %>% 
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = -doc_from_t0, group = Bottle)) + 
  geom_point(aes(fill = Bottle), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Bottle), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(Station~facet_depth, scales = "free_y") +
  labs(y = expression(paste("Delta DOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 2 DOC") + 
  guides(color = F)

```

#### Additions

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT34", Station == 2) %>% 
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = doc, group = Bottle)) + 
  geom_errorbar(aes(ymin = doc - sd_doc, ymax = doc + sd_doc), width = 0.5) +
  geom_point(aes(fill = facet_treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = facet_treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~facet_depth, scales = "free_y") +
  labs(y = expression(paste("DOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 2 Station 2 Experiment") + 
  guides(color = F)

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT34", Station == 2) %>% 
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = -doc_from_t0, group = Bottle)) + 
  geom_point(aes(fill = facet_treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = facet_treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~facet_depth, scales = "free_y") +
  labs(y = expression(paste("Delta DOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 2 Station 2 Experiment") + 
  guides(color = F)

```

There looks to be some poor replication between the experiments conducted at station 4 and U:

- S4 bottle A measurements look suspect. additionally, the increase between day 6 and 7 for both bottles are suspect
- SU bottle B measurements at 24 h is suspect relative to the downward trend in both bottles

These points will affect BGE calculations and my need to be omitted. The BGE from S4 Bottle A may be unreliable. 

BGEs cannot be calculated for the 200 m control experiments given that not DOC drawdown was observed.


### NAAMES 3

#### No Additions

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT38", Treatment == "Control") %>%  
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = ptoc, group = Bottle)) + 
  geom_errorbar(aes(ymin = ptoc - sd_ptoc, ymax = ptoc + sd_ptoc), width = 0.5) +
  geom_point(aes(fill = Bottle), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Bottle), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(Station~facet_depth, scales = "free") +
  labs(y = expression(paste("TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 3 PTOC") + 
  guides(color = F)

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT38", Treatment == "Control") %>%  
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = -ptoc_from_t0, group = Bottle)) + 
  geom_point(aes(fill = Bottle), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Bottle), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(Station~facet_depth, scales = "free_y") +
  labs(y = expression(paste("Delta TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 3 PTOC") + 
  guides(color = F)

```

#### Mixing

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT38", Station == 1, !Treatment %in% c("SynExd", "SynLys", "TWExd")) %>%
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = ptoc, group = Bottle)) + 
  geom_errorbar(aes(ymin = ptoc - sd_ptoc, ymax = ptoc + sd_ptoc), width = 0.5) +
  geom_point(aes(fill = facet_treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = facet_treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~facet_depth, scales = "free_y") +
  labs(y = expression(paste("TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 3 Station 1 Mixing Experiment") + 
  guides(color = F)

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT38", Station == 1, !Treatment %in% c("SynExd", "SynLys", "TWExd")) %>%
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = -ptoc_from_t0, group = Bottle)) + 
  geom_point(aes(fill = facet_treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = facet_treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~facet_depth, scales = "free_y") +
  labs(y = expression(paste("Delta TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 3 Station 1 Mixing Experiment") + 
  guides(color = F)

```

#### Additions

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT38", Station == 1, Treatment %in% c("Control", "SynExd", "SynLys", "TWExd")) %>%
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = ptoc, group = Bottle)) + 
  geom_errorbar(aes(ymin = ptoc - sd_ptoc, ymax = ptoc + sd_ptoc), width = 0.5) +
  geom_point(aes(fill = facet_treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = facet_treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~facet_depth, scales = "free_y") +
  labs(y = expression(paste("TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 3 Station 1 Addition Experiment") + 
  guides(color = F)

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT38", Station == 1, Treatment %in% c("Control", "SynExd", "SynLys", "TWExd")) %>%
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = -ptoc_from_t0, group = Bottle)) + 
  geom_point(aes(fill = facet_treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = facet_treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~facet_depth, scales = "free_y") +
  labs(y = expression(paste("Delta TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 3 Station 1 Addition Experiment") + 
  guides(color = F)

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT38", Depth == 10, Station %in% c(1, 3, 6), Treatment %in% c("Control", "SynLys")) %>% 
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = ptoc, group = Bottle)) + 
  geom_errorbar(aes(ymin = ptoc - sd_ptoc, ymax = ptoc + sd_ptoc), width = 0.5) +
  geom_point(aes(fill = facet_treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = facet_treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~Station, scales = "free_y") +
  labs(y = expression(paste("TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 3 Addition Experiments") +
  guides(color = F)

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT38", Depth == 10, Station %in% c(1, 3, 6), Treatment %in% c("Control", "SynLys")) %>% 
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = -ptoc_from_t0, group = Bottle)) + 
  geom_point(aes(fill = facet_treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = facet_treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~Station, scales = "free_y") +
  labs(y = expression(paste("Delta TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 3 Addition Experiments") +
  guides(color = F)

```

### NAAMES 4

#### No Additions

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 11, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT39", Treatment == "Control") %>% 
  mutate(facet_depth = paste(Depth, "m")) %>% 
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = ptoc, group = Bottle)) + 
  geom_errorbar(aes(ymin = ptoc - sd_ptoc, ymax = ptoc + sd_ptoc), width = 0.5) +
  geom_point(aes(fill = Bottle), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Bottle), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~Station, scales = "free") +
  labs(y = expression(paste("TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 4 PTOC") +
  guides(color = F)

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 11, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT39", Treatment == "Control") %>% 
  mutate(facet_depth = paste(Depth, "m")) %>% 
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = -ptoc_from_t0, group = Bottle)) + 
  geom_point(aes(fill = Bottle), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Bottle), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~Station, scales = "free_y") +
  labs(y = expression(paste("Delta TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 4 PTOC")

```

The replication between experiments at Station 4 is poor. 

#### Additions

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT39", Station == 2, !Treatment == "Parallel") %>% 
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = ptoc, group = Bottle)) + 
  geom_errorbar(aes(ymin = ptoc - sd_ptoc, ymax = ptoc + sd_ptoc), width = 0.5) +
  geom_point(aes(fill = Treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~facet_treatment, scales = "free_y") +
  labs(y = expression(paste("TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 4 Addition Experiment") +
  guides(fill = F, color = F)

```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT39", Station == 2, !Treatment == "Parallel") %>% 
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = -ptoc_from_t0, group = Bottle)) + 
  geom_point(aes(fill = Treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~facet_treatment, scales = "free_y") +
  labs(y = expression(paste("Delta TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 4 Addition Experiment") +
  guides(fill = F, color = F)

```

#### Variable Set-Up 


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 14, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT39", Treatment %in% c("Control", "Parallel"), Depth == 10) %>% 
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = ptoc, group = Bottle)) + 
  geom_errorbar(aes(ymin = ptoc - sd_ptoc, ymax = ptoc + sd_ptoc), width = 0.5) +
  geom_point(aes(fill = facet_bottle), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = facet_bottle, linetype = Treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~Station, scales = "free") +
  labs(y = expression(paste("TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 4 Parallel Experiments") +
  guides(color = F)

```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 14, fig.align = "center", warning = FALSE}
oc_p %>% 
  filter(Cruise == "AT39", Treatment %in% c("Control", "Parallel"), Depth == 10) %>% 
  group_by(Station, Depth, Treatment, Bottle) %>%
  ggplot(aes(x = Days, y = -ptoc_from_t0, group = Bottle)) + 
  geom_point(aes(fill = facet_bottle), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = facet_bottle, linetype = Treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~Station, scales = "free_y") +
  labs(y = expression(paste("Delta TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 4 Parallel Experiments") +
  guides(color = F)

```


# Bacterial Carbon

POC from DOC remineralization bioassays was estimated by filtering cells onto double-stacked GF75 filters (0.3 µm pore size) and then running each filter on an elemental analyzer at Bigelow (Maine). This document shows how bacterial carbon estimates were calculated from those measurements.

Upon importing the dataset, we'll add two categorical variables that indicate what type of filtrate was used as the "blank" water. On NAAMES 2, 0.2 µm-filtered water was used and on NAAMES 4, TFF-filtered water was used. Unfortunately, blanks were not taken on NAAMES 3. 

```{r message = F}

bigelow <- read_csv("~/naames_bioav_ms/Input/N2-4_BactC_Processing.csv") %>% 
  select(-c(Treatment_Btl:Days)) %>% 
  rename(Filter = Rep) %>% 
  mutate(BlnkFiltrate = ifelse(Cruise == "AT34", "0.2 µm", "TFF"),
         BlnkFiltrate = ifelse(Cruise == "AT38", NA, BlnkFiltrate),
         facetlabel = paste(Depth, " m"),
         Season = Cruise,
         Season = gsub("AT34", "Late Spring", Season),
         Season = gsub("AT38", "Early Autumn", Season),
         Season = gsub("AT39", "Early Spring", Season),
         Treatment = ifelse(is.na(Treatment), "Niskin", Treatment),
         Treatment = ifelse(Bottle %in% c("SA13", "SB13", "DA13", "DB13"), "TW13", Treatment),
         Bottle = gsub("SA", "A", Bottle),
         Bottle = gsub("SB", "B", Bottle),
         Bottle = gsub("DA", "C", Bottle),
         Bottle = gsub("DB", "D", Bottle), 
         Timepoint = ifelse(Treatment == "Niskin", 0, Timepoint)
         ) %>% 
  mutate_at(vars(BactN_µg, BactC_µg), round, 1)

bigelow$Season <- factor(bigelow$Season, levels = levels)
```

## Determine Blank Values

```{r}
blank.data <- bigelow %>% 
  filter(Bottle == "Blank") 
```

### Filter 1 Summary Statistics

```{r}
blank.data %>% 
  filter(Filter == 1) %>% 
  select(BactC_µg) %>% 
  summary()
```

### Filter 2 Summary Statistics

```{r}
blank.data %>% 
  filter(Filter == 2) %>% 
  select(BactC_µg) %>% 
  summary()
```

In the filter 2 set, the filter value of 6.46 appears to be an outlier relative to all the other filters (across cruises and filtrate types), indicating possible contamination or the compromised integrity of the first filter. This sample (filter 1 & 2), will be omitted from analysis.

### Revised Filter 1 Summary Statistics

```{r}
blank.data %>% 
  filter(Filter == 1, !Season == "Late Spring" | !Station == 1 | !Depth == 10) %>% 
  select(BactC_µg) %>% 
  summary()
```

### Revised Filter 2 Summary Statistics

```{r}
filter2.sum <- blank.data %>% 
  filter(Filter == 2, !Season == "Late Spring" | !Station == 1 | !Depth == 10) %>% 
  select(BactC_µg) %>% 
  summary()
```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}

blank.data %>% 
  filter(!Season == "Late Spring" | !Station == 1 | !Depth == 10) %>% 
  ggplot(aes(x = Season, y = BactC_µg)) + 
  geom_boxplot(width = 0.3, aes(group = Season)) +
  geom_jitter(width = 0.1, size = 6, alpha = 0.7, 
              aes(colour = factor(Filter),
                  shape = BlnkFiltrate)) + 
  labs(x = "", y = expression(italic("POC, µg C")), colour = expression(italic("Filter")), shape = expression(italic("Blank Filtrate"))) + 
  scale_colour_brewer(palette = "Set1") +
  custom_theme() +
  facet_wrap(~facetlabel)

```

This plot shows greater variability in the POC values from the first blank filter (red points). Whether using surface or deep water, 0.2 µm filtrate or TFF filtrate, the small range in the POC values of the second filter indicates that the second filter provides a reasonable estimate of DOC adsorption onto GF75s. 

## Blank Corrections and Bacterial Carbon Estimates

The mean of all blank water filter 2 POC values will be used as a universal correction factor. It will be subtracted from each sample filter to estimate bacterial carbon in µg. Values below the detection limits for N (<0.1) are converted to 0. The addition of the corrected value from filter 1 and from filter 2 of each sample will provide the bacterial carbon estimate for that sample.

Bacterial carbon estimates will then be converted to µmol C^-1^. The same will be done for PON.

```{r}
corrfactor <- blank.data %>% 
  filter(Filter == 2, !Season == "Late Spring" | !Station == 1 | !Depth == 10) %>% 
  mutate(ave_c_blank = round(mean(BactC_µg),1),
         ave_n_blank = round(mean(BactN_µg),1)) %>% 
  select(ave_c_blank, ave_n_blank) %>% 
  distinct()

corrfactor
```

```{r}
bactcarbon <- bigelow %>%
  filter(!Bottle == "Blank") %>%
  cbind(., corrfactor) %>% 
  mutate(c_corr = BactC_µg - ave_c_blank,
         c_corr = ifelse(c_corr < 0, 0, c_corr), 
         n_corr = BactN_µg - ave_n_blank,
         n_corr = ifelse(n_corr < 0.1, 0, n_corr)) %>%
  group_by(Cruise, Station, Depth, Bottle, Timepoint) %>% 
  mutate(bactC = round((sum(c_corr))/12,1),
         bactN = round((sum(n_corr))/14,1),
         bactC_N = ifelse(bactN > 0, round(bactC/bactN,1), NA),
         total_cell_c_µg = round((sum(c_corr)),1)) %>% 
  ungroup() %>% 
  select(-c(Filter, BlnkFiltrate, BactN_µg, BactC_µg, ave_c_blank:n_corr)) %>% 
  select(Season, Cruise, Station, Depth, facetlabel, Treatment, everything()) %>% 
  distinct() %>% 
  arrange(Season, Cruise, Station, Depth, Treatment, Timepoint) %>% 
  mutate(Treatment = ifelse(Bottle %in% c("1L", "100mls", "250mls", "500mls"), "Volume", Treatment))
```

## Sampling Volume Effect on Bacterial Carbon

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6, fig.align = "center", warning = FALSE}
bactcarbon %>% 
  filter(Treatment == "Volume") %>% 
  select(Bottle, bactC, bactN) %>% 
  gather(key, value, bactC, bactN) %>% 
  mutate(Bottle = gsub("100mls", "0.10 L", Bottle),
         Bottle = gsub("250mls", "0.25 L", Bottle),
         Bottle = gsub("500mls", "0.50 L", Bottle),
         Bottle = gsub("1L", "1.00 L", Bottle),
         key = gsub("bactC", "Carbon", key),
         key = gsub("bactN", "Nitrogen", key)) %>% 
  arrange(key, Bottle) %>% 
  mutate(norm_value = ifelse(Bottle == "0.10 L", value * 0.1, value),
         norm_value = ifelse(Bottle == "0.25 L", value * 0.25, norm_value),
         norm_value = ifelse(Bottle == "0.50 L", value * 0.5, norm_value),
         norm_value = ifelse(Bottle == "1 L", value * 1, norm_value)) %>% 
  ggplot(aes(x = Bottle, y = norm_value, group = key)) + 
  geom_point(aes(fill = key), shape = 21, size = 6, alpha = 0.7) +
  labs(x = "Volume Filtered", y = expression(italic("Bacterial Carbon or Nitrogen, µmols"))) + 
  scale_fill_manual(values = custom.colors) +
  custom_theme() 
```

This test needs to be done again #flattenthecurve

## Calculate Carbon Per Cell

Here we calculate fg C or fg N cell^-1^ by:

- Estimating the cell abundance captured on the 0.3 µm GF75 filters (whole water - filtrate, cells L^-1^) 
- Dividing the GF75 POC or PON value (µmol C or N L^-1^) (see Bacterial_Carbon.Rmd) by the cell abundance on the GF75 filter, then applying the subsequent conversions

The GF75 POC data is tidied before calculations are made (e.g renaming bottle identifiers so they are congruent with datasets to be merged with, duplicating values for initial timepoints where one POC value was taken for replicate bottles). For ease, initial POC and cell abundance data are handled separately from data collected at stationary timepoints. 

### Calculate Filter Cell Abundance and Retention

```{r}
#initial cell abundance
gf75.t0 <- ba.df %>% 
  select(Season:cells) %>% 
  filter(Timepoint == 0, Bottle %in% c("GF75", "Niskin")) %>% 
  group_by(Cruise, Station, Depth) %>% 
  mutate(filtrate_cells = ifelse(Bottle == "GF75", cells, NA)) %>% 
  fill(filtrate_cells, .direction = "downup") %>% 
  filter(Bottle == "Niskin") %>% 
  mutate(initial_gf75_cells = cells - filtrate_cells,
         initial_gf75_retention = round((cells - filtrate_cells)/cells, 2)) %>% 
  ungroup() %>% 
  select(Season:Depth, initial_gf75_cells, initial_gf75_retention)

#stationary cell abundance
gf75.st <- ba.df %>% 
  select(Season:cells) %>% 
  filter(!Timepoint == 0) %>% 
  arrange(Cruise, Station, Depth, Bottle, Timepoint) %>% 
  group_by(Cruise, Station,  Depth, Bottle) %>%
  mutate(gf75_timepoint = ifelse(Treatment == "GF75", Timepoint, NA)) %>% 
  fill(gf75_timepoint, .direction = "updown") %>% 
  filter(Timepoint == gf75_timepoint) %>% 
  mutate(filtrate_cells = ifelse(Treatment == "GF75", cells, NA)) %>% 
  fill(filtrate_cells, .direction = "updown") %>%  
  filter(!Treatment == "GF75") %>% 
  mutate(stationary_gf75_cells = cells - filtrate_cells,
         stationary_gf75_retention = round((cells - filtrate_cells)/cells, 2)) %>% 
  ungroup() %>% 
  select(Season:Bottle, Treatment, stationary_gf75_cells, stationary_gf75_retention)
```


### Combine Cell Abundance and POC Data, Calculate CCF
 
```{r message = F}
bc.df <- bactcarbon %>% 
  filter(!Treatment == "Volume") %>% 
  select(Season, Cruise, Station, Depth, Treatment:total_cell_c_µg)

#initial timepoints
fg_cell.t0 <- bc.df %>% 
  filter(Timepoint == 0) %>% 
  select(-c(Treatment:Timepoint)) %>% 
  mutate(Station = gsub("2RD", "S2RD", Station),
         Station = gsub("2RF", "S2RF", Station)) %>% 
  left_join(., gf75.t0) %>% 
  mutate(initial_ccf = round(bactC/initial_gf75_cells * 12 * 10^9),
         initial_ncf = round(bactN/initial_gf75_cells * 14 * 10^9, 1)) %>% 
  rename(initial_bactC = bactC,
         initial_bactN = bactN,
         initial_bactC_N = bactC_N,
         initial_total_cell_c_µg = total_cell_c_µg) %>% 
  select(Season:Depth, initial_bactC:initial_ncf) %>% 
  ungroup()

#stationary timepoints
fg_cell.st <- bc.df %>% 
  filter(!Timepoint == 0) %>% 
  select(Season:Bottle, bactC:total_cell_c_µg) %>% 
  mutate(Station = gsub("2RD", "S2RD", Station),
         Station = gsub("2RF", "S2RF", Station),
         Treatment = gsub("TW15", "TW20", Treatment),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW12" & Bottle == "A12", gsub("A12", "C", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW12" & Bottle == "B12", gsub("B12", "D", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW13" & Bottle == "A13", gsub("A13", "E", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 10 & Treatment == "TW13" & Bottle == "B13", gsub("B13", "F", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "Control" & Bottle == "C", gsub("C", "G", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "Control" & Bottle == "D", gsub("D", "H", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW12" & Bottle == "C12", gsub("C12", "I", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW12" & Bottle == "D12", gsub("D12", "J", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW13" & Bottle == "C13", gsub("C13", "K", Bottle), Bottle),
         Bottle = ifelse(Cruise == "AT34" & Station == 2 & Depth == 200 & Treatment == "TW13" & Bottle == "D13", gsub("D13", "L", Bottle), Bottle)) %>% 
  add_row(Season = "Early Autumn", Cruise = "AT38", Station = 1, Depth = 10, Treatment = "SynExd", Bottle = "I") %>% 
    add_row(Season = "Early Autumn", Cruise = "AT38", Station = 1, Depth = 10, Treatment = "SynLys", Bottle = "N") %>% 
  add_row(Season = "Early Autumn", Cruise = "AT38", Station = 1, Depth = 10, Treatment = "TWExd", Bottle = "K") %>% 
  add_row(Season = "Early Autumn", Cruise = "AT38", Station = 1, Depth = 200, Treatment = "SynLys", Bottle = "P") %>% 
  arrange(Cruise, Station, Depth, Treatment, Bottle) %>% 
  group_by(Cruise, Station, Depth, Treatment) %>% 
  fill(bactC:bactN, .direction = "updown") %>% 
  mutate(bactN = ifelse(Cruise == "AT38" & Treatment == "MixDS" & Bottle == "C", NA, bactN),
         bactN = ifelse(Cruise == "AT38" & Station == 6 & Treatment == "SynLys" & Bottle == "C", NA, bactN), 
         Bottle = gsub("JI", "J", Bottle),
         Bottle = gsub("MN", "M", Bottle),
         Bottle = gsub("LK", "L", Bottle),
         Bottle = gsub("OP", "O", Bottle),
         bactC_N = ifelse(bactN > 0, round(bactC/bactN, 1), NA)) %>% 
  left_join(., gf75.st) %>% 
  mutate(stationary_ccf = round((bactC/stationary_gf75_cells) * 12 * 10^9),
         stationary_ncf = round((bactN/stationary_gf75_cells) * 14 * 10^9, 1)) %>%
  rename(stationary_bactC = bactC,
         stationary_bactN = bactN,
         stationary_bactC_N = bactC_N,
         stationary_total_cell_c_µg = total_cell_c_µg) %>% 
  select(Season:Bottle, stationary_bactC:stationary_ncf) %>% 
  ungroup()

fg_cell <- left_join(fg_cell.st, fg_cell.t0) %>% 
  select(Season:Bottle, initial_bactC_N:initial_ncf, everything())

fg_cell$Season <- factor(fg_cell$Season, levels = levels)
  

```

### Plot Retention of GF75 Filters

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
fg_cell %>% 
  select(Season, Station, Depth, Treatment, initial_gf75_retention, stationary_gf75_retention) %>% 
  mutate(facet_depth = paste(Depth, "m")) %>% 
  gather(key, value, initial_gf75_retention:stationary_gf75_retention) %>% 
  mutate(key = gsub("initial_gf75_retention", "Initial", key),
         key = gsub("stationary_gf75_retention", "Stationary", key)) %>% 
  ggplot(aes(x = Season, y = value)) + 
  geom_boxplot(width = 0.3) +
  geom_jitter(aes(fill = key), width = 0.1, shape = 21, size = 6, alpha = 0.7) + 
  labs(x = "", y = expression(italic("Bacterioplankton Fraction Retained on GF75")), colour = expression(italic(""))) + 
  scale_fill_brewer(palette = "Set1") +
  custom_theme() +
  facet_wrap(~facet_depth)

```

This figure shows that while GF75 filter retention is fairly consistent across the samples taken during the stationary phase of cell growth (median 85%, mean 83%), they are pretty variable for the samples taken at the initial condition (median 73%, mean 66%, range 10 - 88%, 1st Qu = 56%). Those samples with filter retentions <= 0.56 (1st Qu.) likely reflect faulty procedure (i.e. ripped filters) and may be associated with questionable measurements.

### QC Data

As a result, we will replace the C:N, CCF, and NCF values of those samples with the following criteria:

- If samples were taken from the initial condition, values will be replaced by cruise means. 
- If samples were taken from the stationary phase, values will be replaced with those taken from the replicate sample from the same treatment if possible. There are 3 sets of experiments that do not have conversion factors for the stationary phase of either replicate bottle: AT34 S3 200 m, AT38 S1 MixDS, AT38 S1 MixSD.
  + For AT34 S3 200 m, the mean value of samples taken from stationary in the 200 m control experiments of AT34 will be used
  + For AT38 S1 MixDS, the mean value of samples taken from stationary in the deep-deep incubations will be used (cell growth is similar)
  + For AT38 S1 MixSD, the mean value of samples taken from stationary in the surface-surface incubations will be used (cell growth is similar)


```{r}
fg_cell.rm <- fg_cell %>% 
  mutate(initial_bactC = ifelse(initial_gf75_retention <= 0.56, NA, initial_bactC),
         initial_bactN = ifelse(initial_gf75_retention <= 0.56, NA, initial_bactN),
         initial_bactC_N = ifelse(initial_gf75_retention <= 0.56, NA, initial_bactC_N),
         initial_ccf = ifelse(initial_gf75_retention <= 0.56, NA, initial_ccf),
         initial_ncf = ifelse(initial_gf75_retention <= 0.56, NA, initial_ncf),
         stationary_bactC = ifelse(stationary_gf75_retention <= 0.56, NA, stationary_bactC),
          stationary_bactN = ifelse(stationary_gf75_retention <= 0.56, NA, stationary_bactN),
          stationary_bactC_N = ifelse(stationary_gf75_retention <= 0.56, NA, stationary_bactC_N),
         stationary_ccf = ifelse(stationary_gf75_retention <= 0.56, NA, stationary_ccf),
         stationary_ncf = ifelse(stationary_gf75_retention <= 0.56, NA, stationary_ncf)) 

```

```{r}
fg_cell.qc <- fg_cell.rm %>% 
  group_by(Season) %>% 
  mutate(Depth = as.numeric(Depth),
         Depth = ifelse(Treatment == "MixDS", 200, Depth),
         Depth = ifelse(Treatment == "MixSD", 10, Depth),
         mean_initial_bactC = round(mean(initial_bactC, na.rm = T), 1),
         mean_initial_bactN = round(mean(initial_bactN, na.rm = T), 1),
         mean_initial_bactC_N = round(mean(initial_bactC_N, na.rm = T), 1),
         mean_initial_ccf = round(mean(initial_ccf, na.rm = T)),
         mean_initial_ncf = round(mean(initial_ncf, na.rm = T), 1),
           initial_bactC = ifelse(is.na(initial_bactC), mean_initial_bactC, initial_bactC),
           initial_bactN = ifelse(is.na(initial_bactN), mean_initial_bactN, initial_bactN),
         initial_bactC_N = ifelse(is.na(initial_bactC_N), mean_initial_bactC_N, initial_bactC_N),
         initial_ccf = ifelse(is.na(initial_ccf), mean_initial_ccf, initial_ccf),
         initial_ncf = ifelse(is.na(initial_ncf), mean_initial_ncf, initial_ncf)) %>% 
  ungroup() %>% 
  group_by(Cruise, Station, Depth, Treatment) %>% 
  fill(c(stationary_bactC, stationary_bactN, stationary_bactC_N, stationary_ccf, stationary_ncf), .direction = "downup") %>%
  ungroup() %>% 
  group_by(Cruise, Depth, Treatment) %>% 
  mutate(mean_stationary_ccf = round(mean(stationary_ccf, na.rm = T)),
         mean_stationary_ncf = round(mean(stationary_ncf, na.rm = T)),
         stationary_ccf = ifelse(is.na(stationary_ccf), mean_stationary_ccf, stationary_ccf),
         stationary_ncf = ifelse(is.na(stationary_ncf), mean_stationary_ncf, stationary_ncf)) %>% 
ungroup() %>% 
   group_by(Cruise, Station, Depth, Treatment) %>% 
  mutate(mean_stationary_ccf = round(mean(stationary_ccf, na.rm = T)),
         mean_stationary_ncf = round(mean(stationary_ncf, na.rm = T)),
         stationary_ccf = ifelse(Treatment == "MixDS", 34, stationary_ccf),
         stationary_ncf = ifelse(Treatment == "MixDS", 6, stationary_ncf),
         stationary_ccf = ifelse(Treatment == "MixSD", 42, stationary_ccf),
         stationary_ncf = ifelse(Treatment == "MixSD", 5, stationary_ncf),
         ) %>% 
  ungroup() 

```

### Plot CCFs and C:N ratios

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
fg_cell.rm %>% 
  select(Season, Station, Depth, Treatment, initial_ccf, stationary_ccf) %>% 
  mutate(facet_depth = paste(Depth, "m")) %>% 
  gather(key, value, initial_ccf:stationary_ccf) %>% 
  mutate(key = gsub("initial_ccf", "Initial", key),
         key = gsub("stationary_ccf", "Stationary", key)) %>% 
  ggplot(aes(x = Season, y = value)) + 
  geom_boxplot(width = 0.3) +
  geom_jitter(aes(fill = key), width = 0.1, shape = 21, size = 6, alpha = 0.7) + 
  labs(x = "", y = expression(italic("CCF, fg C cell"^-1)), colour = expression(italic(""))) + 
  scale_fill_brewer(palette = "Set1") +
  custom_theme() +
  facet_wrap(~facet_depth) + 
  ggtitle("Carbon Conversion Factors")

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
fg_cell.rm %>% 
  select(Season, Station, Depth, Treatment, initial_bactC_N, stationary_bactC_N) %>% 
  mutate(facet_depth = paste(Depth, "m")) %>% 
  gather(key, value, initial_bactC_N:stationary_bactC_N) %>% 
  mutate(key = gsub("initial_bactC_N", "Initial", key),
         key = gsub("stationary_bactC_N", "Stationary", key)) %>% 
  ggplot(aes(x = Season, y = value)) + 
  geom_boxplot(width = 0.3) +
  geom_jitter(aes(fill = key), width = 0.1, shape = 21, size = 6, alpha = 0.7) + 
  labs(x = "", y = expression(italic("C:N")), colour = expression(italic(""))) + 
  scale_fill_brewer(palette = "Set1") +
  custom_theme() +
  facet_wrap(~facet_depth) + 
  ggtitle("Bacterioplankton C:N")

```

```{r echo = FALSE, results = 'asis'}
fg_cell.rm %>% 
  select(initial_bactC_N:stationary_ncf) %>% 
  summary()
```


Overall, the mean bacterial C:N ratios for the in situ community (initial condition) estimated here are higher than those reported for oceanic bacteria by Fukuda et al. (1998): $$6.8 \pm 1.2$$

The mean aveage contents of carbon and nitrogen are also higher than those reported by Fukuda et al. (1998): $$12.4 \pm 6.3$$ and $$2.1 \pm 1.1$$ fg cell^-1^

These deviations from Fukuda et al. may be in part due to differences in sampling locations (NA v Pacific and Southern Ocean) and time of collection (range of seasons for NAAMES, winter in both Pacific and Southern Ocean). They could also be due to differences in growth conditions (i.e nutrient limitation) and differences in bacterial communities (Vrede et al 2002).

# Biovolume

Cell biovolume was determined from 10 images captured with a digital camera (Retiga Exi-QImaging, Surrey, BC, Canada). Images were processed using ImageJ software according to established image analyses protocols (Baldwin and Bankston 1988; Sieracki et al. 1989, Ducklow et al., 1995). In addition to calculating cell carbon using GF75 POC-derived CCFs, we'll also caclulate cell carbon based on the biovolume measurements we have. Biovolume-based cell carbon will be calculated as: **Bacterial Abundance * Cell Biovolume * CCF of 148 fg C µm^-3^** 

```{r message = F}

biovol <- read_csv("~/naames_bioav_ms/Input/Biovolume_Summary.csv") %>% 
  select(Cruise:Timepoint, Biovol_Mean_All) %>% 
  rename(biovol = Biovol_Mean_All) %>% 
  mutate_at(vars(biovol), round, 3) %>% 
  mutate(phase = ifelse(Timepoint == 0, "initial", "stationary"),
         Station = gsub("2RD", "S2RD", Station),
         Station = gsub("2RF", "S2RF", Station)) %>% 
  group_by(phase) %>% 
  mutate(mean_biovol = round(mean(biovol, na.rm = T),3),
         sd_biovol = round(sd(biovol, na.rm = T),3)) %>% 
  add_tally() %>% 
  rename(n_biovol = n) %>% 
  select(Cruise, phase:n_biovol) %>% 
  ungroup() %>% 
  add_row(Cruise = "AT34", phase = "initial") %>% 
  add_row(Cruise = "AT34", phase = "stationary") %>% 
  group_by(phase) %>% 
  fill(mean_biovol:n_biovol) %>% 
  ungroup() %>% 
  distinct() 

biovol_table <- biovol %>% select(-Cruise) %>% distinct()

biovol_merge <- biovol %>% 
  select(Cruise, phase, mean_biovol) %>% 
  spread(., phase, mean_biovol) %>% 
  rename(initial_biovol = initial,
         stationary_biovol = stationary)

```

```{r echo = FALSE, results = 'asis'}
kable(biovol_table, caption = "Mean Biovolume AT38, AT39")
```

As in Gunderson et al (2002), we'll see if there is a log-linear relationship between the cell carbon calculated from the GF75 POC data (fg C L^-1^) and the estimated biovolumes (µm^3^). We'll use data from the initial condition of the surface bioassys. 

```{r message = F, warning = F}

biovol_plot_data <- read_csv("~/naames_bioav_ms/Input/Biovolume_Summary.csv") %>%
  select(Cruise:Timepoint, Biovol_Mean_All) %>% 
  rename(biovol = Biovol_Mean_All) %>% 
  mutate(Station = gsub("2RD", "S2RD", Station),
         Station = gsub("2RF", "S2RF", Station)) %>% 
  mutate_at(vars(biovol), round, 3) %>% 
  group_by(Cruise, Station, Bottle) %>% 
  mutate(last_tp = last(Timepoint)) %>% 
  filter(Timepoint == 0 | Timepoint == last_tp) %>% 
  ungroup() %>% 
  mutate(phase = ifelse(Timepoint == 0, "initial", "stationary")) %>% 
  select(-c(Timepoint, last_tp)) 

bact_C_gather <- fg_cell.qc %>% 
  filter(Depth == 10) %>%  
  select(Season:Bottle, initial_bactC, stationary_bactC) %>% 
  gather(phase, bact_C, initial_bactC, stationary_bactC, -c(Season:Bottle)) %>% 
  mutate(phase = gsub("initial_bactC", "initial", phase),
         phase = gsub("stationary_bactC", "stationary", phase))

bact_N_gather <- fg_cell.qc %>% 
  filter(Depth == 10) %>%  
  select(Season:Bottle, initial_bactN, stationary_bactN) %>% 
  gather(phase, bact_N, initial_bactN, stationary_bactN, -c(Season:Bottle)) %>% 
  mutate(phase = gsub("initial_bactN", "initial", phase),
         phase = gsub("stationary_bactN", "stationary", phase))


bact_C_N_gather <- fg_cell.qc %>% 
  filter(Depth == 10) %>%  
  select(Season:Bottle, initial_bactC_N, stationary_bactC_N) %>% 
  gather(phase, bact_C_N, initial_bactC_N, stationary_bactC_N, -c(Season:Bottle)) %>% 
  mutate(phase = gsub("initial_bactC_N", "initial", phase),
         phase = gsub("stationary_bactC_N", "stationary", phase)) 

total_cell_c_gather <- fg_cell.qc %>% 
  filter(Depth == 10) %>%  
  select(Season:Bottle, initial_total_cell_c_µg, stationary_total_cell_c_µg) %>% 
  gather(phase, total_cell_c_µg, initial_total_cell_c_µg, stationary_total_cell_c_µg, -c(Season:Bottle)) %>% 
  mutate(phase = gsub("initial_total_cell_c_µg", "initial", phase),
         phase = gsub("stationary_total_cell_c_µg", "stationary", phase))

filter_cells_gather <- fg_cell.qc %>% 
  filter(Depth == 10) %>%  
  select(Season:Bottle, initial_gf75_cells, stationary_gf75_cells) %>% 
  gather(phase, filter_cells, initial_gf75_cells, stationary_gf75_cells, -c(Season:Bottle)) %>% 
  mutate(phase = gsub("initial_gf75_cells", "initial", phase),
         phase = gsub("stationary_gf75_cells", "stationary", phase)) 

ret_gather <- fg_cell.qc %>% 
  filter(Depth == 10) %>%  
  select(Season:Bottle, initial_gf75_retention, stationary_gf75_retention) %>% 
  gather(phase, retention, initial_gf75_retention, stationary_gf75_retention, -c(Season:Bottle)) %>% 
  mutate(phase = gsub("initial_gf75_retention", "initial", phase),
         phase = gsub("stationary_gf75_retention", "stationary", phase),
         retention = retention * 100) 

ccf_gather <- fg_cell.qc %>% 
  filter(Depth == 10) %>%  
  select(Season:Bottle, initial_ccf, stationary_ccf) %>% 
  gather(phase, ccf, initial_ccf, stationary_ccf, -c(Season:Bottle)) %>% 
  mutate(phase = gsub("initial_ccf", "initial", phase),
         phase = gsub("stationary_ccf", "stationary", phase)) 

ncf_gather <- fg_cell.qc %>% 
  filter(Depth == 10) %>%  
  select(Season:Bottle, initial_ncf, stationary_ncf) %>% 
  gather(phase, ncf, initial_ncf, stationary_ncf, -c(Season:Bottle)) %>% 
  mutate(phase = gsub("initial_ncf", "initial", phase),
         phase = gsub("stationary_ncf", "stationary", phase))

ccf_biovol <- left_join(bact_C_gather, bact_N_gather) %>%
  left_join(., bact_C_N_gather) %>% 
  left_join(., total_cell_c_gather) %>% 
  left_join(., filter_cells_gather) %>% 
  left_join(., ret_gather) %>% 
  left_join(., ccf_gather) %>% 
  left_join(., ncf_gather) %>% 
  left_join(., biovol_plot_data) %>% 
  mutate(amendment = ifelse(Treatment == "Control", F, T),
         phase = gsub("initial", "Initial", phase),
         phase = gsub("stationary", "Stationary", phase))
  
```

## Plot Biovolume v. Cell Carbon (this study and literature)

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 9, fig.align = "center", warning = FALSE}

biovol_x <-  seq(from = 0.01, to = 0.1, length.out = 23)
exports_y <-  87.4*(biovol_x^0.616)
simon_azam_y <-  92.0*(biovol_x^0.5985) #1989
gunderson_y <-  108.8*(biovol_x^0.898) #2002
malfatti_y <-  103.02*(biovol_x^0.59) #2002

lit_df <- data_frame(biovol_x, exports_y, simon_azam_y, gunderson_y, malfatti_y) 

ccf_biovol_plot.data <- ccf_biovol  %>% 
  drop_na(biovol)  %>% 
  bind_cols(., lit_df) 

ccf_biovol_plot.data %>%  
ggplot(aes(x =  biovol, y = ccf)) +
  geom_point(aes(color = Season, shape = phase), size = 4, alpha = 0.7 ) +
  labs(x = expression(paste("Biovolume, µm"^-3)), y = expression(paste("Cellular C, fg C cell"^-1))) +
  scale_x_continuous(trans = 'log10', breaks = pretty_breaks(), limits = c(0.005, 0.09)) +
  scale_y_continuous(trans = 'log10', breaks = pretty_breaks(), limits = c(1, 90)) +
  scale_color_manual(values = custom.colors) +
  custom_theme_linedraw()  +
  geom_line(aes(x = biovol_x, y = exports_y)) + 
   geom_line(aes(x = biovol_x, y = simon_azam_y), linetype = 2, color = "#4DAF4A") +
    geom_line(aes(x = biovol_x, y = gunderson_y), linetype = 3, color = "#FF7F00") +
   geom_line(aes(x = biovol_x, y = malfatti_y), color = "#552583") +
  geom_label(data = filter(ccf_biovol_plot.data, biovol_x == 0.010), aes(x = biovol_x, y = exports_y, label = "EXPORTS")) +
  geom_label(data = filter(ccf_biovol_plot.data, biovol_x == 0.010), aes(x = biovol_x, y = simon_azam_y + 1, label = "Simon & Azam (1989)"), fill = "#4DAF4A") + 
   geom_label(data = filter(ccf_biovol_plot.data, biovol_x == 0.010), aes(x = biovol_x, y = gunderson_y, label = "Gunderson et al (2002)"), fill = "#FF7F00")  +
geom_label(data = filter(ccf_biovol_plot.data, biovol_x == 0.010), aes(x = biovol_x, y = malfatti_y + 2, label = "Malfatti (2009)"), fill = "#552583", color = "white")  
 
```

## Plot Cell Carbon v GF75 Retention

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8, fig.align = "center", warning = FALSE}
ccf_biovol %>% 
  mutate(retention = ifelse(amendment == T & phase == "Initial", NA, retention),
         ccf = ifelse(amendment == T & phase == "Initial", NA, ccf),
         amendment = ifelse(amendment == T, "Addition", "Non-Addition")) %>% 
  ggplot(aes(x =  retention, y = ccf)) +
  geom_point( aes(color = Season, shape = phase), size = 4, alpha = 0.7 ) +
  labs(x = expression(paste("GF75 Filter Cell Retention, %")), y = expression(paste("Cellular C, fg C Cell"^-1))) +
  scale_x_continuous(trans = 'log10', breaks = pretty_breaks(), limits = c(30, 110)) +
  scale_y_continuous(trans = 'log10', breaks = pretty_breaks(), limits = c(1, 90)) +
  scale_color_manual(values = custom.colors) +
  custom_theme_linedraw()  +
  facet_grid(~amendment)
  
```

## Plot Cell Carbon v GF75 Filter Cell Abundance

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 12, fig.align = "center", warning = FALSE}
ccf_biovol %>% 
  mutate(filter_cells = ifelse(amendment == T & phase == "Initial", NA, filter_cells),
         ccf = ifelse(amendment == T & phase == "Initial", NA, ccf),
         amendment = ifelse(amendment == T, "Addition", "Non-Addition")) %>% 
  ggplot(aes(x =  filter_cells/(10^9), y = ccf)) +
  geom_point( aes(color = Season, shape = phase), size = 4, alpha = 0.7 ) +
  labs(x = expression(paste("Bacterial Abundance on GF75 Filter, 10"^9,"Cells L"^-1)), y = expression(paste("Cellular C, fg C Cell"^-1))) +
  scale_x_continuous(trans = 'log10', breaks = pretty_breaks()) +
  scale_y_continuous(trans = 'log10', breaks = pretty_breaks(), limits = c(1, 90)) +
  scale_color_manual(values = custom.colors) +
  custom_theme_linedraw()  +
  facet_grid(~amendment)
  
```

## Plot Cell Carbon v POC 

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 13, fig.align = "center", warning = FALSE}
ccf_biovol %>% 
  mutate(bact_C = ifelse(amendment == T & phase == "Initial", NA, bact_C),
         ccf = ifelse(amendment == T & phase == "Initial", NA, ccf),
         amendment = ifelse(amendment == T, "Addition", "Non-Addition")) %>% 
  ggplot(aes(x =  bact_C, y = ccf)) +
  geom_point( aes(color = Season, shape = phase), size = 4, alpha = 0.7 ) +
  labs(x = expression(paste("Bacterial POC on GF75 Filter, umol C L"^-1)), y = expression(paste("Cellular C, fg C Cell"^-1))) +
  scale_x_continuous(trans = 'log10', breaks = pretty_breaks()) +
  scale_y_continuous(trans = 'log10', breaks = pretty_breaks(), limits = c(1, 90)) +
  scale_color_manual(values = custom.colors) +
  custom_theme_linedraw()  +
  facet_grid(~amendment)
  
```

## Plot Cell Carbon v C:N 

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 13, fig.align = "center", warning = FALSE}
ccf_biovol %>% 
  mutate(bact_C_N = ifelse(amendment == T & phase == "Initial", NA, bact_C_N),
         ccf = ifelse(amendment == T & phase == "Initial", NA, ccf),
         amendment = ifelse(amendment == T, "Addition", "Non-Addition")) %>% 
  ggplot(aes(x =  bact_C_N, y = ccf)) +
  geom_point( aes(color = Season, shape = phase), size = 4, alpha = 0.7 ) +
  labs(x = expression(paste("Bacterial C:N, molar")), y = expression(paste("Cellular C, fg C Cell"^-1))) +
  scale_x_continuous(trans = 'log10', breaks = pretty_breaks()) +
  scale_y_continuous(trans = 'log10', breaks = pretty_breaks(), limits = c(1, 90)) +
  scale_color_manual(values = custom.colors) +
  custom_theme_linedraw()  +
  facet_grid(~amendment)
  
```

# Merge Data

```{r message = F, warning = F}

ba.merge <- gcstat.df %>% 
  mutate(key = paste(Cruise, Station, Depth, Treatment, Bottle, Timepoint, sep = "."),
         Depth = as.numeric(Depth)) %>% 
  filter(!Treatment %in% c("GF75", "Niskin", "TFF-Ret", "Volume", "Parallel"))

oc.merge <- oc_p %>% 
  select(-Days) %>% 
  filter(!Treatment == "Parallel")


merge <- full_join(ba.merge, oc.merge) %>% 
  left_join(., fg_cell.qc) %>% 
  left_join(., biovol_merge) %>% 
  arrange(Cruise, Station, Depth, Treatment, Bottle, Hours) %>%
  group_by(Cruise, Station, Depth, Treatment, Bottle) %>% 
  fill(stationary, .direction = "downup") %>% 
  fill(facet_depth:facet_bottle, .direction = "downup") %>% 
  fill(k:auc_e, .direction = "downup") %>% 
  mutate(Days = round(Hours/24, 1)) %>% 
  ungroup() %>% 
  drop_na(Hours) %>% 
  select(Season:Depth, facet_depth,  Treatment, facet_treatment, Bottle, facet_bottle, Hours, stationary, Days, cells:sd_p_cells, doc, sd_doc, ptoc, sd_ptoc, doc_from_t0, ptoc_from_t0, initial_biovol, stationary_biovol, initial_ccf:stationary_ncf) 
   
```

# Bottle v. Vial Incubation Comparisons

## PTOC v. PDOC

### Absolute

```{r message = F}
ptoc_pdoc.data <- oc_p %>% 
  filter(Cruise == "AT39", !Treatment == "Parallel") 
ptoc_pdoc.reg <- lmodel2(pdoc ~ ptoc, data = ptoc_pdoc.data , nperm = 99)
```

```{r echo = FALSE}
ptoc_pdoc.reg 
```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6, fig.align = "center", warning = FALSE}
ptoc_pdoc.data %>% 
  ggplot(aes(x = ptoc, y = pdoc, group = Bottle)) + 
  geom_abline(aes(intercept = 0, slope = 1)) +
  geom_abline(intercept = ptoc_pdoc.reg$regression.results[3,2],
              slope = ptoc_pdoc.reg$regression.results[3,3],colour = "black", linetype = 2, size = 1) +
  geom_point( fill = "white", shape = 21, size = 4, alpha = 0.7 ) +
  labs(x = expression(paste("TOC, µmol C L"^-1)), y = expression(paste("DOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 4 Parallel Samples") 

```

### Delta


```{r message = F}
delta_ptoc_pdoc.reg <- lmodel2(pdoc_from_t0 ~ ptoc_from_t0, data = ptoc_pdoc.data , nperm = 99)
```

```{r echo = FALSE}
delta_ptoc_pdoc.reg 
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6, fig.align = "center", warning = FALSE}
ptoc_pdoc.data %>% 
  ggplot(aes(x = ptoc_from_t0, y = pdoc_from_t0, group = Bottle)) + 
  geom_abline(aes(intercept = 0, slope = 1)) +
  geom_abline(intercept = delta_ptoc_pdoc.reg$regression.results[3,2],
              slope = delta_ptoc_pdoc.reg$regression.results[3,3],colour = "black", linetype = 2, size = 1) +
  geom_point( fill = "white", shape = 21, size = 4, alpha = 0.7 ) +
  labs(x = expression(paste("∆TOC, µmol C L"^-1)), y = expression(paste("∆DOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 4 Parallel Samples") 

```


## Bottle TOC v. Vial TOC

Because the same samples are measured for TOC and PTOC for T0, these data are omitted from the regression analysis.

### Absolute

```{r message = F}
toc_ptoc.data <- oc_p %>% 
  filter(!Cruise == "AT34", !Timepoint == 0, !Treatment == "Parallel") 
toc_ptoc.reg <- lmodel2(ptoc ~ toc, data = toc_ptoc.data, nperm = 99)
```
```{r echo = FALSE}
toc_ptoc.reg
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6, fig.align = "center", warning = FALSE}
toc_ptoc.data %>% 
  ggplot(aes(x = toc, y = ptoc)) + 
  geom_abline(aes(intercept = 0, slope = 1)) +
  geom_abline(intercept = toc_ptoc.reg$regression.results[3,2],
              slope = toc_ptoc.reg$regression.results[3,3],colour = "black", linetype = 2, size = 1) +
  geom_point( fill = "white", shape = 21, size = 4, alpha = 0.7 ) +
  labs(x = expression(paste("Bottle TOC, µmol C L"^-1)), y = expression(paste("Vial TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 3 & 4 TOC") 

```

### Delta

```{r message = F}
delta_toc_ptoc.reg <- lmodel2(ptoc_from_t0 ~ toc_from_t0, data = toc_ptoc.data, nperm = 99)
```
```{r echo = FALSE}
delta_toc_ptoc.reg
```
```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6, fig.align = "center", warning = FALSE}
toc_ptoc.data %>% 
  ggplot(aes(x = toc_from_t0, y = ptoc_from_t0)) + 
  geom_abline(aes(intercept = 0, slope = 1)) +
  geom_abline(intercept = delta_toc_ptoc.reg$regression.results[3,2],
              slope = delta_toc_ptoc.reg$regression.results[3,3],colour = "black", linetype = 2, size = 1) +
  geom_point( fill = "white", shape = 21, size = 4, alpha = 0.7 ) +
  labs(x = expression(paste("Bottle ∆TOC, µmol C L"^-1)), y = expression(paste("Vial ∆TOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 3 & 4 TOC") 

```



## Bottle v. Vial Cell Abundance


```{r message = F}
btl_vial_cell.data <- merge %>% 
 drop_na(p_cells)
btl_vial_cell.reg <- lmodel2(p_cells ~ cells, data = btl_vial_cell.data, nperm = 99)
```

```{r echo = FALSE}
btl_vial_cell.reg
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6, fig.align = "center", warning = FALSE}
btl_vial_cell.data %>% 
  ggplot(aes(x = cells, y = p_cells)) + 
  geom_abline(aes(intercept = 0, slope = 1)) +
  geom_abline(intercept = btl_vial_cell.reg$regression.results[3,2],
              slope = btl_vial_cell.reg$regression.results[3,3],colour = "black", linetype = 2, size = 1) +
  geom_point( fill = "white", shape = 21, size = 4, alpha = 0.7 ) +
  labs(x = expression(paste("Bottle Cells L"^-1)), y = expression(paste("Vial Cells L"^-1))) +
  scale_y_continuous(breaks = pretty_breaks()) +
  scale_x_continuous(breaks = pretty_breaks()) +
  custom_theme() 

```

# Tidy and Wrangle Merged Data

## Condense DOC Data

Because DOC and TOC samples are essentially the same in this dataset, we will treat them as such. We'll use the DOC samples from AT34 and the parallel TOC samples from AT38 and AT39.

```{r}
tidy_merge <- merge %>% 
  mutate(ptoc = ifelse(Cruise == "AT34", doc, ptoc),
         sd_ptoc = ifelse(Cruise == "AT34", sd_doc, sd_ptoc),
         ptoc_from_t0 = ifelse(Cruise == "AT34", doc_from_t0, ptoc_from_t0)) %>% 
  select(-c(p_cells, sd_p_cells, doc, sd_doc, doc_from_t0)) %>% 
  rename(doc = ptoc,
         sd_doc = sd_ptoc,
         doc_from_t0 = ptoc_from_t0) %>% 
  # merge duplicate stationary timepoints
  group_by(Cruise, Station, Depth, Treatment, Bottle, Hours) %>%
  fill(cells:stationary_ncf, .direction = "downup") %>% 
  distinct() %>% 
  ungroup() %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle) 

tidy_merge_keys <- tidy_merge %>% 
  group_keys() %>%
  mutate(key = paste(Cruise, ", S", Station, ", Z =", Depth, ",", Treatment, ",", Bottle))
tidy_merge_header <- tidy_merge_keys$key

tidy_merge_list <- tidy_merge %>%
  group_split()
names(tidy_merge_list) <- tidy_merge_header

```

## Interpolate Stationary Timepoint

```{r warning = FALSE}
interp.func <- function(x) {
  y <- zoo(x, order.by = x$Hours)
  interp_cells <- round(as.numeric(na.approx(y$cells, na.rm = F)))
  interp_doc <- round(as.numeric(na.approx(y$doc, na.rm = F)), 1)
  z <- cbind(y, interp_cells,  interp_doc)
  as_tibble(z)
}

interp_st <- lapply(tidy_merge_list, interp.func) %>% 
  plyr::ldply(., as.data.frame) %>% 
  select(-.id) %>% 
  mutate_at(vars(Depth, Hours:interp_doc), as.numeric)
```

# Calculate Derived Variables

We'll calculate and define:

- Division rates (**r**) between each timepoint (Monod 1949). We assume all cells are viable. 
- Duration of lag, log, stationary phases based on calculated division rates and timing of stationary determined via GrowthCurver
  + lag phase ends when r > 0.01
  + we've already filtered out the death phases so stationary runs from GrowthCurver determined timepoint until cell counts cease
  + we do not determine growth phases where there is no observable growth
- Carrying Capacity (**k**), mean of cell abundance during stationary
- Exponential growth rate day^-1^
- Dynamic CCFs: we use a weighted function to determine the CCF from the initial condition to the beginning of stationary, end members which we have measured:
  + CCF~t~ = CCF~initial~ + w(CCF~stationary~ - CCF~initial~), where w = cells~t~ / cells~st~
  + for this to work, we normalize the cell counts to those at stationary
- Cell carbon in µmol C L^-1^, using the dynamic CCFS
- Biovolume-based cell carbon will be calculated using dynamic biovolumes, in the same way as above.
- Bacterial growth efficiencies (BGE) using multiple approaches, only where ∆DOC is resolvable:
  + point-to-point (**BGE_p**), ∆BC and ∆DOC from T0 to stationary
  + phase-to-phase (**BGE_ph**), ∆BC and ∆DOC using means of lag phase and stationary phase values
  + area under the curve (**BGE_ac**)

```{r message = F}
calcs <- interp_st %>%
  group_by(Cruise, Station, Depth, Treatment, Bottle) %>% 
  #division rates 
  mutate(r = round((log(interp_cells) - lag(log(interp_cells)))/(Hours - lag(Hours)), 2),
         r = ifelse(Hours == 0, 0, r)) %>% 
  #cell growth phase
  mutate(cell_div = ifelse(Hours >= stationary & !is.na(interp_cells), "stationary", NA),
         cell_div = ifelse(Hours > stationary & is.na(cell_div), "out of bounds", cell_div),
         cell_div = ifelse(Hours < stationary & r > 0.01, "exponential", cell_div)) %>% 
  fill(cell_div, .direction = "down") %>% 
  mutate(cell_div = ifelse(Hours < stationary & r == 0 & is.na(cell_div), "lag", cell_div)) %>% 
  fill(cell_div, .direction = "down") %>% 
  mutate(full_curve = ifelse(cell_div == "stationary", cell_div, NA)) %>% 
  fill(full_curve, .direction = "downup") %>% 
  mutate(full_curve = ifelse(full_curve == "stationary", T, F),
         full_curve = ifelse(is.na(full_curve), F, full_curve),
         cell_div = ifelse(full_curve == F, "no growth", cell_div),
         full_curve = ifelse(cell_div == "exponential", T, NA)) %>% 
  fill(full_curve, .direction = "downup") %>% 
  mutate(full_curve = ifelse(is.na(full_curve), F, full_curve),
         cell_div = ifelse(full_curve == F, "no growth", cell_div)) %>% 
  # carrying capacity
  mutate(k = ifelse(cell_div == "stationary", interp_cells, NA),
         k = ifelse(!is.na(k), mean(k, na.rm = T), NA)) %>% 
  #exponential growth rate
  mutate(end_lag_t = ifelse(cell_div == "lag", Hours, NA),
         end_lag_t = ifelse(!is.na(end_lag_t), max(end_lag_t, na.rm = T), NA),
         end_lag_cells = ifelse(Hours == end_lag_t, interp_cells, NA),
         beg_stationary_cells = ifelse(Hours == stationary, interp_cells, NA)) %>% 
  fill(k:beg_stationary_cells, .direction = "downup") %>% 
  mutate(mew = ifelse(!is.na(end_lag_cells), ((log(beg_stationary_cells) - log(end_lag_cells))/(stationary - end_lag_t)) * 24, NA )) %>% 
  #weighted CCF and cell carbon
  mutate(initial_cells = ifelse(Hours == 0, interp_cells, NA)) %>% 
  fill(initial_cells, .direction = "updown") %>% 
  mutate(delta_cells = interp_cells - initial_cells,
         stationary_delta_cells = ifelse(Hours == stationary & stationary != 0 & full_curve == T, delta_cells, NA)) %>% 
  fill(stationary_delta_cells, .direction = "updown") %>% 
  mutate(norm_cells = ifelse(!is.na(stationary_delta_cells), round(delta_cells/stationary_delta_cells,2), NA)) %>% 
  rename(weight = norm_cells) %>% 
  mutate(ccf = round(initial_ccf + (weight * (stationary_ccf - initial_ccf)),1),
         ccf_biovol = round(initial_biovol + (weight * (stationary_biovol - initial_biovol)),3),
         cell_carbon =  round((interp_cells * ccf) / (12*10^9), 1),
         cell_carbon_biovol = round((interp_cells * ccf_biovol * 148)/(12*10^9), 1)) %>% 
  #BGE_p
  mutate(cell_carbon_from_t0 = cell_carbon - first(cell_carbon),
         cell_carbon_from_t0_biovol = cell_carbon_biovol - first(cell_carbon_biovol),
         interp_doc_from_t0 = first(interp_doc) - interp_doc,
         ddoc_resolve_p = ifelse(Hours == stationary & interp_doc_from_t0 >= 1.5, T, NA)) %>% 
  fill(ddoc_resolve_p, .direction = "downup") %>% 
  mutate(ddoc_resolve_p = ifelse(is.na(ddoc_resolve_p), F, ddoc_resolve_p),
         bge_p = ifelse(Hours == stationary & ddoc_resolve_p == T, round(((first(cell_carbon) - cell_carbon))/(interp_doc - first(interp_doc)),2), NA),
          bge_p_biovol = ifelse(Hours == stationary & ddoc_resolve_p == T, round(((first(cell_carbon_biovol) - cell_carbon_biovol))/(interp_doc - first(interp_doc)),2), NA)) %>%
  fill(bge_p:bge_p_biovol, .direction = "downup") %>% 
  #BGE_ph 
  ungroup() %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle, cell_div) %>% 
  mutate(cell_carbon_cell_div = round(mean(cell_carbon, na.rm = T), 1),
         cell_carbon_cell_div_biovol = round(mean(cell_carbon_biovol, na.rm = T), 1),
         doc_cell_div = round(mean(interp_doc, na.rm = T), 1),
         cell_carbon_lag = ifelse(cell_div == "lag", cell_carbon_cell_div, NA),
         cell_carbon_st = ifelse(cell_div == "stationary", cell_carbon_cell_div, NA),
           cell_carbon_lag_biovol = ifelse(cell_div == "lag", cell_carbon_cell_div_biovol, NA),
         cell_carbon_st_biovol = ifelse(cell_div == "stationary", cell_carbon_cell_div_biovol, NA),
         doc_lag = ifelse(cell_div == "lag", doc_cell_div, NA),
         doc_st = ifelse(cell_div == "stationary", doc_cell_div, NA) ) %>%
  ungroup() %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle) %>%
  fill(cell_carbon_lag:doc_st, .direction = "downup") %>% 
  mutate(ddoc_ph = doc_lag - doc_st,
         ddoc_resolve_ph = ifelse(ddoc_ph >= 1.5, T, F),
         bge_ph = ifelse(ddoc_resolve_ph == T, round((cell_carbon_st - cell_carbon_lag)/(doc_lag - doc_st), 2), NA),
         bge_ph_biovol = ifelse(ddoc_resolve_ph == T, round((cell_carbon_st_biovol - cell_carbon_lag_biovol)/(doc_lag - doc_st), 2), NA)) %>% 
  ungroup()
  
bge <- calcs %>%
  group_by(Cruise, Station, Depth, Treatment, Bottle) %>%
  filter(full_curve == T) %>% 
  drop_na(interp_doc_from_t0, cell_carbon_from_t0) %>% 
  mutate(auc_cell_carbon = round(integrateTrapezoid(Hours, cell_carbon_from_t0, type = "A"), 1),
         auc_cell_carbon_biovol = round(integrateTrapezoid(Hours, cell_carbon_from_t0_biovol, type = "A"), 1),
         auc_doc = round(integrateTrapezoid(Hours, interp_doc_from_t0, type = "A"), 1),
         bge_ac = round(auc_cell_carbon/auc_doc, 2),
         bge_ac = ifelse(ddoc_resolve_p == F, NA, bge_ac),
         bge_ac_biovol = round(auc_cell_carbon_biovol/auc_doc, 2),
         bge_ac_biovol = ifelse(ddoc_resolve_p == F, NA, bge_ac)) %>% 
  select(Cruise, Station, Depth, Treatment, Bottle, auc_cell_carbon:bge_ac_biovol) %>%  
  distinct() %>% 
  drop_na() %>% 
  left_join(calcs, .) %>% 
  ungroup() 

bge$Season <- factor(bge$Season, levels = levels)

test <- bge %>% 
  select(Cruise, Station, Depth, Treatment, bge_p, bge_p_biovol, bge_ph, bge_ph_biovol, bge_ac, bge_ac_biovol) %>% 
  distinct()

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 12, fig.align = "center", warning = FALSE}
bge %>%
  filter(Depth == 10, Treatment == "Control") %>% 
  select(Season, bge_p, bge_ph, bge_ac) %>% 
  distinct() %>% 
  gather(key, value, bge_p, bge_ph, bge_ac) %>% 
  drop_na(value) %>% 
  mutate(key = gsub("bge_ph", "Phase to Phase", key),
         key = gsub("bge_p", "Point to Point", key),
         key = gsub("bge_ac", "Area Under the Curve", key)) %>% 
  ggplot(aes(x = Season, y = value)) +
  geom_boxplot(width = 0.3) +
  geom_jitter(aes(fill = key), width = 0.1, shape = 21, size = 6, alpha = 0.7) + 
  labs(x = "", y = expression(italic("BGE")), colour = expression(italic(""))) + 
  scale_fill_brewer(palette = "Set1") +
  custom_theme() +
  facet_grid(~key) +
  ggtitle("Bacterial Growth Efficiences - GF75 POC") +
  guides(fill = F)
  
  
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 12, fig.align = "center", warning = FALSE}
bge %>%
  filter(Depth == 10, Treatment == "Control") %>% 
  select(Season, bge_p_biovol, bge_ph_biovol, bge_ac_biovol) %>% 
  distinct() %>% 
  gather(key, value, bge_p_biovol, bge_ph_biovol, bge_ac_biovol) %>% 
  drop_na(value) %>% 
  mutate(key = gsub("bge_ph_biovol", "Phase to Phase", key),
         key = gsub("bge_p_biovol", "Point to Point", key),
         key = gsub("bge_ac_biovol", "Area Under the Curve", key)) %>% 
  #filter(!key == "Area Under the Curve") %>% 
  #filter(!key == "Point to Point") %>% 
  ggplot(aes(x = Season, y = value)) +
  geom_boxplot(width = 0.3) +
  geom_jitter(aes(fill = key), width = 0.1, shape = 21, size = 6, alpha = 0.7) + 
  labs(x = "", y = expression(italic("BGE")), colour = expression(italic(""))) + 
  scale_fill_brewer(palette = "Set1") +
  custom_theme() +
  facet_grid(~key) +
  ggtitle("Bacterial Growth Efficiences - Biovolume") +
  guides(fill = F)
  
  
```

```{r}
bge_table <- bge %>% 
  filter(Depth == 10, Treatment == "Control") %>% 
  select(Season, bge_p_biovol, bge_ph_biovol, bge_ac_biovol) %>% 
  distinct() %>% 
  gather(key, value, bge_p_biovol, bge_ph_biovol, bge_ac_biovol) %>% 
  drop_na(value) %>% 
  mutate(key = gsub("bge_ph_biovol", "Phase to Phase", key),
         key = gsub("bge_p_biovol", "Point to Point", key),
         key = gsub("bge_ac_biovol", "Area Under the Curve", key)) %>%
  rename(approach = key, 
         bge = value) %>% 
  group_by(Season, approach) %>% 
  mutate(mean_bge = round(mean(bge), 2),
         sd_bge = round(sd(bge), 2),
         min_bge = round(min(bge), 2),
         max_bge = round(max(bge), 2)) %>%
  add_tally() %>% 
  ungroup() %>% 
  select(-bge) %>% 
  distinct() %>% 
  arrange(Season)
```

```{r echo = FALSE, results = 'asis'}
kable(bge_table, caption = "Biovolume-based BGE")
```

Despite all this... BGEs based on POC are trash. BUT it would seem that it doesn't really matter how one calculates BGE as the different approaches are fairly consistent. 

Major factors are likely problems with: 

- CCFs
  + especially the AT38 values, which seem really high for open ocean during a stratified period
- Short-term DOC dynamics
  + small flucuations could be making a big difference, especially for area under the curve/phase mean calculations. 
- Bacterial abundance
  + counts overstimated? a spot check of initial condition counts with Niskin counts suggests that counts are fine (initial experimentalcondition is 30% of whole water counts) ... unless all counts are off, but this is unlikely. 
  
Biovolume-based BGEs seem to be much more reasonable, particulary those calculated via the phase-to-phase approach. 

# Recalculations Using Mean CCFs

Because the surface and deepwater CCFs calculated for AT38 are high relative to the surface values of the other cruises, they are suspicious. 

To workaround using them, we'll:

- calculate mean conversion factors for the initial and stationary condition for addition (A) and non-addition (NA) experiments at 10 and 200 m
- as above, use a weighted function to determine the conversion factors between the initial and stationary conditions
- recalculate cell carbon using those conversion factors 

This is still a slightly better approach than applying a single conversion factor (from the literature) across all data. It does make some sense to do in comparing experiments across the different seasons.

```{r}
rm_n3_ccf <- fg_cell.rm %>% 
  filter(Cruise == "AT38") %>% 
  select(Season:Bottle)


mean_ccf <- fg_cell.rm %>% 
  filter(!Cruise == "AT38") %>% 
  bind_rows(., rm_n3_ccf) %>% 
  mutate(Depth = as.numeric(Depth),
         Depth = ifelse(Treatment == "MixDS", 200, Depth),
         Depth = ifelse(Treatment == "MixSD", 10, Depth),
         Addition = ifelse(Treatment %in% c("Control", "MixSD", "MixDS"), F, T)) %>% 
  group_by(Depth) %>% 
  mutate(ave_initial_ccf = round(mean(initial_ccf, na.rm = T)),
         sd_initial_ccf = round(sd(initial_ccf, na.rm = T)),
         ave_initial_bactC_N = round(mean(initial_bactC_N, na.rm = T)),
         sd_initial_bactC_N = round(sd(initial_bactC_N, na.rm = T))) %>% 
  ungroup() %>% 
  group_by(Depth, Addition) %>% 
  mutate(ave_NA_stationary_ccf = ifelse(Addition == F, round(mean(stationary_ccf, na.rm = T)), NA),
         sd_NA_stationary_ccf = ifelse(Addition == F, round(sd(stationary_ccf, na.rm = T)), NA),
         ave_NA_stationary_bactC_N = ifelse(Addition == F, round(mean(stationary_bactC_N, na.rm = T)), NA),
         sd_NA_stationary_bactC_N = ifelse(Addition == F, round(sd(stationary_bactC_N, na.rm = T)), NA),
         ave_A_stationary_ccf = ifelse(Addition == T, round(mean(stationary_ccf, na.rm = T)), NA),
         sd_A_stationary_ccf = ifelse(Addition == T, round(sd(stationary_ccf, na.rm = T)), NA),
          ave_A_stationary_bactC_N = ifelse(Addition == T, round(mean(stationary_bactC_N, na.rm = T)), NA),
         sd_A_stationary_bactC_N = ifelse(Addition == T, round(sd(stationary_bactC_N, na.rm = T)), NA)) %>%
  ungroup() %>% 
  mutate(ave_stationary_ccf = ave_NA_stationary_ccf,
         ave_stationary_ccf = ifelse(is.na(ave_stationary_ccf), ave_A_stationary_ccf, ave_stationary_ccf),
         sd_stationary_ccf = sd_NA_stationary_ccf,
         sd_stationary_ccf = ifelse(is.na(sd_stationary_ccf), sd_A_stationary_ccf, sd_stationary_ccf),
         ave_stationary_bactC_N = ave_NA_stationary_bactC_N,
         ave_stationary_bactC_N = ifelse(is.na(ave_stationary_bactC_N), ave_A_stationary_bactC_N, ave_stationary_bactC_N),
         sd_stationary_bactC_N = sd_NA_stationary_bactC_N,
         sd_stationary_bactC_N = ifelse(is.na(sd_stationary_bactC_N), sd_A_stationary_bactC_N, sd_stationary_bactC_N)) %>% 
  select(Season:Bottle, Addition, ave_initial_bactC_N, sd_initial_bactC_N, ave_stationary_bactC_N, sd_stationary_bactC_N, ave_initial_ccf, sd_initial_ccf, ave_stationary_ccf, sd_stationary_ccf )
  
```

```{r echo = FALSE, results = 'asis'}
mean_ccf.table <- mean_ccf %>% 
  select(Depth, Addition:sd_stationary_ccf) %>%
  distinct() %>% 
  arrange(Depth)
```

```{r echo = FALSE, results = 'asis'}
kable(mean_ccf.table, caption = "Mean Bacterioplankton C:N and Converstion Factors")
```

```{r message = F, warning = F}
calcs_ave_ccf <- interp_st %>%
  left_join(., mean_ccf) %>% 
  select(Season, Cruise:facet_treatment, Addition, Bottle:doc_from_t0, ave_initial_ccf, ave_stationary_ccf, initial_biovol, stationary_biovol, interp_cells, interp_doc) %>% 
  rename(initial_ccf = ave_initial_ccf,
         stationary_ccf = ave_stationary_ccf) %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle) %>% 
  #division rates 
  mutate(r = round((log(interp_cells) - lag(log(interp_cells)))/(Hours - lag(Hours)), 2),
         r = ifelse(Hours == 0, 0, r)) %>% 
  #cell growth phase
  mutate(cell_div = ifelse(Hours >= stationary & !is.na(interp_cells), "stationary", NA),
         cell_div = ifelse(Hours > stationary & is.na(cell_div), "out of bounds", cell_div),
         cell_div = ifelse(Hours < stationary & r > 0.01, "exponential", cell_div)) %>% 
  fill(cell_div, .direction = "down") %>% 
  mutate(cell_div = ifelse(Hours < stationary & r == 0 & is.na(cell_div), "lag", cell_div)) %>% 
  fill(cell_div, .direction = "down") %>% 
  mutate(full_curve = ifelse(cell_div == "stationary", cell_div, NA)) %>% 
  fill(full_curve, .direction = "downup") %>% 
  mutate(full_curve = ifelse(full_curve == "stationary", T, F),
         full_curve = ifelse(is.na(full_curve), F, full_curve),
         cell_div = ifelse(full_curve == F, "no growth", cell_div),
         full_curve = ifelse(cell_div == "exponential", T, NA)) %>% 
  fill(full_curve, .direction = "downup") %>% 
  mutate(full_curve = ifelse(is.na(full_curve), F, full_curve),
         cell_div = ifelse(full_curve == F, "no growth", cell_div)) %>% 
  #carrying capacity
  mutate(k = ifelse(cell_div == "stationary", interp_cells, NA),
         k = ifelse(!is.na(k), mean(k, na.rm = T), NA)) %>% 
  #exponential growth rate
  mutate(end_lag_t = ifelse(cell_div == "lag", Hours, NA),
         end_lag_t = ifelse(!is.na(end_lag_t), max(end_lag_t, na.rm = T), NA),
         end_lag_cells = ifelse(Hours == end_lag_t, interp_cells, NA),
         beg_stationary_cells = ifelse(Hours == stationary, interp_cells, NA)) %>%
  fill(k:beg_stationary_cells, .direction = "downup") %>% 
  mutate(mew = ifelse(!is.na(end_lag_cells), ((log(beg_stationary_cells) - log(end_lag_cells))/(stationary - end_lag_t)) * 24, NA )) %>% 
  #weighted CCF and cell carbon
  mutate(initial_cells = ifelse(Hours == 0, interp_cells, NA)) %>% 
  fill(initial_cells, .direction = "updown") %>% 
  mutate(delta_cells = interp_cells - initial_cells,
         stationary_delta_cells = ifelse(Hours == stationary & stationary != 0 & full_curve == T, delta_cells, NA)) %>% 
  fill(stationary_delta_cells, .direction = "updown") %>% 
  mutate(norm_cells = ifelse(!is.na(stationary_delta_cells), round(delta_cells/stationary_delta_cells,2), NA)) %>% 
  rename(weight = norm_cells) %>% 
  mutate(ccf = round(initial_ccf + (weight * (stationary_ccf - initial_ccf)),1),
         ccf_biovol = round(initial_biovol + (weight * (stationary_biovol - initial_biovol)),3),
         cell_carbon =  round((interp_cells * ccf) / (12*10^9), 1),
         cell_carbon_biovol = round((interp_cells * ccf_biovol * 148)/(12*10^9), 1)) %>% 
 #BGE_p
  mutate(cell_carbon_from_t0 = cell_carbon - first(cell_carbon),
         cell_carbon_from_t0_biovol = cell_carbon_biovol - first(cell_carbon_biovol),
         interp_doc_from_t0 = first(interp_doc) - interp_doc,
         ddoc_resolve_p = ifelse(Hours == stationary & interp_doc_from_t0 >= 1.5, T, NA)) %>% 
  fill(ddoc_resolve_p, .direction = "downup") %>% 
  mutate(ddoc_resolve_p = ifelse(is.na(ddoc_resolve_p), F, ddoc_resolve_p),
         bge_p = ifelse(Hours == stationary & ddoc_resolve_p == T, round(((first(cell_carbon) - cell_carbon))/(interp_doc - first(interp_doc)),2), NA),
          bge_p_biovol = ifelse(Hours == stationary & ddoc_resolve_p == T, round(((first(cell_carbon_biovol) - cell_carbon_biovol))/(interp_doc - first(interp_doc)),2), NA)) %>%
  fill(bge_p:bge_p_biovol, .direction = "downup") %>% 
  #BGE_ph 
  ungroup() %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle, cell_div) %>% 
  mutate(cell_carbon_cell_div = round(mean(cell_carbon, na.rm = T), 1),
         cell_carbon_cell_div_biovol = round(mean(cell_carbon_biovol, na.rm = T), 1),
         doc_cell_div = round(mean(interp_doc, na.rm = T), 1),
         cell_carbon_lag = ifelse(cell_div == "lag", cell_carbon_cell_div, NA),
         cell_carbon_st = ifelse(cell_div == "stationary", cell_carbon_cell_div, NA),
           cell_carbon_lag_biovol = ifelse(cell_div == "lag", cell_carbon_cell_div_biovol, NA),
         cell_carbon_st_biovol = ifelse(cell_div == "stationary", cell_carbon_cell_div_biovol, NA),
         doc_lag = ifelse(cell_div == "lag", doc_cell_div, NA),
         doc_st = ifelse(cell_div == "stationary", doc_cell_div, NA) ) %>%
  ungroup() %>% 
  group_by(Cruise, Station, Depth, Treatment, Bottle) %>%
  fill(cell_carbon_lag:doc_st, .direction = "downup") %>% 
  mutate(ddoc_ph = doc_lag - doc_st,
         ddoc_resolve_ph = ifelse(ddoc_ph >= 1.5, T, F),
         bge_ph = ifelse(ddoc_resolve_ph == T, round((cell_carbon_st - cell_carbon_lag)/(doc_lag - doc_st), 2), NA),
         bge_ph_biovol = ifelse(ddoc_resolve_ph == T, round((cell_carbon_st_biovol - cell_carbon_lag_biovol)/(doc_lag - doc_st), 2), NA)) %>% 
  ungroup()
  
bge_ave_ccf <- calcs_ave_ccf %>%
  group_by(Cruise, Station, Depth, Treatment, Bottle) %>%
 filter(full_curve == T) %>% 
  drop_na(interp_doc_from_t0, cell_carbon_from_t0) %>% 
  mutate(auc_cell_carbon = round(integrateTrapezoid(Hours, cell_carbon_from_t0, type = "A"), 1),
         auc_cell_carbon_biovol = round(integrateTrapezoid(Hours, cell_carbon_from_t0_biovol, type = "A"), 1),
         auc_doc = round(integrateTrapezoid(Hours, interp_doc_from_t0, type = "A"), 1),
         bge_ac = round(auc_cell_carbon/auc_doc, 2),
         bge_ac = ifelse(ddoc_resolve_p == F, NA, bge_ac),
         bge_ac_biovol = round(auc_cell_carbon_biovol/auc_doc, 2),
         bge_ac_biovol = ifelse(ddoc_resolve_p == F, NA, bge_ac)) %>% 
  select(Cruise, Station, Depth, Treatment, Bottle, auc_cell_carbon:bge_ac_biovol) %>%  
  distinct() %>% 
  drop_na() %>% 
  left_join(calcs_ave_ccf, .) %>% 
  ungroup()

bge_ave_ccf$Season <- factor(bge_ave_ccf$Season, levels = levels)

```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8, fig.align = "center", warning = FALSE}
bge_ave_ccf %>%
  filter(Depth == 10, Treatment == "Control") %>% 
  select(Season, bge_p, bge_ph, bge_ac) %>% 
  distinct() %>% 
  gather(key, value, bge_p, bge_ph, bge_ac) %>% 
  drop_na(value) %>% 
  mutate(key = gsub("bge_ph", "Phase to Phase", key),
         key = gsub("bge_p", "Point to Point", key),
         key = gsub("bge_ac", "Area Under the Curve", key)) %>% 
  ggplot(aes(x = Season, y = value)) +
  geom_boxplot(width = 0.3) +
  geom_jitter(aes(fill = key), width = 0.1, shape = 21, size = 6, alpha = 0.7) + 
  labs(x = "", y = expression(italic("BGE")), colour = expression(italic(""))) + 
  scale_fill_brewer(palette = "Set1") +
  custom_theme() +
  facet_grid(~key) +
  ggtitle("Bacterial Growth Efficiences - Mean GF75 POC") +
  guides(fill = F)
  
  
```

Using mean CCF helps, but still provides unreasonable BGEs for surface non-addition experiments.


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8, fig.align = "center", warning = FALSE}
bge_ave_ccf %>%
  filter(Depth == 10, Treatment == "Control") %>% 
  select(Season, mew) %>% 
  distinct() %>% 
  gather(key, value, mew) %>% 
  drop_na(value) %>% 
  ggplot(aes(x = Season, y = value)) +
  geom_boxplot(width = 0.3) +
  geom_jitter(fill = "white", width = 0.1, shape = 21, size = 6, alpha = 0.7) + 
  labs(x = "", y = expression(italic("µ d"^-1)), colour = expression(italic(""))) + 
  scale_fill_brewer(palette = "Set1") +
  custom_theme() +
  ggtitle("Bacterioplankton Growth Rates")
  
  
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8, fig.align = "center", warning = FALSE}
bge_ave_ccf %>%
  filter(Depth == 10, Treatment == "Control") %>% 
  select(Season, k) %>% 
  distinct() %>% 
  gather(key, value, k) %>% 
  drop_na(value) %>% 
  ggplot(aes(x = Season, y = value)) +
  geom_boxplot(width = 0.3) +
  geom_jitter(fill = "white", width = 0.1, shape = 21, size = 6, alpha = 0.7) + 
  labs(x = "", y = expression(italic("Cells L"^-1)), colour = expression(italic(""))) + 
  scale_fill_brewer(palette = "Set1") +
  custom_theme() +
  ggtitle("Bacterioplankton Carrying Capacity")
  
  
```

# Hypotheses on High BGEs in Non-addition Experiments

How can the calculated BGEs be so high in our experiments, even above the theoretical maximum of 0.7-0.8 constrained by del Giorgio and Cole (1998) ? The BGEs would imply that in many cases, the incubating bacterioplankton grew more the remineralization of DOC would allow. 

- Was labile DOC being produced as fast as it is being consumed?
  + since these experiments were dark incubations, photoautotrophy is unlikely, but chemoautotrophy can be a source of labile DOC
- Was the microbial pump at play?
  + the heterotrophic microbes may have been processing the bulk DOM successively and repetitively, transforming reactive DOM pools to a recalcitrant carbon resevoir of a different chemical composition. 
  + the bulk concentration may therefore not change as dramatically as cell abundance
  
Though the absolute values of the BGEs calculated using mean CCFs are nonsensical in relation to the literature, there is some sense to the seasonal pattern if we assume that one or both of the processes described above were at play:

- In the early spring just after/during deep convection and before the phytoplankton bloom is in full swing, DOC concentrations and accumulation are low. There's not a ton of material for microbes to build into biomass, as indicated by the dampened carrying capacities relative to other sesasons. 

- In the late spring, as phytoplankton are blooming, albeit at different stages throughout the NAAMES region, there's a wide spread of BGEs wuth many over 1. We would presume that phytoplankton blooms lead to the increased production of labile DOC. Capturing different stages of that production may explain the spread in BGEs. The microbial pump may be enhanced in some of these incubations that may have started with more reactive DOM.

- In the early autumn during the stratified condition, the range of BGEs narrows but some are still elevated above 1. The range likely decreases as the variability in ecosystem states is dampened relative to the late spring. As above, elevated BGEs could reflect the strength of the microbial pump. 

# Merge Data with Export MS Data

Here, we put our experimental data in the context of the results from the export MS to explore remineralization of the seasonally accumulated DOC pool:

- We first calculate treatment averages for each experiment
- For the surface values at each station, we then subtract the DOC concentration of the winter/early springtime deeply mixed condition (from the export MS) from the DOC concentrations in the experiments conducted at the respective station (**norm_doc**).
- We estimate the concentration of the seasonally accumulated DOC pool as the difference between the initial DOC concentration in each experiment and the DOC concentration of the mixed condition (**accm_doc**)
- We then estimate the total DOC drawdown for the experiments (**bioav_doc**), the total remaining DOC after drawdown(**persis_doc**), the percent DOC bioavalability and persistence (**per_bioav** and **per_persis**, respectively)
- Lastly we calculate the rate of DOC drawdown (nmol C d^-1^, **ddoc**)


```{r message = F, warning = F}

export <- readRDS("~/naames_export_ms/Output/processed_export.rds") %>% 
  mutate(Cruise = gsub("AT39-6", "AT39", Cruise)) %>% 
  select(Cruise, Season, degree_bin, Station, redis_DOC_vol, NCP_mol_100, doc_ncp_100) %>% 
  distinct() %>% 
  mutate_at(vars(redis_DOC_vol), round, 1) %>% 
  mutate_at(vars(NCP_mol_100:doc_ncp_100), round, 2) %>%
  mutate_at(vars(Station), as.character) 

export_bioav <- left_join(bge_ave_ccf, export) %>% 
  mutate(redis_DOC_vol = ifelse(Station %in% c("S2RD", "S2RF"), 55.0, redis_DOC_vol),
         degree_bin = ifelse(is.na(degree_bin), 39, degree_bin)) %>%  
  group_by(Cruise, Station, Depth, Treatment, Hours) %>% 
  mutate(trt_ave_doc = ifelse(!is.na(doc), round(mean(doc, na.rm = T),1), NA),
         trt_sd_doc = ifelse(!is.na(doc), round(sd(doc, na.rm = T),1), NA)) %>% 
  ungroup() %>% 
  group_by(Cruise, Station, Depth, Treatment) %>% 
  mutate(norm_doc = ifelse(Depth != 200 | Treatment == "MixDS", trt_ave_doc - redis_DOC_vol, NA),
         accm_doc = ifelse(Depth == 10 & Treatment == "Control", first(trt_ave_doc) - redis_DOC_vol, NA),
         bioav_accm_doc = ifelse(Depth == 10 & Treatment == "Control", last(trt_ave_doc) - redis_DOC_vol, NA),
         norm_doc_from_t0 = ifelse(!is.na(norm_doc), first(norm_doc) - norm_doc, NA),
         bioav_doc = first(norm_doc) - last(norm_doc),
         persis_doc = accm_doc - bioav_doc,
         per_bioav = round((bioav_doc/accm_doc * 100)),
         per_persis = round((persis_doc/accm_doc * 100)),
         time = last(Days),
         ddoc = round((bioav_doc/time) * 1000)) %>%   
  ungroup() %>% 
  group_by(Cruise, Station, Depth) %>% 
  fill(accm_doc: bioav_accm_doc, .direction = "downup") %>% 
  select(Season, Cruise, degree_bin, Station, redis_DOC_vol:doc_ncp_100, Depth:sd_doc, interp_doc, trt_ave_doc:norm_doc_from_t0, bioav_doc, persis_doc, per_bioav, per_persis, ddoc, interp_cells, initial_ccf, stationary_ccf, ccf, cell_carbon, full_curve, cell_div, r, mew, k, bge_p, bge_ph, bge_ac) %>% 
  ungroup()

export_bioav$Season <- factor(export_bioav$Season, levels = levels)
#export_bioav$Treatment <- factor(export_bioav$Treatment, levels = levels)
#export_bioav$facet_treatment <- factor(export_bioav$facet_treatment, levels = levels)
#export_bioav$facet_bottle <- factor(export_bioav$facet_bottle, levels = levels)
    
```

# Remineralization of Seasonally Accumulated DOC

### NAAMES 2

#### No Addition

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
export_bioav %>% 
  drop_na(norm_doc) %>% 
  select(Cruise, Station, degree_bin, Depth, Treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  filter(Cruise == "AT34", Treatment == "Control", Depth == 10) %>% 
  mutate(degree_bin = paste(degree_bin, "˚N")) %>% 
  group_by(Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = norm_doc, group = Treatment)) + 
  geom_errorbar(aes(ymin = norm_doc - trt_sd_doc, ymax = norm_doc + trt_sd_doc), width = 0.5) +
  geom_point(aes(fill = Treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~degree_bin, scales = "free") +
  labs(y = expression(paste("Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 2 DOC") + 
  guides(color = F, fill = F)

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
export_bioav %>% 
  drop_na(norm_doc) %>% 
  select(Cruise, Station, Depth, Treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  filter(Cruise == "AT34", Treatment == "Control", Depth == 10) %>% 
  group_by(Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = -norm_doc_from_t0, group = Treatment)) + 
  geom_point(aes(fill = Treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~Station, scales = "free") +
  labs(y = expression(paste("Delta Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 2 DOC") + 
  guides(color = F, fill = F)

```


#### Additions

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8, fig.align = "center", warning = FALSE}
export_bioav %>% 
  filter(Cruise == "AT34", Station == 2) %>% 
  drop_na(norm_doc) %>% 
  select(Cruise, Station, degree_bin, Depth, Treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  mutate(degree_bin = paste(degree_bin, "˚N")) %>% 
  group_by(Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = norm_doc, group = Treatment)) + 
  geom_errorbar(aes(ymin = norm_doc - trt_sd_doc, ymax = norm_doc + trt_sd_doc), width = 0.5) +
  geom_point(aes(fill = Treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  labs(y = expression(paste("Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 2 DOC") + 
  guides(color = F, fill = F)
```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8, fig.align = "center", warning = FALSE}
export_bioav %>% 
  filter(Cruise == "AT34", Station == 2) %>% 
  drop_na(norm_doc) %>% 
  select(Cruise, Station, degree_bin, Depth, Treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  mutate(degree_bin = paste(degree_bin, "˚N")) %>% 
  group_by(Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = -norm_doc_from_t0, group = Treatment)) + 
  geom_point(aes(fill = Treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  labs(y = expression(paste("Delta Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  ggtitle("NAAMES 2 DOC") + 
  guides(color = F, fill = F)
```


## NAAMES 3

#### No Additions

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 10, fig.align = "center", warning = FALSE}
export_bioav %>% 
  filter(Cruise == "AT38", Treatment == "Control") %>%  
   drop_na(norm_doc) %>% 
  select(Cruise, Station, degree_bin, Depth, Treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  mutate(degree_bin = paste(degree_bin, "˚N")) %>% 
  group_by(Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = norm_doc, group = Treatment)) + 
  geom_errorbar(aes(ymin = norm_doc - trt_sd_doc, ymax = norm_doc + trt_sd_doc), width = 0.5) +
  geom_point(aes(fill = Treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  labs(y = expression(paste("Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  facet_grid(~degree_bin, scales = "free") +
  ggtitle("NAAMES 3 DOC") + 
  guides(color = F, fill = F)

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
export_bioav %>% 
  filter(Cruise == "AT38", Treatment == "Control") %>%  
  drop_na(norm_doc) %>% 
  select(Cruise, Station, degree_bin, Depth, Treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  mutate(degree_bin = paste(degree_bin, "˚N")) %>% 
  group_by(Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = -norm_doc_from_t0, group = Treatment)) + 
  geom_point(aes(fill = Treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  labs(y = expression(paste("Delta Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  facet_grid(~degree_bin, scales = "free") +
  ggtitle("NAAMES 3 DOC") + 
  guides(color = F, fill = F)

```


#### Additions

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
export_bioav %>% 
  filter(Cruise == "AT38", Station == 1, Treatment %in% c("Control", "SynExd", "SynLys", "TWExd")) %>%
 drop_na(norm_doc) %>% 
  select(Cruise, Station, degree_bin, Depth, Treatment, facet_treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  mutate(degree_bin = paste(degree_bin, "˚N")) %>% 
  group_by(Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = norm_doc, group = Treatment)) + 
  geom_errorbar(aes(ymin = norm_doc - trt_sd_doc, ymax = norm_doc + trt_sd_doc), width = 0.5) +
  geom_point(aes(fill = facet_treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = facet_treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  labs(y = expression(paste("Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  facet_grid(~degree_bin, scales = "free_y") +
  ggtitle("NAAMES 3 Station 1 Addition Experiment") + 
  guides(color = F)

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
export_bioav %>% 
  filter(Cruise == "AT38", Station == 1, Treatment %in% c("Control", "SynExd", "SynLys", "TWExd")) %>%
 drop_na(norm_doc) %>% 
  select(Cruise, Station, degree_bin, Depth, Treatment, facet_treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  mutate(degree_bin = paste(degree_bin, "˚N")) %>% 
  group_by(Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = -norm_doc_from_t0, group = Treatment)) + 
  geom_point(aes(fill = facet_treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = facet_treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  labs(y = expression(paste("Delta Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  facet_grid(~degree_bin, scales = "free_y") +
  ggtitle("NAAMES 3 Station 1 Addition Experiment") + 
  guides(color = F)


```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
export_bioav %>% 
  filter(Cruise == "AT38", Depth == 10, Station %in% c(1, 3, 6), Treatment %in% c("Control", "SynLys")) %>% 
 drop_na(norm_doc) %>% 
  select(Cruise, Station, degree_bin, Depth, Treatment, facet_treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  mutate(degree_bin = paste(degree_bin, "˚N")) %>% 
  group_by(Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = norm_doc, group = Treatment)) + 
  geom_errorbar(aes(ymin = norm_doc - trt_sd_doc, ymax = norm_doc + trt_sd_doc), width = 0.5) +
  geom_point(aes(fill = facet_treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = facet_treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  labs(y = expression(paste("Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  facet_grid(~degree_bin, scales = "free") +
  ggtitle("NAAMES 3 Addition Experiments") +
  guides(color = F)

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
export_bioav %>% 
  filter(Cruise == "AT38", Depth == 10, Station %in% c(1, 3, 6), Treatment %in% c("Control", "SynLys")) %>% 
 drop_na(norm_doc) %>% 
  select(Cruise, Station, degree_bin, Depth, Treatment, facet_treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  mutate(degree_bin = paste(degree_bin, "˚N")) %>% 
  group_by(Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = -norm_doc_from_t0, group = Treatment)) + 
  geom_point(aes(fill = facet_treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = facet_treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  labs(y = expression(paste("Delta Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  facet_grid(~degree_bin, scales = "free") +
  ggtitle("NAAMES 3 Addition Experiments") +
  guides(color = F)

```


### NAAMES 4

#### No Additions

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 11, fig.align = "center", warning = FALSE}
export_bioav %>% 
  filter(Cruise == "AT39", Treatment == "Control") %>% 
   drop_na(norm_doc) %>% 
  select(Cruise, Station, degree_bin, Depth, Treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  mutate(degree_bin = paste(degree_bin, "˚N")) %>% 
  group_by(Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = norm_doc, group = Station)) + 
  geom_errorbar(aes(ymin = norm_doc - trt_sd_doc, ymax = norm_doc + trt_sd_doc), width = 0.5) +
  geom_point(aes(fill = Station), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Station), alpha = 0.7) +
  #scale_color_manual(values = custom.colors) +
  #scale_fill_manual(values = custom.colors) +
  labs(y = expression(paste("Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  facet_grid(~degree_bin, scales = "free") +
  ggtitle("NAAMES 4 DOC") +
  guides(color = F)

```


```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 11, fig.align = "center", warning = FALSE}
export_bioav %>% 
  filter(Cruise == "AT39", Treatment == "Control") %>% 
   drop_na(norm_doc) %>% 
  select(Cruise, Station, degree_bin, Depth, Treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  mutate(degree_bin = paste(degree_bin, "˚N")) %>% 
  group_by(Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = -norm_doc_from_t0, group = Station)) + 
  geom_point(aes(fill = Station), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Station), alpha = 0.7) +
  #scale_color_manual(values = custom.colors) +
  #scale_fill_manual(values = custom.colors) +
  labs(y = expression(paste("Delta Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  facet_grid(~degree_bin, scales = "free") +
  ggtitle("NAAMES 4 DOC") +
  guides(color = F)

```

The replication between experiments at Station 4 is poor. 

#### Additions

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
export_bioav %>% 
  filter(Cruise == "AT39", Station == 2, !Treatment == "Parallel") %>% 
 drop_na(norm_doc) %>% 
  select(Cruise, Station, degree_bin, Depth, Treatment, facet_treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  mutate(degree_bin = paste(degree_bin, "˚N")) %>% 
  group_by(Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = norm_doc, group = Treatment)) + 
  geom_errorbar(aes(ymin = norm_doc - trt_sd_doc, ymax = norm_doc + trt_sd_doc), width = 0.5) +
  geom_point(aes(fill = Treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Treatment), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  labs(y = expression(paste("Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  facet_grid(~facet_treatment, scales = "free") +
  guides(fill = F, color = F)

```

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10, fig.align = "center", warning = FALSE}
export_bioav %>% 
  filter(Cruise == "AT39", Station == 2, !Treatment == "Parallel") %>% 
 drop_na(norm_doc) %>% 
  select(Cruise, Station, degree_bin, Depth, Treatment, facet_treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  mutate(degree_bin = paste(degree_bin, "˚N")) %>% 
  group_by(Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = -norm_doc_from_t0, group = Treatment)) + 
  geom_point(aes(fill = Treatment), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Treatment), alpha = 0.7) +
  #scale_color_manual(values = custom.colors) +
  #scale_fill_manual(values = custom.colors) +
  labs(y = expression(paste("Delta Seasonally Accumulated DOC, µmol C L"^-1))) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  custom_theme() +
  facet_grid(~facet_treatment, scales = "free_y") +
  guides(fill = F, color = F)

```

## Seasonal Comparison

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 16, fig.align = "center", warning = FALSE}
export_bioav %>% 
  drop_na(norm_doc) %>% 
  select(Season, Cruise, Station, degree_bin, Depth, Treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc) %>% 
  distinct() %>% 
  filter(Treatment == "Control", Depth == 10) %>% 
  mutate(degree_bin = paste(degree_bin, "˚N")) %>% 
  group_by(Cruise, Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = norm_doc, group = Station)) + 
  geom_hline(aes(yintercept = 0)) +
  geom_errorbar(aes(ymin = norm_doc - trt_sd_doc, ymax = norm_doc + trt_sd_doc), width = 0.5) +
  geom_point(aes(fill = Season), size = 4, shape = 21, alpha = 0.7 ) +
  geom_line(aes(color = Season), alpha = 0.7) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  facet_grid(~degree_bin, scales = "free") +
  labs(y = expression(paste("Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  guides(color = F, fill = F)
```

```{r include = F}
seas_bioav.table <- export_bioav %>% 
  filter(Treatment == "Control", Depth == "10") %>% 
  select(Season:Station, bioav_doc:per_persis, ddoc) %>% 
  distinct() %>% 
  group_by(Season) %>% 
  summarize(min_bioav_doc = min(bioav_doc, na.rm = T),
            mean_bioav_doc = mean(bioav_doc, na.rm = T),
            med_bioav_doc = median(bioav_doc, na.rm = T),
            max_bioav_doc = max(bioav_doc, na.rm = T),
            
            min_persis_doc = min(persis_doc, na.rm = T),
            mean_persis_doc = mean(persis_doc, na.rm = T),
            med_persis_doc = median(persis_doc, na.rm = T),
            max_persis_doc = max(persis_doc, na.rm = T),
            
            min_ddoc = min(ddoc, na.rm = T),
            mean_ddoc = mean(ddoc, na.rm = T),
            med_ddoc = median(ddoc, na.rm = T),
            max_ddoc = max(ddoc, na.rm = T),
            
            min_bioav = min(per_bioav, na.rm = T),
            mean_bioav = mean(per_bioav, na.rm = T),
            med_bioav = median(per_bioav, na.rm = T),
            max_bioav = max(per_bioav, na.rm = T),
            
            min_persis = min(per_persis, na.rm = T),
            mean_persis = mean(per_persis, na.rm = T),
            med_persis = median(per_persis, na.rm = T),
            max_persis = max(per_persis, na.rm = T)) %>% 
  mutate_at(vars(min_bioav_doc:max_persis), round, 1) %>% 
  mutate_at(vars(min_ddoc:max_persis), round) 
```

```{r echo = FALSE, results = 'asis'}
kable(seas_bioav.table, caption = "Seasonal Accumulated DOC Bioavailability and Persistance")
```

This seasonal comparison is best exemplifies at 44˚N where we have experiments from all cruises. It shows:

- an increase in the accumulated DOC pool from the early spring to the early autumn
- an increase in the persistent fraction of the bulk DOC as the seasons progress
  + DOC in the early spring does not accumulate (also apparent at 39˚N)
  + 64% of DOC pool in the late spring was persistent while 69% of the DOC pool in the early autumn was persistent. This would imply an increase of the persistent DOC fraction by 5%. I think this suggests that most of the net production of persistent DOC occurs in the late spring, closer to the timing of the bloom peak. 

Overall, there are elevated persistent fractions in the late spring and early autumn, with greater proportion of the early autumn pool beeing more consistently persistant. 

Our addition experiments are consistent with our definition of DOC persistence. In every cruise, the addition of DOM substrates (different quality and substrates) stimulated drawdown of accumulated DOC and bacterioplankton growth, but did not result in drawdown into the persistent pool. 

```{r echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 16, fig.align = "center", warning = FALSE}
export_bioav %>% 
  drop_na(norm_doc) %>% 
  select(Season, Cruise, Station, degree_bin, Depth, Addition, Treatment, facet_treatment, Days, norm_doc, norm_doc_from_t0, trt_sd_doc, accm_doc, bioav_accm_doc) %>% 
  distinct() %>% 
  filter(Depth == 10, !Treatment %in% c("MixDS", "MixSD"), !Cruise == "AT34", Addition == T) %>% 
  mutate(degree_bin = paste(degree_bin, "˚N"), 
         plot_treatment = ifelse(Cruise != "AT39", facet_treatment, "T. Weissflogii Exudate")) %>% 
  group_by(Cruise, Station, Depth, Treatment) %>%
  ggplot(aes(x = Days, y = norm_doc, group = Treatment)) + 
  geom_hline(aes(yintercept = 0)) +
  geom_hline(aes(yintercept = accm_doc), linetype = 2) +
  geom_label(aes(x = 50, y = accm_doc + 1.5, label = "Seasonally Accm. DOC"), size = 3) +
  geom_hline(aes(yintercept = bioav_accm_doc), linetype = 3) +
  geom_label(aes(x = 45, y = bioav_accm_doc - 1.5, label = "Non-addition Bioavailable DOC"), size = 3) +
  geom_line(aes(color = plot_treatment), alpha = 0.7, size = 1.5) +
   geom_errorbar(aes(ymin = norm_doc - trt_sd_doc, ymax = norm_doc + trt_sd_doc), width = 0.5) +
   geom_point(aes(fill = plot_treatment, shape = Season), size = 4, alpha = 0.7 ) +
  scale_color_manual(values = custom.colors) +
  scale_fill_manual(values = custom.colors) +
  scale_shape_manual(values = custom.shapes) +
  facet_grid(~degree_bin, scales = "free") +
  labs(y = expression(paste("Seasonally Accumulated DOC, µmol C L"^-1))) +
  custom_theme() +
  guides(fill = F)
```





